### 2016-06-29 overview/heg_equations.tex
added background and organized into directories

\documentclass{revtex4}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{braket}
\usepackage{mathtools}
\usepackage{textcomp}
\usepackage{minted}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

\makeatletter
\def\BState{\State\hskip-\ALG@thistlm}
\makeatother

\begin{document}
\title{Notes on Hartree-Fock Stability of HEG}
\author{Evan Curtin}
\maketitle

\section{Equations}

\subsection{Homogeneous Electron Gas}

The Fermi level, $k_f$, is (p. 30 of \cite{Guiliani2005})

\begin{equation}
k_f
=\begin{cases} 
      (3\pi^2n)^{\frac{1}{3}} = \left(\frac{9\pi}{4}\right)^{\frac{1}{3}}\frac{1}{r_sa_0} & 3D \\ \\
      (2\pi n)^{\frac{1}{2}} = \frac{\sqrt{2}}{r_sa_0}  & 2D \\
      \\
      \frac{\pi}{2}n = \frac{\pi}{4 r_s a_0}   & 1D 
   \end{cases}
   .
\end{equation}

The two electron integral is given by (eq. 12 of \cite{Delyon2008} and p. 16 of \cite{Guiliani2005})

\begin{subequations}
\begin{align}
\braket{\vec{k}, \vec{k}'|\vec{k}'',\vec{k}'''}\stackrel{\text{2D, 3D}}{=}&
	\begin{cases} 
	\frac{\pi}{\Omega}\frac{2^{D-1}}{|\vec{k}-\vec{k}''|^{D-1}} 
	& \vec{k}''' = \vec{k}+\vec{k}'-\vec{k}'' \textbf{ and } |\vec{k}-\vec{k}''| \neq 0 \\
	0 
	& \text{else}
	\end{cases}
\\ \nonumber \\
\braket{k, k'|k'',k'''}\stackrel{\text{1D}}{=}&
	\begin{cases} 
	e^{|k-k''|^2a^2}\text{Ei}(-|k-k''|^2a^2)\text{ ;}
	& k''' = k+k'-k'' \textbf{ and } |k-k''| \neq 0 \\
	0\text{ ;} 
	& \text{else}
	\end{cases}
\end{align}
\end{subequations}
where $\Omega$ is the direct lattice volume and D is the dimensionality of the system. Ei(x) denotes the exponential integral function. The orbital energies are given by

\begin{equation}
\epsilon_{\vec{k},\sigma}=
\begin{cases}
	\frac{\hbar^2\vec{k}^2}{2m}-\left(\frac{L}{2\pi}\right)^D\int\limits_{|\vec{k}'|<\vec{k}_f}^{}\braket{\vec{k}, \vec{k}' |\vec{k}', \vec{k}}d\vec{k}'
	&\text{continuous (eq. 23 of \cite{Yamada2015})} \\
	\frac{\hbar^2\vec{k}^2}{2m} - \sum\limits_{\vec{k}}^{|\vec{k}|< k_f}n_{\vec{k}\sigma}\braket{\vec{k}, \vec{k}' |\vec{k}', \vec{k}}
	&\text{discrete (p. 80 of \cite{Guiliani2005})}
\end{cases}
\end{equation}
Where $n_{\vec{k}\sigma}$ is the occupation number of the state with momentum $\vec{k}$ and spin $\sigma$. Here we have used the relationship to relate the discrete and continuous quantities, (p. 15 of \cite{Guiliani2005})

\begin{equation}
	\sum\limits_{\vec{k}}^{}{(...)}\xrightarrow{\text{$dk \ll L$}}\left(\frac{L}{2\pi}\right)^D\int (...)d\vec{k}
\end{equation}

\subsection{Hartree-Fock Stability}
The HF stability conditions (to my knowledge) were presented by Thouless \cite{Thouless1972} ($1^{st}$ Ed. 1960). More general conditions were presented by Adams\cite{Adams1962}. The stability condition is that the eigenvalues ($\lambda$) given by (p. 41 of \cite{Thouless1972})

\begin{equation}
(\epsilon_a-\epsilon_i)C_{ai} + \sum\limits_{\text{j}}^{occ}\sum\limits_{\text{b}}^{vir}
	(\braket{aj|ib}-\braket{aj|bi})C_{bj}
	+(\braket{ab|ij}-\braket{ab|ji})C_{bj}^*
	=\lambda C_{ai}
\end{equation}

\begin{equation}
(\epsilon_a-\epsilon_i)C_{ai}^* + \sum\limits_{\text{j}}^{occ}\sum\limits_{\text{b}}^{vir}
	(\braket{ij|ab}-\braket{ij|ba})C_{bj}
	+(\braket{ib|aj}-\braket{ib|ja})C_{bj}^*
	=\lambda C_{ai}^*,
\end{equation}
are nonnegative. This is equivalent to the RPA oscillation frequencies being all real (p. 115 of \cite{Thouless1972}). The RPA is a linearized approximation to Time-Dependent Hartree-Fock theory. These can be written\cite{Dunning1967}\cite{Seeger1977} in the following form:
\begin{equation}
{}^{1,3}\bf{H'}=
\begin{bmatrix}
{}^{1,3}\bf{A'} & {}^{1,3}\bf{B'} \\
\left({}^{1,3}\bf{B'}\right)^* & \left({}^{1,3}\bf{A'}\right)^* \\
\end{bmatrix}
\end{equation}
Where the $1,3$ denote singlet and triplet states, respectively. $\bf{A}$, $\bf{B}$ have dimension $N_{occ}\times N_{vir}$ and are defined as follows:
\begin{subequations}
	\begin{align}
	{}^{1}{A'}_{i\rightarrow a, j\rightarrow b} &= (\epsilon_a-\epsilon_i)\delta_{ij}\delta_{ab} + 2\braket{aj|ib}-\braket{aj|bi}\\
	{}^{3}{A'}_{i\rightarrow a, j\rightarrow b} &= (\epsilon_a-\epsilon_i)\delta_{ij}\delta_{ab} - \braket{aj|bi}\\
	{}^{1}{B'}_{i\rightarrow a, j\rightarrow b} &= 2\braket{ab|ij}-\braket{ab|ji}\\
	{}^{3}{B'}_{i\rightarrow a, j\rightarrow b} &= -\braket{ab|ji}
	\end{align}
\end{subequations}
\begin{figure}[h]
   \includegraphics[width=1.0\linewidth]{figures/seeger_stability.pdf}
  	\caption {Hartree-Fock Stability conditions reproduced from Seeger \& Pople \cite{Seeger1977}}
  	\label{fig:stability_table}
\end{figure}

\subsection{Davidson's Algorithm}
\subsubsection{Theory}
Oftentimes we're interested only in the lowest or highest few eigenvalues of a large, symmetric matrix. Matrix eigenvalue problem operation counts scale as \url{~}$O(N^3)$ for an $N\times N$ matrix, while the memory requirement scales quadratically. Iterative subspace methods based off the Rayleigh-Ritz method are popular ways of dealing with this issue. The most famous are the Lanczos (hermitian) and Arnoldi (non-hermitian) algorithms, which build as their subspace a Krylov space. A more involved algorithm was proposed by Davidson\cite{Davidson1975} and involves building a subspace with correction vectors to be described momentarily. But first, a few definitions are introduced to define the notation to be used.

We are interested in the lowest (or highest) $k$ ($0 < k \leq N$) eigenvalue(s) of the $N \times N$ hermitian matrix, A,
\begin{equation}
\bf{Ax}=\lambda\bf{x}
\end{equation}
We begin by guessing $M$ ($M \geq k$) vectors, $\bf{v}$ which approximately span the space of the actual eigenvectors. Let $\bf{V}$ be the $N\times M$ matrix whose columns are the approximate eigenvectors, 
\begin{equation}
\bf{V}=[\bf{v_1,v_2,...,v_M}]	
\end{equation}
where care must be taken to ensure columns of $\bf{V}$ form an orthogonal set. We then transform our matrix into the subspace as follows, 
\begin{equation}
\bf{\tilde{A}} = \bf{V}^\dag\bf{AV}
\end{equation}
where the \url{~} will be used to denote entities in the subspace. $\bf{\tilde{A}}$ is an $M \times M$ matrix where $M \ll N$, and therefore we can use standard diagonalization routines to calculate the eigenvalues and eigenvectors in the subspace, 
\begin{equation}
\bf{\tilde{A}\tilde{x}}=\tilde{\lambda}\bf{\tilde{x}}
\end{equation}
The subspace eigenpair $(\tilde{\lambda}_i,\mathbf{\tilde{x}}_i)$ is then used to create the \emph{Ritz pair}, $({\lambda_i^R},\mathbf{x}_i^R)$. The ritz pair is the approximation to the exact eigenpair of the matrix, and is determined by
\begin{subequations}
	\begin{align}
	 \mathbf{x_i} &\approx \mathbf{x}_i^R = \mathbf{V\tilde{x}}_i\\
	 \lambda_i &\approx \lambda_i^R = \tilde{\lambda}_i
	\end{align}
\end{subequations}
At any time, the quality of the approximation can be determined by calculating the norm of the \emph{residue},
\begin{equation}
\mathbf{r}_i=\left(\mathbf{A}-\lambda_i\mathbf{I}\right)\mathbf{x}_i^R
\end{equation}
when $||\mathbf{r}_i||$ is smaller than a given tolerance for the desired k eigenpairs, the algorithm is finished and the current Ritz pairs are taken to be the eigenpairs. If this condition is not met, the subspace needs to be expanded. This is done by computing correction vectors, $\mathbf{\delta}_i$,
\begin{equation}
\mathbf{\delta}_i = c_i\mathbf{r}_i
\end{equation}
for $i =0...l$ where $l$ is the number of desired ritz pairs with $||\mathbf{r}_i||$ greater than the given tolerance. Corrections are only calculated for these Ritz pairs. The coefficient, $c_i$ is a preconditioner. The original choice of $c_i$ introduced by Davidson\cite{Davidson1975} was diagonal preconditioning, 
\begin{equation}
c_i = \frac{1}{\lambda_i\mathbf{I}-\mathbf{D}}
\end{equation}
where $\mathbf{D}$ is the $N\times N$ diagonal matrix consisting of the diagonal elements of $\mathbf{A}$, and $\mathbf{I}$ is the identity matrix of the same size. It may help convergence to use a modified version of this approach, 
\begin{equation}
c_i = \frac{1}{\rho_i\mathbf{I}-\mathbf{D}}
\end{equation}
where $\rho_i$ is the \emph{rayleigh quotient}, defined by
\begin{equation}
\rho_i = \frac{\mathbf{x}_i^{R\dag}\mathbf{A}\mathbf{x}_i^{R}}{||\mathbf{x}_i^{R}||}
\end{equation}
The rayleigh quotient from a physicist's perspective is $\rho_i = \braket{\mathbf{x}_i^{R}|\mathbf{A}|\mathbf{x}_i^{R}}$, which looks like the expectation value of $\mathbf{A}$ in the state $\mathbf{x}_i^{R}$. As $\mathbf{x}_i^{R}$ approaches the actual eigenstate of the system, the rayleigh quotient approaches the eigenvalue.
\\\\
The correction vector is then added to $\mathbf{V}$ and the process is repeated. The correction vector must be normalized and orthogonalized to the columns of $\mathbf{V}$. The subspace size is therefore increased by $l$. 
\begin{subequations}
\begin{align}
\mathbf{V} &= [\mathbf{v_1,v_2,...,v_M}\mathbf{,\delta}_1\mathbf{,\delta}_2,...\mathbf{,\delta}_l] \\
\mathbf{V} &= orthonormalized(\mathbf{V})\\
M &= M + l
\end{align}
\end{subequations}

\subsubsection{Implementation}
\begin{algorithm}[H]
\caption{Davidson's Algorithm}\label{davidson}
\begin{algorithmic}[1]
\State create \bf{V}
\For {$i = 0, max\text{ }iterations$}
\State $\bf{\tilde{A}} = \bf{V}^\dag\bf{AV}$
\State $\tilde{\lambda},\mathbf{\tilde{x}} = eigensystem(\bf{\tilde{A}})$
\State sort $\tilde{\lambda},\mathbf{\tilde{x}}$
\If {$i > \textit{stringlen}$} \Return false
\EndIf
\State $j \gets \textit{patlen}$
\If {$\textit{string}(i) = \textit{path}(j)$}
\State $j \gets j-1$.
\State $i \gets i-1$.
\State \textbf{goto} \emph{loop}.
\State \textbf{close};
\EndIf
\State $i \gets i+\max(\textit{delta}_1(\textit{string}(i)),\textit{delta}_2(j))$.
\State \textbf{goto} \emph{top}.
\EndFor

\end{algorithmic}
\end{algorithm}

\section{Code Layout}
\begin{figure}[H]
   \includegraphics[width=1.0\linewidth]{figures/hf_stability_diagram.eps}
   \caption {Layout of code implementation. Red boxes are python, blue are C++ and purple dotted lines require cython. Green are likely to be removed for speed}
   \label{fig:code_diagram}
\end{figure}

\section{References}
\bibliography{heg_references}
\end{document}

### 2016-06-29 source/HFStability.pyx

@@ -1,0 +1,166 @@
+################################################################################
+#																			   # 
+#            				   C++ Land is Here								   # 
+#																			   # 
+################################################################################
+from libcpp cimport bool
+import numpy as np
+cimport numpy as np
+include "cyarma.pyx"
+	
+#C++ class
+#Note only methods/attributes that want python access need to be here.
+cdef extern from "stability.h" namespace "HFStability":
+	cdef cppclass HEG:
+		HEG() except +
+
+		#Attrubutes
+		double  bzone_length, vol, rs, kf
+		long    Nocc, Nvir, Nexc, N_elec, ndim, Nk
+		mat states, excitations       #arma::mat wrapped by cyarma
+		umat excitations              #arma::umat not native to cyarma I added it
+
+		#Methods
+		double min_eigval(long, long, long, long, long, long, bool, double, double*)
+		double two_electron(double[], double[], double[], double[])
+		double two_electron_2d(double[], double[], double[], double[])
+
+################################################################################
+#																			   # 
+#            				   Python Land is Here							   # 
+#                         (it's all actually Cython tho)                       #
+#																			   # 
+################################################################################
+#Python interface to c++ class
+cdef class PyHEG:
+	cdef HEG* c_HEG
+
+	#Standard stuff
+	def __cinit__(self):
+		self.c_HEG = new HEG()
+	def __dealloc__(self):
+		del self.c_HEG
+
+	#Class methods
+#	def getA(self, long i, long j):
+#		return self.c_HEG.get_A(i, j)
+#	def min_eigval(self, 
+#				   np.ndarray[double, ndim = 2] GUESS_VECS not None,
+#				   long MAX_ITS = 20, 
+#				   long NUM_OF_ROOTS = 1, 
+#				   long MAX_SUB_SIZE = 2000, 
+#				   long BLOCK_SIZE   = 1,
+#				   bool DOTEST=False, 
+#				   double TOLERANCE  =  10E-8):
+#
+#		GUESS_VECS = np.asfortranarray(GUESS_VECS)
+#		
[…]

### 2016-06-29 source/cyarma.pyx

@@ -1,0 +1,325 @@
+import numpy as np
+cimport numpy as np
+cimport cython
+
+from cython.operator cimport dereference as deref
+
+from libcpp cimport bool
+
+cdef extern from "armadillo" namespace "arma" nogil:
+	# unsigned in matrix class, added by Ecurtin, June 28, 2016
+    cdef cppclass umat:
+        umat(unsigned int * aux_mem, int n_rows, int n_cols, bool copy_aux_mem, bool strict) nogil
+        umat(unsigned int * aux_mem, int n_rows, int n_cols) nogil
+        umat(int n_rows, int n_cols) nogil
+        umat() nogil
+        # attributes
+        int n_rows
+        int n_cols
+        int n_elem
+        int n_slices
+        int n_nonzero
+        #management
+        umat reshape(int, int) nogil
+        umat resize(int, int) nogil
+        unsigned int * memptr() nogil
+
+    # matrix class (double)
+    cdef cppclass mat:
+        mat(double * aux_mem, int n_rows, int n_cols, bool copy_aux_mem, bool strict) nogil
+        mat(double * aux_mem, int n_rows, int n_cols) nogil
+        mat(int n_rows, int n_cols) nogil
+        mat() nogil
+        # attributes
+        int n_rows
+        int n_cols
+        int n_elem
+        int n_slices
+        int n_nonzero
+        # fuctions
+        mat i() nogil #inverse
+        mat t() nogil #transpose
+        vec diag() nogil
+        vec diag(int) nogil
+        fill(double) nogil
+        void raw_print(char*) nogil
+        void raw_print() nogil
+        vec unsafe_col(int) nogil
+        vec col(int) nogil
+        #print(char)
+        #management
+        mat reshape(int, int) nogil
+        mat resize(int, int) nogil
+        double * memptr() nogil
+        # opperators
+        double& operator[](int) nogil
+        double& operator[](int,int) nogil
+        double& at(int,int) nogil
+        double& at(int) nogil
+        mat operator*(mat) nogil
+        mat operator%(mat) nogil
+        vec operator*(vec) nogil
+        mat operator+(mat) nogil
+        mat operator-(mat) nogil
+        mat operator*(double) nogil
[…]

### 2016-06-29 source/setup.py

@@ -1,0 +1,16 @@
+from distutils.core import setup 
+from Cython.Build import cythonize 
+from distutils.extension import Extension
+
+sourcefiles  = ['*.pyx', 'stability.cpp']
+compile_opts = ['-O3', '-ffast-math', '-std=c++11']
+my_libraries = ['armadillo']
+
+ext=[Extension('*', sourcefiles, extra_compile_args=compile_opts, language='c++', libraries=my_libraries)] 
+ 
+setup( 
+  ext_modules=cythonize(ext) 
+) 
+
+#import os
+#os.system('mv *.so ~/usr/bin/python')

### 2016-06-29 source/stability.h

@@ -1,0 +1,32 @@
+#ifndef CPP_STABILITY // header guards 
+#define CPP_STABILITY
+#ifndef PI
+	#define PI 3.14159265358979323846264338327
+#endif
+#include "armadillo"
+
+namespace HFStability {
+	class HEG {
+	public:
+		//Attributes
+		double  bzone_length, vol, rs, kf;
+		long    Nocc, Nvir, Nexc, N_elec, ndim, Nk;
+		arma::mat  states;
+		arma::umat excitations;
+
+		//Methods
+        double min_eigval(long, long, long, long, long, long, bool, double, double*);
+		double two_electron_3d(double[], double[], double[]);
+		double two_electron_2d(double[], double[], double[]);
+		double davidson_algorithm(long, 
+				long,
+			   	long, 
+				long, 
+				arma::uword,
+			   	arma::mat,
+				double, 
+			   	double (HFStability::HEG::*)(long, long));
+	};
+}
+
+#endif

### 2016-06-29 HFStability.pyx
Delete HFStability.pyx

@@ -1,166 +1,0 @@
-################################################################################
-#																			   # 
-#            				   C++ Land is Here								   # 
-#																			   # 
-################################################################################
-from libcpp cimport bool
-import numpy as np
-cimport numpy as np
-include "cyarma.pyx"
-	
-#C++ class
-#Note only methods/attributes that want python access need to be here.
-cdef extern from "stability.h" namespace "HFStability":
-	cdef cppclass HEG:
-		HEG() except +
-
-		#Attrubutes
-		double  bzone_length, vol, rs, kf
-		long    Nocc, Nvir, Nexc, N_elec, ndim, Nk
-		mat states, excitations       #arma::mat wrapped by cyarma
-		umat excitations              #arma::umat not native to cyarma I added it
-
-		#Methods
-		double min_eigval(long, long, long, long, long, long, bool, double, double*)
-		double two_electron(double[], double[], double[], double[])
-		double two_electron_2d(double[], double[], double[], double[])
-
-################################################################################
-#																			   # 
-#            				   Python Land is Here							   # 
-#                         (it's all actually Cython tho)                       #
-#																			   # 
-################################################################################
-#Python interface to c++ class
-cdef class PyHEG:
-	cdef HEG* c_HEG
-
-	#Standard stuff
-	def __cinit__(self):
-		self.c_HEG = new HEG()
-	def __dealloc__(self):
-		del self.c_HEG
-
-	#Class methods
-#	def getA(self, long i, long j):
-#		return self.c_HEG.get_A(i, j)
-#	def min_eigval(self, 
-#				   np.ndarray[double, ndim = 2] GUESS_VECS not None,
-#				   long MAX_ITS = 20, 
-#				   long NUM_OF_ROOTS = 1, 
-#				   long MAX_SUB_SIZE = 2000, 
-#				   long BLOCK_SIZE   = 1,
-#				   bool DOTEST=False, 
-#				   double TOLERANCE  =  10E-8):
-#
-#		GUESS_VECS = np.asfortranarray(GUESS_VECS)
-#		
[…]

### 2016-06-29 cyarma.pyx
Delete cyarma.pyx

@@ -1,325 +1,0 @@
-import numpy as np
-cimport numpy as np
-cimport cython
-
-from cython.operator cimport dereference as deref
-
-from libcpp cimport bool
-
-cdef extern from "armadillo" namespace "arma" nogil:
-	# unsigned in matrix class, added by Ecurtin, June 28, 2016
-    cdef cppclass umat:
-        umat(unsigned int * aux_mem, int n_rows, int n_cols, bool copy_aux_mem, bool strict) nogil
-        umat(unsigned int * aux_mem, int n_rows, int n_cols) nogil
-        umat(int n_rows, int n_cols) nogil
-        umat() nogil
-        # attributes
-        int n_rows
-        int n_cols
-        int n_elem
-        int n_slices
-        int n_nonzero
-        #management
-        umat reshape(int, int) nogil
-        umat resize(int, int) nogil
-        unsigned int * memptr() nogil
-
-    # matrix class (double)
-    cdef cppclass mat:
-        mat(double * aux_mem, int n_rows, int n_cols, bool copy_aux_mem, bool strict) nogil
-        mat(double * aux_mem, int n_rows, int n_cols) nogil
-        mat(int n_rows, int n_cols) nogil
-        mat() nogil
-        # attributes
-        int n_rows
-        int n_cols
-        int n_elem
-        int n_slices
-        int n_nonzero
-        # fuctions
-        mat i() nogil #inverse
-        mat t() nogil #transpose
-        vec diag() nogil
-        vec diag(int) nogil
-        fill(double) nogil
-        void raw_print(char*) nogil
-        void raw_print() nogil
-        vec unsafe_col(int) nogil
-        vec col(int) nogil
-        #print(char)
-        #management
-        mat reshape(int, int) nogil
-        mat resize(int, int) nogil
-        double * memptr() nogil
-        # opperators
-        double& operator[](int) nogil
-        double& operator[](int,int) nogil
-        double& at(int,int) nogil
-        double& at(int) nogil
-        mat operator*(mat) nogil
-        mat operator%(mat) nogil
-        vec operator*(vec) nogil
-        mat operator+(mat) nogil
-        mat operator-(mat) nogil
-        mat operator*(double) nogil
[…]

### 2016-07-01 overview/heg_equations.tex

@@
 
-\section{Equations}
-
-\subsection{Homogeneous Electron Gas}
+\section{Homogeneous Electron Gas}
 
@@
 
-\subsection{Hartree-Fock Stability}
+The analytic form of the exchange energy is known in the continuous case.
+Let $y = \frac{k}{k_{F\sigma}}$.
+Equations \ref{eq:hfexch} through \ref{eq:fnd} are from p.
+81-82 of \cite{Guiliani2005}.
+In 2 or 3 dimensions the exchange energy is,
+
+\begin{equation}\label{eq:hfexch}
+\epsilon_{k\sigma}^{(x)} = -\frac{2e^2k_{F\sigma}}{\pi}f_{ND}\left(\frac{k}{k_{F\sigma}}\right),
+\end{equation}
+where in 3D, the function $f_{3D}$ is given by
+\begin{equation}
+f_{3D}\left(y\right) = \frac{1}{2} + \frac{1-y^2}{4y} ln \left|\frac{1+y}{1-y} \right|,
+\end{equation}
+and in 2D, it is
+\begin{equation}\label{eq:fnd}
+f_{2D}\left(y\right) = 
+\begin{cases} 
+    \mathbf{E}\left(y\right), &  y \leq 1, \\
+    y 
+    \left[ 
+        \mathbf{E} 
+        \left(
+            \frac{1}{y} 
+        \right)
+        -
+        \left(
+            1 - \frac{1}{y^2}
+        \right)
+        \mathbf{K}
+        \left(
+            \frac{1}{y}
+        \right)
+       \right]  ,& y \geq 1. 
+\end{cases}
+\end{equation}
+The functions $\mathbf{K}(y)$ and $ \mathbf{E}(y) $ are complete elliptic integrals of the first and second kind, respectively.
+These are implemented in SciPy as \emph{scipy.special.ellipk} and \emph{scipy.special.ellipe}.
+
+\section{Hartree-Fock Stability}
 The HF stability conditions (to my knowledge) were presented by Thouless \cite{Thouless1972} ($1^{st}$ Ed.
@@
 These can be written\cite{Dunning1967}\cite{Seeger1977} in the following form:
-\begin{equation}
+\begin{equation}\label{eq:1,3H}
 {}^{1,3}\bf{H'}=
@@
 \end{subequations}
+The matrix given in Equation \ref{eq:1,3H} represents the case of complex RHF stability in the space of complex RHF space (${}^{1}\mathbf{H}$ - internal instability) and in the space of complex UHF space (${}^{3}\mathbf{H}$ - triplet instability).
+Seeger and Pople \cite{Seeger1977} give both more general formulae, and simplifications in special cases.
+Figure \ref{fig:stability_table} is a reproduction of the stability conditions they developed, and more details can be found in the paper.
 \begin{figure}[h]
@@
 
-\subsection{Davidson's Algorithm}
-\subsubsection{Theory}
+\section{Davidson's Algorithm}
+\subsection{Theory}
 Oftentimes we're interested only in the lowest or highest few eigenvalues of a large, symmetric matrix.
-Matrix eigenvalue problem operation counts scale as \url{~}$O(N^3)$ for an $N\times N$ matrix, while the memory requirement scales quadratically.
+Matrix eigenvalue problem operation counts scale as \url{~}$O(N^3)$ for an $N \times N$ matrix, while the memory requirement scales quadratically.
 Iterative subspace methods based off the Rayleigh-Ritz method are popular ways of dealing with this issue.
@@
 
-\subsubsection{Implementation}
+\subsection{Implementation}
 \begin{algorithm}[H]

### 2016-07-25 overview/heg_equations.tex
Pushed functionality to the class level within .pyx. The calc is started by __init__(args) and is greatly simplified at the python level.

@@
 These are implemented in SciPy as \emph{scipy.special.ellipk} and \emph{scipy.special.ellipe}.
+After a significant struggle, I have found that the author of the textbook\cite{Guiliani2005} and scipy/wolfram use a different definition of the complete elliptic integral.
+I was able to reproduce the graphs on pages 82 and 83 of \cite{Guiliani2005} properly with $\mathbf{K}(x) \rightarrow \mathbf{K}(x^2)$ and $\mathbf{E}(x) \rightarrow \mathbf{E}(x^2)$.
 

### 2016-07-25 source/HFStability.pyx

@@ -4,6 +4,9 @@
 #																			   # 
 ################################################################################
 from libcpp cimport bool
+import itertools
+import math
+from scipy import special as sp
 import numpy as np
 cimport numpy as np
 include "cyarma.pyx"
@@ -18,7 +21,7 @@ cdef extern from "stability.h" namespace "HFStability":
 		double  bzone_length, vol, rs, kf
 		long    Nocc, Nvir, Nexc, N_elec, ndim, Nk
 		mat states                                #arma::mat wrapped by cyarma
-		umat excitations                         #arma::umat not native to cyarma I added it
+		umat excitations                          #arma::umat not native to cyarma I added it
 		uvec occ_states, vir_states
 
 		#Methods
@@ -35,6 +38,7 @@ cdef extern from "stability.h" namespace "HFStability":
 ################################################################################
 #Python interface to c++ class
 cdef class PyHEG:
+	"""This is a class docstring"""
 	cdef HEG* c_HEG
 
 	#Standard stuff
@@ -43,9 +47,92 @@ cdef class PyHEG:
 	def __dealloc__(self):
 		del self.c_HEG
 
+	#All constants of calculation specified by __init__
+	def __init__(self, ndim=3, rs=1.0, Nk=4):
+		"""This is an init docstring"""
+		self.ndim = int(ndim)
+		self.rs = float(rs)
+		self.Nk = int(Nk)
+
+		#Determine other parameters
+		if self.ndim == 1:
+			self.kf = np.pi / (4 *self.rs)
+		elif self.ndim == 2:
+			self.kf = 2**0.5 /self.rs
+		elif self.ndim == 3:
+			self.kf = (9 * np.pi / 4)**(1./3.) * (1. / self.rs) 
+
+		kmax = 2.0 * self.kf
+		kgrid = np.linspace(-kmax, kmax, self.Nk)
+		#brillioun zone is from - pi/a .. pi/a
+		self.bzone_length =  kmax
+		direct_length = np.pi / kmax
+		self.vol = direct_length**(self.ndim)
+
+		temp = range(self.Nk)
+		states = temp
+		for i in range(self.ndim - 1):
+			states = itertools.product(states,temp)
+		states = list(states)
+
+		#unpack into list of tuples
+		if self.ndim == 3:
+			states = [(item[0][0], item [0][1], item[1]) for item in states]
+
+		if self.ndim == 1:
[…]

### 2016-08-11 source/HFStability.pyx
Fixed the states and streamlined their calculation using itertools. The resulting parameters are now updated whenever Nk, ndim or rs are changed. The Exchange energy is still not being done properly

@@ -15,7 +15,7 @@ cdef extern from "stability.h" namespace "HFStability":
     cdef cppclass HEG:
         HEG() except +
         #Attributes
-        double bzone_length, vol, rs, kf
+        double bzone_length, vol, rs, kf, fermi_energy
         long Nocc, Nvir, Nexc, N_elec, ndim, Nk
         mat states          #arma::mat wrapped by cyarma
         umat excitations    #arma::umat not native to cyarma I added it
@@ -43,8 +43,8 @@ cdef class PyHEG:
     #All constants of calculation specified by __init__
     def __init__(self, ndim=3, rs=1.0, Nk=4):
         """This is an init docstring"""
-        self.ndim = int(ndim)
         self.rs = float(rs)
+        self.ndim = int(ndim)
         self.Nk = int(Nk)
         self.get_resulting_params()
 
@@ -52,7 +52,8 @@ cdef class PyHEG:
         """Given rs, ndim, Nk, determine other parameters
 
         Description:
-
+                Does nothing if all 3 aren't defined, which shouldn't
+                ever be possible.
         Args:
                 No args
         Returns:
@@ -62,34 +63,36 @@ cdef class PyHEG:
                 
 
         """
+        #It looks like the variables default to 0, not undefined?
+        if self.rs == 0 or self.ndim == 0 or self.Nk == 0:
+            return None
+        try:
+            self.rs
+            self.ndim
+            self.Nk
+        except:
+            return None #Don't try to calc resulting params until all defined!
+        else:
+            pass #Continue on if it checks out
+
         if self.ndim == 1:
-            self.kf = np.pi / (4 *self.rs)
+            self.kf = np.pi / (4 * self.rs)
         elif self.ndim == 2:
-            self.kf = 2**0.5 /self.rs
+            self.kf = 2**0.5 / self.rs
         elif self.ndim == 3:
             self.kf = (9 * np.pi / 4)**(1./3.) * (1. / self.rs) 
 
         kmax = 2.0 * self.kf
-        kgrid = np.linspace(-kmax, kmax, self.Nk)
+        self.fermi_energy = 0.5 * self.kf**2
         #brillioun zone is from - pi/a .. pi/a
         self.bzone_length =  2.0 * kmax
         direct_length = self.bzone_length / (2.0 * np.pi)
-        self.vol = direct_length**(self.ndim)
+        self.vol = direct_length ** (self.ndim)
 
-        temp = range(self.Nk)
-        states = temp
[…]

### 2016-08-11 source/stability.cpp

@@ -18,7 +18,7 @@ double HFStability::HEG::energy(long long unsigned int state)
         k[i] = states(state, i);
         kin += k[i]*k[i];
     }
-    // ||k||/2m
+    // ||k||**2/2m in atomic units
     kin /= 2.0;
 
     double exc = 0;
@@ -29,7 +29,7 @@ double HFStability::HEG::energy(long long unsigned int state)
         //4th is always k by momentum conservation, 2 is occupation #
         exc += 2.0 * two_electron_2d(k, kprime, kprime);
     }
-    exc /= bzone_length*bzone_length;
+    exc /= vol;
     energy = kin - exc;
     return energy;
 }
@@ -65,12 +65,12 @@ double HFStability::HEG::two_electron_3d(double kp[], double kq[], double kr[])
     return 4.0 * PI / (vol * norm);
 }
 
-double HFStability::HEG::two_electron_2d(double kp[], double kq[], double kr[])
+double HFStability::HEG::two_electron_2d(double k1[], double k2[], double k3[])
 {
     //This is momentum conserving
     double k[ndim];
     for (int i = 0; i < ndim; ++i) {
-        k[i] = kp[i] + kq[i] - kr[i];
+        k[i] = k1[i] + k2[i] - k3[i];
     }
 
     //Translate into first BZ
@@ -86,14 +86,14 @@ double HFStability::HEG::two_electron_2d(double kp[], double kq[], double kr[])
     const double tolerance = 10E-10;
     double norm = 0.0;
     for (int i = 0; i < ndim; ++i) {
-        norm += (kp[i] - kr[i]) * (kp[i] - kr[i]);
+        norm += (k1[i] - k3[i]) * (k1[i] - k3[i]);
     }
 
     //avoid singularities    
     if (norm < tolerance){
         return 0.0;
     }
-    return 2.0 * PI    / (vol * sqrt(norm));
+    return 2.0 * PI / (vol * sqrt(norm));
 }
 
 double HFStability::HEG::davidson_algorithm(

### 2016-08-11 source/stability.h

@@ -9,7 +9,7 @@ namespace HFStability {
 	class HEG {
 	public:
 		//Attributes
-		double  bzone_length, vol, rs, kf;
+		double  bzone_length, vol, rs, kf, fermi_energy;
 		long    Nocc, Nvir, Nexc, N_elec, ndim, Nk;
 		arma::mat  states;
 		arma::umat excitations;

### 2016-08-12 source/HFStability.pyx
Fixed the numerical expression for energies in 2D. Fixed the corresponding equations in the summary sheet.

@@ -82,12 +82,12 @@ cdef class PyHEG:
         elif self.ndim == 3:
             self.kf = (9 * np.pi / 4)**(1./3.) * (1. / self.rs) 
 
+
         kmax = 2.0 * self.kf
         self.fermi_energy = 0.5 * self.kf**2
         #brillioun zone is from - pi/a .. pi/a
         self.bzone_length =  2.0 * kmax
         direct_length = self.bzone_length / (2.0 * np.pi)
-        self.vol = direct_length ** (self.ndim)
 
         # states is list of tuples each of length ndim containing the 
         # coordinates in k-space of each state
@@ -109,9 +109,13 @@ cdef class PyHEG:
         self.states = np.asarray(states)
         self.occ_states = np.asarray(occ_states, dtype=np.uint64)
         self.vir_states = np.asarray(vir_states, dtype=np.uint64)
-
         #RHF ONLY
         self.N_elec = 2 * self.Nocc
+
+        #self.vol = direct_length ** (self.ndim)
+        #2D ONLY OK 
+        self.vol = self.N_elec *np.pi * (self.rs**2)
+
 
     #Class methods
     def two_electron_3d(self, i1, i2, i3, i4):

### 2016-09-16 source/HFStability.pyx
Added cython functionality for energies, will convert to cython

@@ -1,17 +1,20 @@
+# cython: profile=False
+# cython: boundscheck=False
+# cython: wraparound=False
 ################################################################################
 #                                   C++ Land is Here 
 ################################################################################
 from libcpp cimport bool
+from libc.math cimport sqrt
 import itertools
 import math
 from scipy import special as sp
 import numpy as np
 cimport numpy as np
+cimport cython
+
 include "cyarma.pyx"
 include "general_methods.pyx" #functions prepended with gm_
-
-cdef extern from "stdint.h" nogil:
-    ctypedef unsigned long long uint64_t
 	
 #C++ class
 #Note only methods/attributes that want python access need to be here.
@@ -21,13 +24,79 @@ cdef extern from "stability.h" namespace "HFStability":
         #Attributes
         double bzone_length, vol, rs, kf, kmax, fermi_energy
         double two_e_const, deltaK
-        uint64_t Nocc, Nvir, Nexc, N_elec, ndim, Nk
+        long long unsigned int Nocc, Nvir, Nexc, N_elec, ndim, Nk
         vec  occ_energies, vir_energies, exc_energies, kgrid
         umat occ_states, vir_states, excitations, 
 
         #Methods
         void calc_energy_wrap(bool) # True = vir, else = occ 
         void calc_exc_energy()
+
+cdef cppclass test:
+    test() except +
+    np.float64_t x
+
+
+    double func(double y):
+        return 2.0 * y
+
+cdef c_en(np.ndarray[np.uint64_t, ndim=2] occ, np.ndarray[np.float64_t, ndim=1] kgrid, int ndim, 
+          np.float64_t two_e_const, np.float64_t kmax):
+    cdef int N = len(occ)
+    cdef np.ndarray energies = np.zeros(N, dtype=np.float64)
+    cdef int i, j 
+    cdef np.float64_t kin
+    
+    for i in range(0,N):
+        kin = 0.0
+        for j in range(ndim):
+            kin += kgrid[occ[i,j]] * kgrid[occ[i,j]]
+        energies[i] = 0.5 * kin + c_exch(occ, kgrid, ndim, i, two_e_const, kmax) #kinetic + exch
+    return energies
+    
[…]

### 2016-09-16 source/stability.cpp

@@ -128,17 +128,18 @@ double HFStability::HEG::two_electron_3d(double k1[], double k2[]) {
 }
 
 void HFStability::HEG::get_vir_states_inv_2d() {
-    arma::umat vir_states_inv(Nexc)
+//arma::umat vir_states_inv(3)
     for (arma::uword i = 0; i < Nvir; ++i) {
-        
+        int x = 0;
     }
 }
 
-arma::uword HFStability::HEG::get_k_to_idx(k[]) {
+arma::uword HFStability::HEG::get_k_to_idx(double k[]) {
     
     for (arma::uword i = 0; i < Nexc; ++i) { 
-    
-
+        int k = 1;
+    }
+    return 3.0;
 }
 
 arma::vec& HFStability::HEG::mat_vec_prod_2d(arma::vec v) {
@@ -164,11 +165,15 @@ arma::vec& HFStability::HEG::mat_vec_prod_2d(arma::vec v) {
             double kb_B[2] = { (ki[0] + kj[0] - ka[0]), (ki[1] + kj[1] - ka[1]) };
             // virtual orbital index, k_to_idx needs to first find indices of kgrid, then do an inverse
             // map of vir_states
-            arma::uword b_A = k_to_idx(kb_A);
-            arma::uword b_B = k_to_idx(kb_B);
-            // excitations index, needed to know matrix location; A[s,t]
-            arma::uword t_A = inverse_exc_map(j, b_A);
-            arma::uword t_B = inverse_exc_map(j, b_A);
+            arma::uword b_A = 1;
+            arma::uword b_B = 1;
+            arma::uword t_A = 1;
+            arma::uword t_B = 1;
+//            arma::uword b_A = k_to_idx(kb_A);
+//            arma::uword b_B = k_to_idx(kb_B);
+//            // excitations index, needed to know matrix location; A[s,t]
+//            arma::uword t_A = inverse_exc_map(j, b_A);
+//            arma::uword t_B = inverse_exc_map(j, b_A);
 
             Mv(s) += two_electron_2d(kj, ka) * v(t_B + Nexc); // B is offset by Nexc because of the layout of H
             if (s == t_A) { // if diagonal element of A

### 2016-09-16 source/stability.h

@@ -23,6 +23,8 @@ namespace HFStability {
                 void   calc_energies_2d(arma::umat&, arma::vec&);
                 double two_electron_2d(double[], double[]);
                 double exchange_2d(arma::umat&, arma::uword);
+                arma::uword get_k_to_idx(double[]);
+                void get_vir_states_inv_2d();
                 //3d
                 void   calc_energies_3d(arma::umat&, arma::vec&);
                 double exchange_3d(arma::umat&, arma::uword);

### 2016-09-27 sourcefiles/stability.cpp
Edit MVM a bit, still needs work

@@ -341,29 +341,22 @@ arma::vec HFStability::HEG::mat_vec_prod(arma::vec v) {
     // orbital index and the  _A means this corresponds to the A matrix
 
     arma::vec Mv(Nexc*2.0, arma::fill::zeros);  // matrix vector product
-      // This outer loop fills Mv[0..Nexc]
+    // This outer loop fills Mv[0..Nexc]
     for (arma::uword s = 0; s < Nexc; ++s) {
         // s, i and a are the same for A and B (Seeger/Pople notation)
-        arma::uword i = excitations(s, 0);
-        arma::uword a = excitations(s, 1);
-        arma::vec ki(ndim);
-        arma::vec ka(ndim);
+        arma::uword i = excitations(s, 0), a = excitations(s, 1);
+        arma::vec ki(ndim), ka(ndim);
         ki = occ_idx_to_k(i);
         ka = vir_idx_to_k(a);
         for (arma::uword j = 0; j < Nocc; ++j) {
             // j is the same for A and B
-            arma::vec kj(ndim);
-            arma::vec kb_A(ndim);
-            arma::vec kb_B(ndim);
-
-            for (int idx = 0; idx < 1; ++idx) {
-                kj[idx] = kgrid(occ_states(j, idx));
-            }
+            arma::vec kj(ndim), kb_A(ndim), kb_B(ndim);
+            kj = occ_idx_to_k(j);
+    
             // find the momentum conserving virtual orbital
             // A and B matrices have different momentum conservation rules
             // Exciting only in one dimension, the rest are unchanged
-
-            kb_A[0] = kj[0] + (ka[0] - ki[0]);
+            kb_A[0] = ka[0] + kj[0] - ki[0];
             kb_B[0] = ki[0] + kj[0] - ka[0];
             for (int idx = 1; idx < ndim; ++idx) {
                 kb_A[idx] = kj[idx];
@@ -371,74 +364,20 @@ arma::vec HFStability::HEG::mat_vec_prod(arma::vec v) {
             }
             to_first_BZ(kb_A);
             to_first_BZ(kb_B);
-            std::cout << "ki = " << std::endl;
-            ki.print();
-            std::cout << "ka = " << std::endl;
-            ka.print();
-            std::cout << "kj = " << std::endl;
-            kj.print();
-            std::cout << "kb_A = " << std::endl;
-            kb_A.print();
-            std::cout << "kb_B = " << std::endl;
-            kb_B.print();
-
-
[…]

### 2016-09-29 presentations/GroupMeeting_Fall2016.tex
Fixed plot and started presentation

\documentclass[10pt]{beamer}

\usetheme{metropolis}
\usepackage{appendixnumberbeamer}

\usepackage{booktabs}
\usepackage[scale=2]{ccicons}

\usepackage{pgfplots}
\usepgfplotslibrary{dateplot}

\usepackage{xspace}
\newcommand{\themename}{\textbf{\textsc{metropolis}}\xspace}

\title{Hartree-Fock Stability}
\subtitle{Applications to the Homogeneous Electron Gas}
\date{\today}
\author{Evan Curtin}
\institute{University of Illinois at Urbana-Champaign}
% \titlegraphic{\hfill\includegraphics[height=1.5cm]{logo.pdf}}

\begin{document}

\maketitle

\begin{frame}{Table of contents}
  \setbeamertemplate{section in toc}[sections numbered]
  \tableofcontents[hideallsubsections]
\end{frame}

\section{Background Information}

\begin{frame}[fragile]{Levels of Hartree-Fock Theory}
	\begin{center}
		\begin{tabular}{ | c | c | c | c |}
			\hline
			 Method & Spinorbital & DoF & Eigenfunction of\\ 
			\hline

			Restricted \rule{0pt}{7ex} & 
			\begin{tabular}{c@{}c@{}} 
			$\chi_j^\alpha(\vec{r},\sigma) = 
			\sum\limits_{i=1}^{N} c_{ij}\phi_i\left(\vec{r \,}\right)\alpha(\sigma)$
			\\ \rule{0pt}{4ex} 
			$\chi_j^\beta(\vec{r},\sigma) =
			\sum\limits_{i=1}^{N} c_{ij}\phi_i\left(\vec{r \,}\right)\beta(\sigma)$
			\end{tabular}
			& N/2 
			& $\hat{S}^2$, $\hat{S}_z$
			\\ [5ex] \hline

			Unrestricted \rule{0pt}{7ex} &
			\begin{tabular}{c@{}c@{}}  
			$\chi_j^\alpha(\vec{r},\sigma) = \sum\limits_{i=1}^{N} 
			c_{ij}^\alpha\phi_i(\vec{r \,}) \alpha(\sigma)$
			\\ \rule{0pt}{4ex}
			$\chi_j^\beta(\vec{r},\sigma) = \sum\limits_{i=1}^{N} 
			c_{ij}^\beta\phi_i(\vec{r \,}) \beta(\sigma)$
			\end{tabular}
			& N & $\hat{S}_z$ \\ [5ex]
			\hline

			General \rule{0pt}{7ex}&
			\begin{tabular}{r@{}r@{}}  
				$\chi_j(\vec{r},\sigma) = \sum\limits_{i=1}^{N} [
				c_{ij}^\alpha\phi_i\left(\vec{r \,}\right) \alpha(\sigma) $
				\\ \rule{0pt}{4ex}
				$+c_{ij}^\beta \phi_i(\vec{r \,}) \beta(\sigma)]  $
			\end{tabular} 
			& 2N & Neither \\ [5ex]

			\hline
		\end{tabular}
	\end{center}

\end{frame}
\begin{frame}[fragile]{Restricted Minimization}
	\includegraphics[width=0.7\linewidth]{../images/pes.jpeg}
\end{frame}

\section{Titleformats}

\begin{frame}{Metropolis titleformats}
	\themename supports 4 different titleformats:
	\begin{itemize}
		\item Regular
		\item \textsc{Smallcaps}
		\item \textsc{allsmallcaps}
		\item ALLCAPS
	\end{itemize}
	They can either be set at once for every title type or individually.
\end{frame}

{
    \metroset{titleformat frame=smallcaps}
\begin{frame}{Small caps}
	This frame uses the \texttt{smallcaps} titleformat.

	\begin{alertblock}{Potential Problems}
		Be aware, that not every font supports small caps. If for example you typeset your presentation with pdfTeX and the Computer Modern Sans Serif font, every text in smallcaps will be typeset with the Computer Modern Serif font instead.
	\end{alertblock}
\end{frame}
}

{
\metroset{titleformat frame=allsmallcaps}
\begin{frame}{All small caps}
	This frame uses the \texttt{allsmallcaps} titleformat.

	\begin{alertblock}{Potential problems}
		As this titleformat also uses smallcaps you face the same problems as with the \texttt{smallcaps} titleformat. Additionally this format can cause some other problems. Please refer to the documentation if you consider using it.

		As a rule of thumb: Just use it for plaintext-only titles.
	\end{alertblock}
\end{frame}
}

{
\metroset{titleformat frame=allcaps}
\begin{frame}{All caps}
	This frame uses the \texttt{allcaps} titleformat.

	\begin{alertblock}{Potential Problems}
		This titleformat is not as problematic as the \texttt{allsmallcaps} format, but basically suffers from the same deficiencies. So please have a look at the documentation if you want to use it.
	\end{alertblock}
\end{frame}
}

\section{Elements}

\begin{frame}[fragile]{Typography}
      \begin{verbatim}The theme provides sensible defaults to
\emph{emphasize} text, \alert{accent} parts
or show \textbf{bold} results.\end{verbatim}

  \begin{center}becomes\end{center}

  The theme provides sensible defaults to \emph{emphasize} text,
  \alert{accent} parts or show \textbf{bold} results.
\end{frame}

\begin{frame}{Font feature test}
  \begin{itemize}
    \item Regular
    \item \textit{Italic}
    \item \textsc{SmallCaps}
    \item \textbf{Bold}
    \item \textbf{\textit{Bold Italic}}
    \item \textbf{\textsc{Bold SmallCaps}}
    \item \texttt{Monospace}
    \item \texttt{\textit{Monospace Italic}}
    \item \texttt{\textbf{Monospace Bold}}
    \item \texttt{\textbf{\textit{Monospace Bold Italic}}}
  \end{itemize}
\end{frame}

\begin{frame}{Lists}
  \begin{columns}[T,onlytextwidth]
    \column{0.33\textwidth}
      Items
      \begin{itemize}
        \item Milk \item Eggs \item Potatos
      \end{itemize}

    \column{0.33\textwidth}
      Enumerations
      \begin{enumerate}
        \item First, \item Second and \item Last.
      \end{enumerate}

    \column{0.33\textwidth}
      Descriptions
      \begin{description}
        \item[PowerPoint] Meeh. \item[Beamer] Yeeeha.
      \end{description}
  \end{columns}
\end{frame}
\begin{frame}{Animation}
  \begin{itemize}[<+- | alert@+>]
    \item \alert<4>{This is\only<4>{ really} important}
    \item Now this
    \item And now this
  \end{itemize}
\end{frame}
\begin{frame}{Figures}
  \begin{figure}
    \newcounter{density}
    \setcounter{density}{20}
    \begin{tikzpicture}
      \def\couleur{alerted text.fg}
      \path[coordinate] (0,0)  coordinate(A)
                  ++( 90:5cm) coordinate(B)
                  ++(0:5cm) coordinate(C)
                  ++(-90:5cm) coordinate(D);
      \draw[fill=\couleur!\thedensity] (A) -- (B) -- (C) --(D) -- cycle;
      \foreach \x in {1,...,40}{%
          \pgfmathsetcounter{density}{\thedensity+20}
          \setcounter{density}{\thedensity}
          \path[coordinate] coordinate(X) at (A){};
          \path[coordinate] (A) -- (B) coordinate[pos=.10](A)
                              -- (C) coordinate[pos=.10](B)
                              -- (D) coordinate[pos=.10](C)
                              -- (X) coordinate[pos=.10](D);
          \draw[fill=\couleur!\thedensity] (A)--(B)--(C)-- (D) -- cycle;
      }
    \end{tikzpicture}
    \caption{Rotated square from
    \href{http://www.texample.net/tikz/examples/rotated-polygons/}{texample.net}.}
  \end{figure}
\end{frame}
\begin{frame}{Tables}
  \begin{table}
    \caption{Largest cities in the world (source: Wikipedia)}
    \begin{tabular}{lr}
      \toprule
      City & Population\\
      \midrule
      Mexico City & 20,116,842\\
      Shanghai & 19,210,000\\
      Peking & 15,796,450\\
      Istanbul & 14,160,467\\
      \bottomrule
    \end{tabular}
  \end{table}
\end{frame}
\begin{frame}{Blocks}
  Three different block environments are pre-defined and may be styled with an
  optional background color.

  \begin{columns}[T,onlytextwidth]
    \column{0.5\textwidth}
      \begin{block}{Default}
        Block content.
      \end{block}

      \begin{alertblock}{Alert}
        Block content.
      \end{alertblock}

      \begin{exampleblock}{Example}
        Block content.
      \end{exampleblock}

    \column{0.5\textwidth}

      \metroset{block=fill}

      \begin{block}{Default}
        Block content.
      \end{block}

      \begin{alertblock}{Alert}
        Block content.
      \end{alertblock}

      \begin{exampleblock}{Example}
        Block content.
      \end{exampleblock}

  \end{columns}
\end{frame}
\begin{frame}{Math}
  \begin{equation*}
    e = \lim_{n\to \infty} \left(1 + \frac{1}{n}\right)^n
  \end{equation*}
\end{frame}
\begin{frame}{Line plots}
  \begin{figure}
    \begin{tikzpicture}
      \begin{axis}[
        mlineplot,
        width=0.9\textwidth,
        height=6cm,
      ]

        \addplot {sin(deg(x))};
        \addplot+[samples=100] {sin(deg(2*x))};

      \end{axis}
    \end{tikzpicture}
  \end{figure}
\end{frame}
\begin{frame}{Bar charts}
  \begin{figure}
    \begin{tikzpicture}
      \begin{axis}[
        mbarplot,
        xlabel={Foo},
        ylabel={Bar},
        width=0.9\textwidth,
        height=6cm,
      ]

      \addplot plot coordinates {(1, 20) (2, 25) (3, 22.4) (4, 12.4)};
      \addplot plot coordinates {(1, 18) (2, 24) (3, 23.5) (4, 13.2)};
      \addplot plot coordinates {(1, 10) (2, 19) (3, 25) (4, 15.2)};

      \legend{lorem, ipsum, dolor}

      \end{axis}
    \end{tikzpicture}
  \end{figure}
\end{frame}
\begin{frame}{Quotes}
  \begin{quote}
    Veni, Vidi, Vici
  \end{quote}
\end{frame}

{%
\setbeamertemplate{frame footer}{My custom footer}
\begin{frame}[fragile]{Frame footer}
    \themename defines a custom beamer template to add a text to the footer. It can be set via
    \begin{verbatim}\setbeamertemplate{frame footer}{My custom footer}\end{verbatim}
\end{frame}
}

\begin{frame}{References}
  Some references to showcase [allowframebreaks] \cite{knuth92,ConcreteMath,Simpson,Er01,greenwade93}
\end{frame}

\section{Conclusion}

\begin{frame}{Summary}

  Get the source of this theme and the demo presentation from

  \begin{center}\url{github.com/matze/mtheme}\end{center}

  The theme \emph{itself} is licensed under a
  \href{http://creativecommons.org/licenses/by-sa/4.0/}{Creative Commons
  Attribution-ShareAlike 4.0 International License}.

  \begin{center}\ccbysa\end{center}

\end{frame}

\begin{frame}[standout]
  Questions?
\end{frame}

\appendix

\begin{frame}[fragile]{Backup slides}
  Sometimes, it is useful to add slides at the end of your presentation to
  refer to during audience questions.

  The best way to do this is to include the \verb|appendixnumberbeamer|
  package in your preamble and call \verb|\appendix| before your backup slides.

  \themename will automatically turn off slide numbering and progress bars for
  slides in the appendix.
\end{frame}

\begin{frame}[allowframebreaks]{References}

  \bibliography{demo}
  \bibliographystyle{abbrv}

\end{frame}

\end{document}

### 2016-09-30 presentations/GroupMeeting_Fall2016.tex
Added images, image generator and a unimportant things. Also added group meeting stuff

@@
 \usepackage{appendixnumberbeamer}
-
+\usepackage{graphicx}
 \usepackage{booktabs}
@@
 \institute{University of Illinois at Urbana-Champaign}
-% \titlegraphic{\hfill\includegraphics[height=1.5cm]{logo.pdf}}
+\titlegraphic{\hfill\includegraphics[height=1.5cm]{../images/imark_bold.eps}}
 
@@
 			& 2N & Neither \\ [5ex]
-
 			\hline			
@@
 	\end{center}
+\end{frame}
 
+\begin{frame}[fragile]{Restricted Minimization}
+	\begin{itemize}
+		\item<1-> Hartee-Fock SCF guarantees only stationary energy w.r.t. change in orbitals
+		\item<1-> The solution may be a maximum, minimum or saddle point
+		\begin{itemize}
+			\item<2-> \emph{Within the constrained space}
+		\end{itemize}
+	\end{itemize}
+	\begin{center}
+		\includegraphics[width=0.5\textwidth, trim={3cm, 2cm, 3cm, 2cm}, clip]{../images/1d_extrema.pdf}
+	\end{center}
 \end{frame}
+
 \begin{frame}[fragile]{Restricted Minimization}
-	\includegraphics[width=0.7\linewidth]{../images/pes.jpeg}
+	\includegraphics[width=0.5\linewidth, trim={7cm, 2cm, 7cm, 3cm}, clip]{../images/const_opt_globalmin.jpeg}
+\end{frame}
+
+\begin{frame}[fragile]{Restricted Minimization}
+	\includegraphics[width=0.5\linewidth, trim={7cm, 2cm, 7cm, 3cm}, clip]{../images/const_opt_saddle.jpeg}
+\end{frame}
+
+\begin{frame}[fragile]{Restricted Minimization}
+	\includegraphics[width=0.5\linewidth, trim={7cm, 2cm, 7cm, 3cm}, clip]{../images/const_opt_nonstationary.jpeg}
 \end{frame}

### 2016-11-03 presentations/GroupMeeting_Fall2016.tex
changed presentation a little
Changed initial guess to be 1/diags type of thing It's a vast improvement

@@
 \usetheme{metropolis}
+\useoutertheme{metropolis}
+\useinnertheme{metropolis}
+\usefonttheme{metropolis}
+%\usecolortheme{seahorse}   % or your preferred color theme
 \usepackage{appendixnumberbeamer}
@@
 \usepackage[scale=2]{ccicons}
+\usepackage{xspace}
+\usepackage[justification=centering]{caption}
 
-\usepackage{pgfplots}
-\usepgfplotslibrary{dateplot}
-
-\usepackage{xspace}
-\newcommand{\themename}{\textbf{\textsc{metropolis}}\xspace}
+\usepackage[version=3]{mhchem}
+\definecolor{darkgreen}{RGB}{30, 133, 12}
+\definecolor{lightgray}{gray}{0.9}
+\renewcommand{\arraystretch}{1.2}
 
 \title{Hartree-Fock Stability}
-\subtitle{Applications to the Homogeneous Electron Gas}
+\subtitle{Applications to the Homogeneous Electron Gas \\ And Implications in Electron Correlation}
 \date{\today}
@@
 
+{%
+\setbeamertemplate{frame footer}{Seeger, R.; Pople, J. A. J. Chem. Phys. 1977, 66 (7), 3045.
+}
 \begin{frame}[fragile]{Levels of Hartree-Fock Theory}
@@
 			\hline
-			 Method & Spinorbital & DoF & Eigenfunction of\\ 
+			 \textbf{Method} & \textbf{Spinorbital} & \textbf{DoF} & \textbf{Eigenfunction of}\\ 
 			\hline
@@
 
+{%+
+\setbeamertemplate{frame footer}{}
+
 \begin{frame}[fragile]{Restricted Minimization}
@@
 		\begin{itemize}
-			\item<2-> \emph{Within the constrained space}
+			\item<2->[] \begin{alertblock}{Within the Constrained Space} \end{alertblock}
 		\end{itemize}
@@
 
-\begin{frame}[fragile]{Restricted Minimization}
-	\includegraphics[width=0.5\linewidth, trim={7cm, 2cm, 7cm, 3cm}, clip]{../images/const_opt_globalmin.jpeg}
+\begin{frame}{Restricted Minimization}
+	\begin{columns}[c] % align columns
+		\begin{column}{.48\textwidth}
+			\begin{itemize}[<+->]
+				\item {Restricted minima may correspond to absolute minima}
+				\item {Restricted minima may correspond to absolute maxima}
+				\item {Restricted minima may be nonstationary}
+			\end{itemize}				
+		\end{column}
+		\hfill
+		\begin{column}{0.48\textwidth}
+		    \begin{overprint}
+			    \onslide<1>\includegraphics[width=0.9\linewidth, trim={7cm, 2cm, 7cm, 3cm}, clip]{../images/const_opt_globalmin.jpeg}
+				\onslide<2>\includegraphics[width=0.9\linewidth, trim={7cm, 1cm, 7cm, 1cm}, clip]{../images/const_opt_saddle.jpeg}
+				\onslide<3>\includegraphics[width=0.9\linewidth, trim={7cm, 2cm, 7cm, 3cm}, clip]{../images/const_opt_nonstationary.jpeg}
+			\end{overprint}
+		\end{column}	
+	\end{columns}
 \end{frame}
 
-\begin{frame}[fragile]{Restricted Minimization}
-	\includegraphics[width=0.5\linewidth, trim={7cm, 2cm, 7cm, 3cm}, clip]{../images/const_opt_saddle.jpeg}
-\end{frame}
+\section{Hartree-Fock Stability}
 
-\begin{frame}[fragile]{Restricted Minimization}
-	\includegraphics[width=0.5\linewidth, trim={7cm, 2cm, 7cm, 3cm}, clip]{../images/const_opt_nonstationary.jpeg}
-\end{frame}
+{%
+	\setbeamertemplate{frame footer}{Thouless, D. J. Nucl. Phys. 1960, 21, 225–232.}
+\begin{frame}{Outline}
+	\begin{columns}[c] % align columns
+		\begin{column}{.48\textwidth}
+			\begin{itemize}
+				\item {Inspired by biological evolution}
+				\item {Evolve a population over generations}
+				\item {Survival of the fittest}
+				\item {Requirements:}
+				\begin{itemize}
+					\item {Represent individuals as vector}
+					\item {Fitness function}
+				\end{itemize}
+				\item{$v = \left(\begin{smallmatrix}
+					x_1 & y_1 & z_1 & x_2 &  y_2 & z_2 &
+					... & x_N & y_N & z_N
+					\end{smallmatrix}\right)$}
+				\item{$F = \frac{E_{max} - E}{E_{max} - E_{min}}$}
+			\end{itemize}
 
-\section{Titleformats}
+		\end{column}
+		\hfill
+		\begin{column}{0.48\textwidth}
 
-\begin{frame}{Metropolis titleformats}
-	\themename supports 4 different titleformats:
-	\begin{itemize}
-		\item Regular
-		\item \textsc{Smallcaps}
-		\item \textsc{allsmallcaps}
-		\item ALLCAPS
-	\end{itemize}
-	They can either be set at once for every title type or individually.
-\end{frame}
-
-{
-    \metroset{titleformat frame=smallcaps}
-\begin{frame}{Small caps}
-	This frame uses the \texttt{smallcaps} titleformat.
-
-	\begin{alertblock}{Potential Problems}
-		Be aware, that not every font supports small caps.
-If for example you typeset your presentation with pdfTeX and the Computer Modern Sans Serif font, every text in smallcaps will be typeset with the Computer Modern Serif font instead.
-	\end{alertblock}
+		\end{column}	
+	\end{columns}
 \end{frame}
@@
 
-{
-\metroset{titleformat frame=allsmallcaps}
-\begin{frame}{All small caps}
-	This frame uses the \texttt{allsmallcaps} titleformat.
+{%
+\setbeamertemplate{frame footer}{1. Supady, A.; Blum, V.; Baldauf, C. J. Chem. Inf. Model. 2015, 55 (11), 2338–2348.
 
-	\begin{alertblock}{Potential problems}
-		As this titleformat also uses smallcaps you face the same problems as with the \texttt{smallcaps} titleformat.
-Additionally this format can cause some other problems.
-Please refer to the documentation if you consider using it.
-
-		As a rule of thumb: Just use it for plaintext-only titles.
-	\end{alertblock}
+2. http://www.chemspider.com/Chemical-Structure.2298795.html}
+\begin{frame}{From Structure to Vector}
+	\begin{columns}[c] % align columns
+		\begin{column}{.48\textwidth}
+			\begin{itemize}
+				\item<1-> {Several Ways to Define Structure
+					\begin{itemize}
+						\item[] {Cartesian}
+						\item[] {Internal Coordinates (bond length, angle ...)}
+						\item[] {SMILES, InChI}
+					\end{itemize}
+				}
+				\item<2-> {InChI$^2$= 1S/C8H16/c1-5-7(3)8(4)6-2/h5-6H2,1-4H3/b8-7-}
+				\item<only@3> {Equivalent in theory}
+				\item<only@4> {Equivalent \alert{\textbf{in theory}}}
+			\end{itemize}			
+		\end{column}
+		\hfill
+		\begin{column}{0.48\textwidth}
+			1
+		\end{column}	
+	\end{columns}
 \end{frame}
@@
 
-{
-\metroset{titleformat frame=allcaps}
-\begin{frame}{All caps}
-	This frame uses the \texttt{allcaps} titleformat.
+\begin{frame}{Selecting Parents}
+	\begin{columns}[c] % align columns
+		\begin{column}{.48\textwidth}
+			\begin{itemize}[<+->]
+				\item {Several methods are common}
+				\item {Reinforce good characteristics}
+				\item {Still give losers a chance}
+				\item {'Breed' pairs of winners}
+				\item {'Roulette Wheel' Method}
+			\end{itemize}				
+		\end{column}
+		\hfill
+		\begin{column}{0.48\textwidth}
 
-	\begin{alertblock}{Potential Problems}
-		This titleformat is not as problematic as the \texttt{allsmallcaps} format, but basically suffers from the same deficiencies. So please have a look at the documentation if you want to use it.
-	\end{alertblock}
+		\end{column}	
+	\end{columns}
+\end{frame}
+
+{%
+\setbeamertemplate{frame footer}{http://www.turingfinance.com/computational-finance
+
+-updates-ieee-world-congress-computational-intelligence}
+\begin{frame}{The Next Generation}
+	\begin{itemize}[<+->]
+
+		\item[]{~\\Crossover distinguishes this from Monte Carlo}
+	\end{itemize}
 \end{frame}
@@
 
-\section{Elements}
+\begin{frame}{The Whole Algorithm}
+	\begin{columns}[c] % align columns
+		\begin{column}{.48\textwidth}
+			\begin{itemize}[<+->]
+				\item[1.] {Generate N random, sensible geometries}
+				\item[2.] {Add each to blacklist}
+				\item[3.] {Optimize each geometry}
+				\item[4.] {Select Parents}
+				\item[5.] {Crossover \& Mutate into sensible geometry}
+				\item[6.] {Add Children to population}
+				\item[7.] {Remove High energy individuals}
+				\item[8.] {If converged:}
+				\begin{itemize}
+					\item{Done!}
+				\end{itemize}
+				\item[] {Otherwise:}
+				\begin{itemize}
+					\item{Go to 2}
+				\end{itemize}
+			\end{itemize}
+		\end{column}
+		\hfill
+		\begin{column}{0.48\textwidth}
+			\onslide<11>\begin{itemize}
+				\medskip
+				\item[]{
 
-\begin{frame}[fragile]{Typography}
-      \begin{verbatim}The theme provides sensible defaults to
-\emph{emphasize} text, \alert{accent} parts
-or show \textbf{bold} results.\end{verbatim}
+				}
+			    \item[]{
 
-  \begin{center}becomes\end{center}
-
-  The theme provides sensible defaults to \emph{emphasize} text,
-  \alert{accent} parts or show \textbf{bold} results.
+				}
+			\end{itemize}
+		\end{column}	
+	\end{columns}
 \end{frame}
 
-\begin{frame}{Font feature test}
-  \begin{itemize}
-    \item Regular
-    \item \textit{Italic}
-    \item \textsc{SmallCaps}
-    \item \textbf{Bold}
-    \item \textbf{\textit{Bold Italic}}
-    \item \textbf{\textsc{Bold SmallCaps}}
-    \item \texttt{Monospace}
-    \item \texttt{\textit{Monospace Italic}}
-    \item \texttt{\textbf{Monospace Bold}}
-    \item \texttt{\textbf{\textit{Monospace Bold Italic}}}
-  \end{itemize}
-\end{frame}
-
-\begin{frame}{Lists}
-  \begin{columns}[T,onlytextwidth]
-    \column{0.33\textwidth}
-      Items
-      \begin{itemize}
-        \item Milk \item Eggs \item Potatos
-      \end{itemize}
-
-    \column{0.33\textwidth}
-      Enumerations
-      \begin{enumerate}
-        \item First, \item Second and \item Last.
-      \end{enumerate}
-
-    \column{0.33\textwidth}
-      Descriptions
-      \begin{description}
-        \item[PowerPoint] Meeh. \item[Beamer] Yeeeha.
-      \end{description}
-  \end{columns}
-\end{frame}
-\begin{frame}{Animation}
-  \begin{itemize}[<+- | alert@+>]
-    \item \alert<4>{This is\only<4>{ really} important}
-    \item Now this
-    \item And now this
-  \end{itemize}
-\end{frame}
-\begin{frame}{Figures}
-  \begin{figure}
-    \newcounter{density}
-    \setcounter{density}{20}
-    \begin{tikzpicture}
-      \def\couleur{alerted text.fg}
-      \path[coordinate] (0,0)  coordinate(A)
-                  ++( 90:5cm) coordinate(B)
-                  ++(0:5cm) coordinate(C)
-                  ++(-90:5cm) coordinate(D);
-      \draw[fill=\couleur!\thedensity] (A) -- (B) -- (C) --(D) -- cycle;
-      \foreach \x in {1,...,40}{%
-          \pgfmathsetcounter{density}{\thedensity+20}
-          \setcounter{density}{\thedensity}
-          \path[coordinate] coordinate(X) at (A){};
-          \path[coordinate] (A) -- (B) coordinate[pos=.10](A)
-                              -- (C) coordinate[pos=.10](B)
-                              -- (D) coordinate[pos=.10](C)
-                              -- (X) coordinate[pos=.10](D);
-          \draw[fill=\couleur!\thedensity] (A)--(B)--(C)-- (D) -- cycle;
-      }
-    \end{tikzpicture}
-    \caption{Rotated square from
-    \href{http://www.texample.net/tikz/examples/rotated-polygons/}{texample.net}.}
-  \end{figure}
-\end{frame}
-\begin{frame}{Tables}
-  \begin{table}
-    \caption{Largest cities in the world (source: Wikipedia)}
-    \begin{tabular}{lr}
-      \toprule
-      City & Population\\
-      \midrule
-      Mexico City & 20,116,842\\
-      Shanghai & 19,210,000\\
-      Peking & 15,796,450\\
-      Istanbul & 14,160,467\\
-      \bottomrule
-    \end{tabular}
-  \end{table}
-\end{frame}
-\begin{frame}{Blocks}
-  Three different block environments are pre-defined and may be styled with an
-  optional background color.
-
-  \begin{columns}[T,onlytextwidth]
-    \column{0.5\textwidth}
-      \begin{block}{Default}
-        Block content.
-      \end{block}
-
-      \begin{alertblock}{Alert}
-        Block content.
-      \end{alertblock}
-
-      \begin{exampleblock}{Example}
-        Block content.
-      \end{exampleblock}
-
-    \column{0.5\textwidth}
-
-      \metroset{block=fill}
-
-      \begin{block}{Default}
-        Block content.
-      \end{block}
-
-      \begin{alertblock}{Alert}
-        Block content.
-      \end{alertblock}
-
-      \begin{exampleblock}{Example}
-        Block content.
-      \end{exampleblock}
-
-  \end{columns}
-\end{frame}
-\begin{frame}{Math}
-  \begin{equation*}
-    e = \lim_{n\to \infty} \left(1 + \frac{1}{n}\right)^n
-  \end{equation*}
-\end{frame}
-\begin{frame}{Line plots}
-  \begin{figure}
-    \begin{tikzpicture}
-      \begin{axis}[
-        mlineplot,
-        width=0.9\textwidth,
-        height=6cm,
-      ]
-
-        \addplot {sin(deg(x))};
-        \addplot+[samples=100] {sin(deg(2*x))};
-
-      \end{axis}
-    \end{tikzpicture}
-  \end{figure}
-\end{frame}
-\begin{frame}{Bar charts}
-  \begin{figure}
-    \begin{tikzpicture}
-      \begin{axis}[
-        mbarplot,
-        xlabel={Foo},
-        ylabel={Bar},
-        width=0.9\textwidth,
-        height=6cm,
-      ]
-
-      \addplot plot coordinates {(1, 20) (2, 25) (3, 22.4) (4, 12.4)};
-      \addplot plot coordinates {(1, 18) (2, 24) (3, 23.5) (4, 13.2)};
-      \addplot plot coordinates {(1, 10) (2, 19) (3, 25) (4, 15.2)};
-
-      \legend{lorem, ipsum, dolor}
-
-      \end{axis}
-    \end{tikzpicture}
-  \end{figure}
-\end{frame}
-\begin{frame}{Quotes}
-  \begin{quote}
-    Veni, Vidi, Vici
-  \end{quote}
-\end{frame}
+\section{Finding Low Energy Conformers of Dipeptides}
 
 {%
-\setbeamertemplate{frame footer}{My custom footer}
-\begin{frame}[fragile]{Frame footer}
-    \themename defines a custom beamer template to add a text to the footer. It can be set via
-    \begin{verbatim}\setbeamertemplate{frame footer}{My custom footer}\end{verbatim}
+	\setbeamertemplate{frame footer}{Supady, A.; Blum, V.; Baldauf, C. J. Chem. Inf. Model. 2015, 55 (11), 2338–2348.}
+\begin{frame}{Dipeptide Structures}
+
 \end{frame}
@@
 
-\begin{frame}{References}
-  Some references to showcase [allowframebreaks] \cite{knuth92,ConcreteMath,Simpson,Er01,greenwade93}
+{%
+\setbeamertemplate{frame footer}{Supady, A.; Blum, V.; Baldauf, C. J. Chem. Inf. Model. 2015, 55 (11), 2338–2348.
+}
+\begin{frame}{Combinatorics}
+	\begin{columns}[c] % align columns
+		\begin{column}{.4\textwidth}
+			\begin{itemize}
+				\item {GA beats other methods if space is large}
+				\item {Space gets large \textbf{\alert{fast}}}
+			\end{itemize}		
+		\end{column}
+		\hfill
+		\begin{column}{0.6\textwidth}
+
+		\end{column}	
+	\end{columns}
 \end{frame}
+}
 
-\section{Conclusion}
+{%
+\setbeamertemplate{frame footer}{Supady, A.; Blum, V.; Baldauf, C. J. Chem. Inf. Model. 2015, 55 (11), 2338–2348.
+}
+\begin{frame}{Coverage}
+	\begin{columns}[c] % align columns
+		\begin{column}{.4\textwidth}
+			\begin{itemize}
+				\item {Smaller systems are reliably sampled}
+				\item {As \# of conformers increases, miss more and more}
+				\item {Is there a pattern to what is missed?}
+			\end{itemize}		
+		\end{column}
+		\hfill
+		\begin{column}{0.6\textwidth}
 
-\begin{frame}{Summary}
+		\end{column}	
+	\end{columns}
+\end{frame}
+}
 
-  Get the source of this theme and the demo presentation from
+{%
+\setbeamertemplate{frame footer}{Supady, A.; Blum, V.; Baldauf, C. J. Chem. Inf. Model. 2015, 55 (11), 2338–2348.
+}
+\begin{frame}{Coverage}
+	\begin{columns}[c] % align columns
+		\begin{column}{.4\textwidth}
+			\begin{itemize}[<+->]
+				\item {Most misses are very high energy}
+				\item {Algorithm favors low energy areas of the space}
+				\item {Features low in energy are favored and recombined}
+			\end{itemize}		
+		\end{column}
+		\hfill
+		\begin{column}{0.6\textwidth}
 
-  \begin{center}\url{github.com/matze/mtheme}\end{center}
+		\end{column}	
+	\end{columns}
+\end{frame}
+}
 
-  The theme \emph{itself} is licensed under a
-  \href{http://creativecommons.org/licenses/by-sa/4.0/}{Creative Commons
-  Attribution-ShareAlike 4.0 International License}.
+{%
+\setbeamertemplate{frame footer}{Supady, A.; Blum, V.; Baldauf, C. J. Chem. Inf. Model. 2015, 55 (11), 2338–2348.}
+\begin{frame}{Energy Cutoff}
+	\begin{columns}[c] % align columns
+		\begin{column}{.4\textwidth}
+			\begin{itemize}[<+->]
+				\item[] {
 
-  \begin{center}\ccbysa\end{center}
+				}
+				\item {GA is more sensitive to energy cutoff}
+				\item {For finding low energy ensemble, GA outperforms purely stochastic/deterministic method}
+			\end{itemize}		
+		\end{column}
+		\hfill
+		\begin{column}{0.6\textwidth}
 
+		\end{column}	
+	\end{columns}
 \end{frame}
+}
+
+\section{Concluding Remarks}
+
+{%
+\setbeamertemplate{frame footer}{Supady, A.; Blum, V.; Baldauf, C. J. Chem. Inf. Model. 2015, 55 (11), 2338–2348.}
+\begin{frame}{Concluding Remarks}
+	\begin{itemize}[<+->]
+		\item {Finding all the low energy conformers for a molecule is hard}
+		\item {In order to get accurate energies/structures, computationally expensive methods should be employed}
+		\item {These take time, so we want to minimize how many of these we do}
+		\item {The Genetic Algorithm provides a framework for a refined global search}
+		\item {It shines when asked to find a host of low energy solutions}
+		\item {GA wrapper can be interfaced with a variety of electronic structure packages(NWChem, ORCA) and is available under the GNU Lesser General Public License at \url{https://github.com/adrianasupady/fafoom}}
+
+	\end{itemize}
+\end{frame}
+}
 
@@
 
-\begin{frame}[fragile]{Backup slides}
-  Sometimes, it is useful to add slides at the end of your presentation to
-  refer to during audience questions.
-
-  The best way to do this is to include the \verb|appendixnumberbeamer|
-  package in your preamble and call \verb|\appendix| before your backup slides.
-
-  \themename will automatically turn off slide numbering and progress bars for
-  slides in the appendix.
+\begin{frame}[fragile]{Backup slide}
+	\begin{itemize}
+		\item Geometry optimization step makes the algorithm more Lamarckian (Jean Baptiste Larmarck, [1744-1829])
+	\end{itemize}
 \end{frame}
 
-\begin{frame}[allowframebreaks]{References}
+{%
+\setbeamertemplate{frame footer}{(1) Blum, V. et. al., M. Comput. Phys. Commun. 2009, 180 (11), 2175–2196.
 
-  \bibliography{demo}
-  \bibliographystyle{abbrv}
+(2) Supady, A.; Blum, V.; Baldauf, C. J. Chem. Inf. Model. 2015, 55 (11), 2338–2348.
+
+	}
+\begin{frame}[fragile]{Genetic Algorithm Parameters}
+	Geometry Optimization: DFT PBE + VdW, \emph{tier1} basis in FHI-aims$^1$.
+	Convergence at 0.005 eV / \AA
 
 \end{frame}
-
+}
 \end{document}

### 2016-11-03 src/cppfiles/HFS_main.cpp

@@ -38,10 +38,21 @@ int main(int argc, char* argv[]){
     }
 
 
+    //std::vector< std::vector<double> > vecs(HFS::num_guess_evecs, std::vector<double>(2*HFS::Nexc, 0.0));
+    //for (unsigned i = 0; i < HFS::num_guess_evecs; ++i) {
+    //    vecs[i][i] = 1.0;
+    //}
+
+    // Try this, weight by how close diags are
     std::vector< std::vector<double> > vecs(HFS::num_guess_evecs, std::vector<double>(2*HFS::Nexc, 0.0));
     for (unsigned i = 0; i < HFS::num_guess_evecs; ++i) {
-        vecs[i][i] = 1.0;
+        arma::vec guessvec;
+        arma::vec temp = arma::abs(HFS::exc_energies[i] - HFS::exc_energies) + 1;
+        guessvec = (1.0 / temp);
+        guessvec /= arma::norm(guessvec);
+        vecs[i] = arma::conv_to< std::vector<double> >::from(guessvec);
     }
+
 
     myeps.SetInitialSpace(vecs);
     arma::wall_clock davtimer;

### 2016-11-03 src/launch.py

@@ -17,15 +17,15 @@ def get_fname(rs, Nk, ndim):
     fname = tempfile.mktemp(suffix=ext, prefix=pre, dir=outdir)
     return fname
 
-Nkrange = range(10, 20)
+Nkrange = range(53, 150, 4)
 rs = 1.2
 ndim = 2
-nguess = 50
-blocksize = 20
-num_evals = 8
+nguess = 1
+blocksize = 1
+num_evals = 1
 maxits = 50
 maxsubsize = 1000
-tolerance = 1e-8
+tolerance = 1e-6
 
 
 paramlist = [['./HFS', rs, Nk, ndim, get_fname(rs, Nk, ndim), tolerance, maxits,

### 2016-11-07 src/cppfiles/SLEPcWrapper.hpp
Decided to add logfiles

@@ -1,0 +1,210 @@
+#include <slepceps.h>
+#include <cstdio>
+#include <petscblaslapack.h>
+#include <armadillo>
+#include <vector>
+
+
+namespace SLEPc {
+    PetscErrorCode Petsc_MatVecProd(Mat matrix, Vec x, Vec y);
+    void (*matvec_product)(arma::vec&, arma::vec&);
+    class EpS {
+        public:
+            PetscErrorCode                     ierr;
+            EPS                                eps;
+            EPSType                            eps_type;
+            PetscMPIInt                        size;
+            Mat                                matrix;
+            PetscInt                           N, nconv, niter, BlockSize=1, nguess=1, Nevals=1, maxits;
+            double                             tol=1E-5;
+            std::vector<double>                iVals, rVals;
+            std::vector< std::vector<double> > iVecs, rVecs;
+            int                                argc=1;
+            char*                              args = (char*)"eps_monitor";
+            char**                             argv=&args;
+
+
+            EpS(PetscInt Ninput, void (*matvec_product)(arma::vec&, arma::vec&)) {
+                static char help[] = "Solves the same eigenproblem as in example ex2, but using a shell matrix. "
+                                     "The problem is a standard symmetric eigenproblem corresponding to the 2-D Laplacian operator.\n\n"
+                                     "The command line options are:\n"
+                                     "  -n <n>, where <n> = number of grid subdivisions in both x and y dimensions.\n\n";
+
+                N = Ninput;
+                SLEPc::matvec_product = matvec_product;
+                SlepcInitialize(&argc, &argv, (char*)0, help);
+                MPI_Comm_size(PETSC_COMM_WORLD, &size);
+                MatCreateShell(PETSC_COMM_WORLD, N, N, PETSC_DETERMINE, PETSC_DETERMINE, &N, &matrix);
+                PETSCMatCreate(matrix);
+                EPSCreate(PETSC_COMM_WORLD, &eps);
+                EPSContext();
+            }
+
+            PetscErrorCode clean() {
+                ierr = EPSDestroy(&eps);    CHKERRQ(ierr);
+                ierr = MatDestroy(&matrix); CHKERRQ(ierr);
+                ierr = SlepcFinalize();
[…]

### 2016-11-07 src/test.py

@@ -1,0 +1,26 @@
+import numpy as np
+import sys
+import os
+
+
+
+Nklist =  range(10, 100)
+rs = 1.2
+ndim = 2
+nguess = 50
+blocksize = 20
+neval = 8
+maxit = 50
+maxsubsize = 1000
+tol = 1e-8
+fname = 'test.log'
+
+tests = [['./HFS', rs, Nk, ndim, fname, tol, maxit, maxsubsize, nguess, blocksize, neval] for Nk in Nklist]
+
+strtests = [' '.join([str(j) for j in test]) for test in tests]
+
+
+
+for test in strtests:
+    print test
+#os.system(test)

### 2016-11-08 presentations/GroupMeeting_Fall2016.tex
Decided to add logfiles
Presentation is updated, figures better, some results

@@
 \usepackage[justification=centering]{caption}
+\usepackage{braket}
+\usepackage{amsmath}
 
@@
 \title{Hartree-Fock Stability}
-\subtitle{Applications to the Homogeneous Electron Gas \\ And Implications in Electron Correlation}
+\subtitle{Applications to the Homogeneous Electron Gas}
 \date{\today}
@@
 			\begin{itemize}[<+->]
-				\item {Restricted minima may correspond to absolute minima}
-				\item {Restricted minima may correspond to absolute maxima}
+				\item {Restricted minima may correspond to minima in another dimension}
+				\item {Restricted minima may correspond to maxima in another dimension}
 				\item {Restricted minima may be nonstationary}
@@
 {%
-	\setbeamertemplate{frame footer}{Thouless, D. J. Nucl. Phys. 1960, 21, 225–232.}
-\begin{frame}{Outline}
-	\begin{columns}[c] % align columns
-		\begin{column}{.48\textwidth}
+	\setbeamertemplate{frame footer}{Thouless, D. J. The Quantum Mechanics of Many-Body Systems, 2nd ed.; Dover: 1972. (p. 114)}
+\begin{frame}{Hartree-Fock Stability}
+	\begin{itemize}[<+->]
+		\item Solving the HF equations guarantees only that the energy is \alert{stationary}. The first order variation is therefore 0. 
+		\item We need to know if this is indeed a minimum.
+		\item We can determine this if we inspect the second order variation in the energy.
+		\item Thouless$^1$ showed a physically motivated derivation using Time-Dependent Hartree-Fock theory (TDHF). 
+	\end{itemize}
+\end{frame}
+
+{%
+	\setbeamertemplate{frame footer}{Thouless, D. J. The Quantum Mechanics of Many-Body Systems, 2nd ed.; Dover: 1972. (p. 114)}
+\begin{frame}{Hartree-Fock Stability Conditions}
+	\begin{itemize}[<+->]
+		\item[]{The TDHF solution is given by the Liouville Von-Neumann Equation of Motion,
+			\begin{eqnarray}
+				i\hbar\frac{\partial \rho}{\partial t} = \left[ T+U, \rho \right],
+			\end{eqnarray}
+		}
+		\item[]{Where U is the self-consistent potential,
+			\begin{eqnarray}
+				U_{pq} = \sum\limits_{p,q} \left(\rho_{pq,rs} - \braket{pr|sq} \right) \rho_{sr}.
+			\end{eqnarray}
+		}
+		\item[]{Under the restrictions,
+			\begin{eqnarray}
+				\rho^2 = \rho \quad \textrm{and} \quad \rho^{\dagger} = \rho,
+			\end{eqnarray}
+		}
+		\item[]{and to first order in $\rho_{ai}$, the elements of the density matrix are ,
+			\begin{eqnarray}
+				\rho_{ai} = C_{ai}, \quad \rho_{ia} = C_{ai}^*.
+			\end{eqnarray}
+		}
+	\end{itemize}
+\end{frame}
+
+{%
+	\setbeamertemplate{frame footer}{Thouless, D. J. The Quantum Mechanics of Many-Body Systems, 2nd ed.; Dover: 1972. (p. 114)}
+
+\begin{frame}{Hartree-Fock Stability Conditions}
+	\begin{itemize}[<+->]
+		\item[]{The TDHF EoM becomes,
+			\begin{eqnarray}
+				i\hbar \frac{dC_{ai} \left(t\right) }{dt} &=& \left(\epsilon_a - \epsilon_i \right) \nonumber
+					\\ &+& \sum\limits_{i}^{occ}  \sum\limits_{b}^{vir} 
+					  \left[\braket{aj||ib}C_{bj}   \left( t \right)
+						  +\braket{ab||ij}C_{bj}^* \left( t \right) \right]. 
+			\end{eqnarray}
+		}
+		\item[]{The solutions are complex exponentials,
+			\begin{eqnarray}
+				C_{ai} \left(t \right)  = \alpha X_{ai} e^{-i \omega t} + \alpha^* Y_{ai}^* e^{i \omega^* t},
+			\end{eqnarray}
+		}
+		\item[]{whose amplitudes, $X_{ai}$ and $Y_{ai}$ satisfy,
+			\begin{align}
+				\left(\epsilon_a - \epsilon_i \right)X_{ai} + \sum\limits_{i}^{occ}  \sum\limits_{b}^{vir} 
+					\left[ \braket{aj||ib}X_{bj} + \braket{ab||ij}Y_{bj} \right] &= \hbar \omega X_{ai}
+				\nonumber \\
+				\left(\epsilon_a - \epsilon_i \right)Y_{ai} + \sum\limits_{i}^{occ}  \sum\limits_{b}^{vir}
+					\left[ \braket{aj||ib}X_{bj} + \braket{ab||ij}Y_{bj} \right] &= -\hbar \omega Y_{ai}.
+			\end{align}
+		}
+		\item[]{These are the equations of the Random Phase Approximation (RPA)}		
+	\end{itemize}
+\end{frame}
+
+{%
+	\setbeamertemplate{frame footer}{Seeger, R.; Pople, J. A. J. Chem. Phys. 1977, 66 (7), 3045.}
+
+\begin{frame}{Hartree-Fock Stability Conditions}
+	\begin{itemize}[<+->]
+		\item{The RPA frequencies represent electronic oscillations about the ground state}
+		\item{Real frequencies are stable, imaginary frequencies are unstable}
+		\item{The RPA frequencies are imaginary when the \alert{Orbital Hessian} (aka stability matrix, electronic Hessian) eigenvalues are negative
+			\begin{eqnarray}
+				\begin{bmatrix}
+					\bf{A}   & \bf{B}   \\
+					\bf{B}^* & \bf{A}^* \\
+				\end{bmatrix}
+				\begin{bmatrix}  \bf{X} \\ \bf{Y}  \end{bmatrix}
+				= \omega \begin{bmatrix}  \bf{X} \\ \bf{Y}  \end{bmatrix}
+			\end{eqnarray}
+		}
+		\item{Where}
+		\begin{eqnarray}
+			A_{ia,jb} &=& \braket{{}_i^a|H-\braket{0|H|0}|{}_j^b} = \left(\epsilon_a - \epsilon_i \right) \delta_{ij}\delta_{ab} + \braket{aj||ib}
+			\nonumber \\
+			B_{ia,jb} &=& \braket{{}_{ij}^{ab}|H-\braket{0|H|0}|0} = \braket{ab||ij}.
+		\end{eqnarray}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{Hartree-Fock Stability Conditions}
 	\begin{itemize}
-				\item {Inspired by biological evolution}
-				\item {Evolve a population over generations}
-				\item {Survival of the fittest}
-				\item {Requirements:}
+		\item[]{The eigenvalue equation can be factorized depending on symmetry.}
+		\item[]{\includegraphics[width=\linewidth]{../images/seeger_stability.pdf} }
+	\end{itemize}
+\end{frame}
+
+\section{Homogeneous Electron Gas}
+
+{%
+	\setbeamertemplate{frame footer}{Phillips, P. Advanced Solid State Physics, 2nd ed.; Cambridge University Press: Cambridge, 2012.}
+
+\begin{frame}{Brief Overview}
 	\begin{itemize}
-					\item {Represent individuals as vector}
-					\item {Fitness function}
+		\item{Homogeneous Electron Gas (HEG) model, also known as Uniform Electron Gas or Jellium Model.}
+		\item{Electrons in a box with "smeared" nuclei $\rightarrow$ uniform positive background charge}
+		\item{The total charge is constrained to be neutral,}
+			\begin{eqnarray}
+				V_{bg}(\mathbf{r}) = \sum\limits_{i} \frac{-Ze^2}{|\mathbf{r}-\mathbf{R_i}|} \rightarrow -e^2 \int \frac{d\mathbf{r'}}{|\mathbf{r}-\mathbf{r'}|},
+			\end{eqnarray}
+		\item{and the background and coulomb terms cancel exactly,
+			\begin{eqnarray}
+				V_{ee} = e^2 \int \frac{d\mathbf{r'}}{|\mathbf{r}-\mathbf{r'}|}.
+			\end{eqnarray}
+		}
 	\end{itemize}
-				\item{$v = \left(\begin{smallmatrix}
-					x_1 & y_1 & z_1 & x_2 &  y_2 & z_2 &
-					... & x_N & y_N & z_N
-					\end{smallmatrix}\right)$}
-				\item{$F = \frac{E_{max} - E}{E_{max} - E_{min}}$}
+\end{frame}
+
+{%
+	\setbeamertemplate{frame footer}{Giuliani, G.; Vignale, G. Quantum Theory of the Electron Liquid; 2005.}
+
+\begin{frame}{Brief Overview}
+	\begin{itemize}
+		\item{The discretized solutions are given by,
+		\begin{eqnarray}\label{eq:hf_orb_energy}
+			\epsilon_{\vec{k}}=
+				\frac{\hbar^2 k^2}{2m} - \sum\limits_{\vec{k}}^{|\vec{k}|< k_f}
+				\braket{\vec{k}, \vec{k}' |\vec{k}', \vec{k}}
+		\end{eqnarray}
+		}
+		\item{Where the two electron integral is given by
+		\begin{align}
+			\braket{\vec{k}, \vec{k}'|\vec{k}'',\vec{k}'''}\stackrel{\text{2D, 3D}}{=}&
+				\begin{cases} 
+				\frac{\pi}{V}\frac{2^{D-1}}{|\vec{k}-\vec{k}''|^{D-1}} 
+				& \vec{k}''' = \vec{k}+\vec{k}'-\vec{k}'' \nonumber\\
+				0 
+				& \text{else}
+				\end{cases}
+			\nonumber \\
+			\braket{k, k'|k'',k'''}\stackrel{\text{1D}}{=}&
+				\begin{cases} 
+				e^{|k-k''|^2a^2}\text{Ei}(-|k-k''|^2a^2)\text{ ;}
+				& k''' = k+k'-k'' \\
+				0\text{ ;} 
+				& \text{else}
+				\end{cases}
+		\end{align}
+		}
+	\end{itemize}
+\end{frame}
+
+{%
+\setbeamertemplate{frame footer}{Overhauser, A. W. Phys. Rev. Lett. 1960, 4 (9), 462–465.}
+\begin{frame}{Project Goal}
+	\begin{itemize}[<+->]
+		\item{Can we use the HF-Stability analysis to determine where the HEG is unstable?}
+		\item{Will this predict the known tendency of crystallization at low density?}
+		\item{It is known that the RHF-GHF instability persists at all densities for the HEG$^1$.}
+		\item{Can we show this numerically, and discriminate between RHF-UHF and RHF-GHF instability?}
+		\item{(Future) Can we combine this with to improve the efficacy of correlation theories (CC, MBPT)?}
+	\end{itemize}
+\end{frame}
+
+\section{Notes on Iterative Subspace Eigenvalue Methods}
+{%
+\setbeamertemplate{frame footer}{1. Saad, Y. Numerical Methods for Large Eigenvalue Problems; SIAM, 2011.
+
+ 2. Davidson, E. R. J. Comput. Phys. 1975, 17 (1), 87–94.}
+\begin{frame}{Subspace Methods in 1 Slide}
+	\begin{itemize}
+		\item{Sometimes the eigenvalue problem is too large to solve completely, and only a few eigenpairs are needed}
+		\item{Subspace methods allow for finding some eigenpairs without full diagonalization}.
+		\item{They need only a matrix-vector product (maybe diagonal elements too).}
+		\item{A small subspace is constructed, then expanded slowly until the eigenpair residual norm,
+			\begin{eqnarray}
+				||\mathbf{Ax} - \lambda \mathbf{x}||,
+			\end{eqnarray}
+		is below some threshold.
+		}
+		\item{The \alert{Lanczos} and \alert{Arnoldi} methods are the most commonly used$^1$, while the \alert{Davidson}$^2$ method is likely more useful in a majority of chemical applications. }
+	\end{itemize}
+\end{frame}
+
+{%
+\setbeamertemplate{frame footer}{1. Saad, Y. Numerical Methods for Large Eigenvalue Problems; SIAM, 2011.
+
+ 2. Li, R.-C.; Zhang, L.-H. Convergence of Block Lanczos Method for Eigenvalue Clusters; 2013.}
+\begin{frame}{Convergence Properties}
+	\begin{itemize}[<+->]
+		\item{The convergence of these subspace algorithms depends on:}
+		\begin{itemize}
+			\item{\alert{Number of eigenvalues} requested}
+			\item{The \alert{block size} of the algorithm}
+			\item{The \alert{density} of the eigenvalue spectrum}
+			\item{The \alert{initial guess} eigenvectors}
+			\item{The \alert{condition number} of the matrix}
+			\item{The \alert{preconditioner} (Davidson only)}
+		\end{itemize}
+		\item{They can \alert{converge to an incorrect answer} if:}
+		\begin{itemize}
+			\item{The block size is too small compared to degeneracy}
+			\item{The approximate eigenvectors become non-orthogonal}
+		\end{itemize}
+		\item{My recommendation for guess eigenvectors is
+		\begin{eqnarray}
+			v_j^{(i)} = normalize\left(\frac{1}{|A_{ii} - A_{jj}| + 1} \right).
+		\end{eqnarray}
+		}
+	\end{itemize}
+\end{frame}
+
+{%
+\setbeamertemplate{frame footer}{Hern, V.; Tom, A.; Vidal, V. SLEPc Technical Reports, 2007.}
+\begin{frame}{Orthogonalization}
+	\begin{itemize}
+		\item{The condition number, $\kappa$, is bound from below by
+			\begin{eqnarray}
+				\kappa \geq \frac{Max(\lambda_i)}{Min(\lambda_j)}
+			\end{eqnarray}
+		}
+		\item{The Gram-Schmidt procedure has numerical issues, 
+			\begin{eqnarray}
+				||\mathbf{I} - \mathbf{Q^TQ}|| \leq \frac{\alpha\kappa^2}{1-\beta\kappa^2}.	
+			\end{eqnarray}
+		}
+		\item{Modified Gram-Schmidt is better, but not perfect,
+			\begin{eqnarray}
+				||\mathbf{I} - \mathbf{Q^TQ}|| \leq \frac{\gamma\kappa}{1-\eta\kappa}	
+			\end{eqnarray}
+		}
+		\item{May need multiple orthogonalization steps}
 	\end{itemize}
 
+\end{frame}
+
+\section{Results}
+
+{%
+\setbeamertemplate{frame footer}{}
+
+\begin{frame}{Matrix Size Scaling}
+	\begin{columns}[c] % align columns
+		\begin{column}{.4\textwidth}
+			\begin{itemize}
+				\item {Scales as $2N_{exc}$}
+				\item {$N_{occ}$ and $N_{vir}$ both scale with $N_{kpoints}^D$}
+			\end{itemize}				
 		\end{column}
 		\hfill
-		\begin{column}{0.48\textwidth}
+		\begin{column}{0.6\textwidth}
+		    \begin{overprint}
+			    \onslide<1>\includegraphics[width=\linewidth]{../images/matscale.eps}
 
+			\end{overprint}
 		\end{column}	
@@
 \end{frame}
-}
 
-{%
-\setbeamertemplate{frame footer}{1. Supady, A.; Blum, V.; Baldauf, C. J. Chem. Inf. Model. 2015, 55 (11), 2338–2348.
-
-2. http://www.chemspider.com/Chemical-Structure.2298795.html}
-\begin{frame}{From Structure to Vector}
+\begin{frame}{Matrix-Vector Scaling}
 	\begin{columns}[c] % align columns
-		\begin{column}{.48\textwidth}
+		\begin{column}{.4\textwidth}
 			\begin{itemize}
-				\item<1-> {Several Ways to Define Structure
-					\begin{itemize}
-						\item[] {Cartesian}
-						\item[] {Internal Coordinates (bond length, angle ...)}
-						\item[] {SMILES, InChI}
-					\end{itemize}
-				}
-				\item<2-> {InChI$^2$= 1S/C8H16/c1-5-7(3)8(4)6-2/h5-6H2,1-4H3/b8-7-}
-				\item<only@3> {Equivalent in theory}
-				\item<only@4> {Equivalent \alert{\textbf{in theory}}}
+				\item {Scales as $N_{exc} \times  N_{occ}$ due to momentum conservation}
 			\end{itemize}				
@@
 		\hfill
-		\begin{column}{0.48\textwidth}
-			1
+		\begin{column}{0.6\textwidth}
+		    \begin{overprint}
+			    \onslide<1>\includegraphics[width=\linewidth]{../images/mvscaling.eps}
+
+			\end{overprint}
 		\end{column}	
@@
 \end{frame}
-}
 
-\begin{frame}{Selecting Parents}
+\begin{frame}{Davidson Scaling}
 	\begin{columns}[c] % align columns
-		\begin{column}{.48\textwidth}
-			\begin{itemize}[<+->]
-				\item {Several methods are common}
-				\item {Reinforce good characteristics}
-				\item {Still give losers a chance}
-				\item {'Breed' pairs of winners}
-				\item {'Roulette Wheel' Method}
+		\begin{column}{.4\textwidth}
+			\begin{itemize}
+				\item {Davidson is Asymptotically quadratic.}
+				\item {Full diagonalization is almost cubic.}
 			\end{itemize}				
@@
 		\hfill
-		\begin{column}{0.48\textwidth}
+		\begin{column}{0.6\textwidth}
+		    \begin{overprint}
+			    \onslide<1>\includegraphics[width=\linewidth]{../images/dav_vs_exact_scaling.eps}
 
+			\end{overprint}
+		\end{column}	
+	\end{columns}
+\end{frame}
+
+\begin{frame}{Efficacy of Davidson's Algorithm}
+	\begin{columns}[c] % align columns
+		\begin{column}{.4\textwidth}
+			\begin{itemize}
+				\item {Scales as $N_{exc} \times  N_{occ}$ due to momentum conservation}
+			\end{itemize}				
+		\end{column}
+		\hfill
+		\begin{column}{0.6\textwidth}
+		    \begin{overprint}
+			    \onslide<1>\includegraphics[width=\linewidth]{../images/dav_vs_exact.eps}
+
+			\end{overprint}
 		\end{column}	
@@
 {%
-\setbeamertemplate{frame footer}{http://www.turingfinance.com/computational-finance
-
--updates-ieee-world-congress-computational-intelligence}
-\begin{frame}{The Next Generation}
-	\begin{itemize}[<+->]
-
-		\item[]{~\\Crossover distinguishes this from Monte Carlo}
-	\end{itemize}
-\end{frame}
-}
-
-\begin{frame}{The Whole Algorithm}
+\setbeamertemplate{frame footer}{Bernu, B.; Delyon, F.; Holzmann, M.; Baguet, L. Phys. Rev. B 2011, 84 (11), 115115.}
+\begin{frame}{Dependence on r${}_s$}
 	\begin{columns}[c] % align columns
-		\begin{column}{.48\textwidth}
-			\begin{itemize}[<+->]
-				\item[1.] {Generate N random, sensible geometries}
-				\item[2.] {Add each to blacklist}
-				\item[3.] {Optimize each geometry}
-				\item[4.] {Select Parents}
-				\item[5.] {Crossover \& Mutate into sensible geometry}
-				\item[6.] {Add Children to population}
-				\item[7.] {Remove High energy individuals}
-				\item[8.] {If converged:}
-				\begin{itemize}
-					\item{Done!}
-				\end{itemize}
-				\item[] {Otherwise:}
-				\begin{itemize}
-					\item{Go to 2}
-				\end{itemize}
-			\end{itemize}
+		\begin{column}{.5\textwidth}
+			\includegraphics[width=0.95\linewidth]{../images/stab_rs.eps}
+			\\
+			My Result
 		\end{column}
 		\hfill
-		\begin{column}{0.48\textwidth}
-			\onslide<11>\begin{itemize}
-				\medskip
-				\item[]{
-
-				}
-			    \item[]{
-
-				}
-			\end{itemize}
+		\begin{column}{0.5\textwidth}
+			\includegraphics[width=\linewidth]{../images/Bernu_2dEnergyGain.pdf}
+			\\
+			Published Result. Red = Square Lattice, Blue = Triangular Lattice
 		\end{column}	
@@
 \end{frame}
-
-\section{Finding Low Energy Conformers of Dipeptides}
-
-{%
-	\setbeamertemplate{frame footer}{Supady, A.; Blum, V.; Baldauf, C. J. Chem. Inf. Model. 2015, 55 (11), 2338–2348.}
-\begin{frame}{Dipeptide Structures}
-
-\end{frame}
-}
-
-{%
-\setbeamertemplate{frame footer}{Supady, A.; Blum, V.; Baldauf, C. J. Chem. Inf. Model. 2015, 55 (11), 2338–2348.
-}
-\begin{frame}{Combinatorics}
-	\begin{columns}[c] % align columns
-		\begin{column}{.4\textwidth}
-			\begin{itemize}
-				\item {GA beats other methods if space is large}
-				\item {Space gets large \textbf{\alert{fast}}}
-			\end{itemize}		
-		\end{column}
-		\hfill
-		\begin{column}{0.6\textwidth}
-
-		\end{column}	
-	\end{columns}
-\end{frame}
-}
-
-{%
-\setbeamertemplate{frame footer}{Supady, A.; Blum, V.; Baldauf, C. J. Chem. Inf. Model. 2015, 55 (11), 2338–2348.
-}
-\begin{frame}{Coverage}
-	\begin{columns}[c] % align columns
-		\begin{column}{.4\textwidth}
-			\begin{itemize}
-				\item {Smaller systems are reliably sampled}
-				\item {As \# of conformers increases, miss more and more}
-				\item {Is there a pattern to what is missed?}
-			\end{itemize}		
-		\end{column}
-		\hfill
-		\begin{column}{0.6\textwidth}
-
-		\end{column}	
-	\end{columns}
-\end{frame}
-}
-
-{%
-\setbeamertemplate{frame footer}{Supady, A.; Blum, V.; Baldauf, C. J. Chem. Inf. Model. 2015, 55 (11), 2338–2348.
-}
-\begin{frame}{Coverage}
-	\begin{columns}[c] % align columns
-		\begin{column}{.4\textwidth}
-			\begin{itemize}[<+->]
-				\item {Most misses are very high energy}
-				\item {Algorithm favors low energy areas of the space}
-				\item {Features low in energy are favored and recombined}
-			\end{itemize}		
-		\end{column}
-		\hfill
-		\begin{column}{0.6\textwidth}
-
-		\end{column}	
-	\end{columns}
-\end{frame}
-}
-
-{%
-\setbeamertemplate{frame footer}{Supady, A.; Blum, V.; Baldauf, C. J. Chem. Inf. Model. 2015, 55 (11), 2338–2348.}
-\begin{frame}{Energy Cutoff}
-	\begin{columns}[c] % align columns
-		\begin{column}{.4\textwidth}
-			\begin{itemize}[<+->]
-				\item[] {
-
-				}
-				\item {GA is more sensitive to energy cutoff}
-				\item {For finding low energy ensemble, GA outperforms purely stochastic/deterministic method}
-			\end{itemize}		
-		\end{column}
-		\hfill
-		\begin{column}{0.6\textwidth}
-
-		\end{column}	
-	\end{columns}
-\end{frame}
-}
 
@@
 \begin{frame}[fragile]{Backup slide}
-	\begin{itemize}
-		\item Geometry optimization step makes the algorithm more Lamarckian (Jean Baptiste Larmarck, [1744-1829])
-	\end{itemize}
+	Empty Backup
 \end{frame}
 
-{%
-\setbeamertemplate{frame footer}{(1) Blum, V. et. al., M. Comput. Phys. Commun. 2009, 180 (11), 2175–2196.
-
-(2) Supady, A.; Blum, V.; Baldauf, C. J. Chem. Inf. Model. 2015, 55 (11), 2338–2348.
-
-	}
-\begin{frame}[fragile]{Genetic Algorithm Parameters}
-	Geometry Optimization: DFT PBE + VdW, \emph{tier1} basis in FHI-aims$^1$.
-	Convergence at 0.005 eV / \AA
-
-\end{frame}
-}
 \end{document}

### 2016-11-08 src/launch.py

@@ -17,8 +17,8 @@ def get_fname(rs, Nk, ndim):
     fname = tempfile.mktemp(suffix=ext, prefix=pre, dir=outdir)
     return fname
 
-Nkrange = range(53, 150, 4)
-rs = 1.2
+Nk = 57
+rsrange = [0.2, 0.3, 0.4, 0.6, 0.7, 0.8, 0.9, 1.1, 1.3, 1.5]
 ndim = 2
 nguess = 1
 blocksize = 1
@@ -29,7 +29,7 @@ tolerance = 1e-6
 
 
 paramlist = [['./HFS', rs, Nk, ndim, get_fname(rs, Nk, ndim), tolerance, maxits,
-              maxsubsize, nguess, blocksize, num_evals] for Nk in Nkrange]
+              maxsubsize, nguess, blocksize, num_evals] for rs in rsrange]
 
 for i in range(my_rank, len(paramlist), nprocs):
      print 'Starting Job: ',  ' '.join([str(j) for j in paramlist[i]])

### 2016-11-08 presentations/GroupMeeting_Fall2016.tex
Presentation updates
Added more figures and finishe groupmeeting

@@
 \usepackage{graphicx}
+\usepackage{multirow}
 \usepackage{booktabs}
@@
 		\item We need to know if this is indeed a minimum.
-		\item We can determine this if we inspect the second order variation in the energy.
+		\item We can determine this if we inspect the \alert{second order variation} in the energy.
 		\item Thouless$^1$ showed a physically motivated derivation using Time-Dependent Hartree-Fock theory (TDHF). 
@@
 		\item{Real frequencies are stable, imaginary frequencies are unstable}
-		\item{The RPA frequencies are imaginary when the \alert{Orbital Hessian} (aka stability matrix, electronic Hessian) eigenvalues are negative
+		\item{The RPA frequencies are imaginary when the \alert{Orbital Hessian} (aka stability matrix, electronic Hessian) eigenvalues are \alert{negative}
 			\begin{eqnarray}
@@
 		\begin{eqnarray}
-			A_{ia,jb} &=& \braket{{}_i^a|H-\braket{0|H|0}|{}_j^b} = \left(\epsilon_a - \epsilon_i \right) \delta_{ij}\delta_{ab} + \braket{aj||ib}
+			A_{ia,jb} &=& \braket{{}_i^a|H-E_0|{}_j^b} = \left(\epsilon_a - \epsilon_i \right) \delta_{ij}\delta_{ab} + \braket{aj||ib}
 			\nonumber \\
-			B_{ia,jb} &=& \braket{{}_{ij}^{ab}|H-\braket{0|H|0}|0} = \braket{ab||ij}.
+			B_{ia,jb} &=& \braket{{}_{ij}^{ab}|H-E_0|0} = \braket{ab||ij}.
 		\end{eqnarray}
@@
 
+{%
+	\setbeamertemplate{frame footer}{1) Seeger, R.; Pople, J. A. J. Chem. Phys. 1977, 66 (7), 3045.}
 \begin{frame}{Hartree-Fock Stability Conditions}
 	\begin{itemize}
-		\item[]{The eigenvalue equation can be factorized depending on symmetry.}
-		\item[]{\includegraphics[width=\linewidth]{../images/seeger_stability.pdf} }
+		\item[]{The eigenvalue equation can be factorized depending on symmetry.} \\~\\
+		\item[]{
+			\resizebox{0.9\textwidth}{!}{%
+			\begin{tabular}{r@{\qquad}cccccc}
+				  \multirow{1}{*}{Solution Type} & \multicolumn{6}{c}{Space Type}  \\
+				  \cmidrule{2-7}
+				  & Real RHF & Complex RHF & Real UHF & Complex UHF & Real GHF & Complex GHF \\
+				  \midrule
+				  Real RHF    & ${}^1\mathbf{A}' + {}^1\mathbf{B}'$ & ${}^1\mathbf{A}' - {}^1\mathbf{B}'$ & ${}^3\mathbf{A}' + {}^3\mathbf{B}'$ & & & \\
+				  Complex RHF & - & ${}^1\mathbf{H}'$ & - & \alert{${}^3\mathbf{H}'$} & - & \\
+				  Real UHF    & - & - & $\mathbf{A}' + \mathbf{B}'$ & $\mathbf{A}' - \mathbf{B}'$ & $\mathbf{A}'' + \mathbf{B}''$ &  \\
+				  Complex UHF & - & - & - &  $\mathbf{H}'$ & - & $\mathbf{H}'$ \\
+				  Real GHF    & - & - & - & - & $\mathbf{A} - \mathbf{B}$ &  $\mathbf{A} - \mathbf{B}$  \\
+				  Complex GHF & - & - & - & - & - & $\mathbf{H}$ \\
+				  \bottomrule
+			\end{tabular}}
+		\item[] \tiny Table reproduced from Seeger \& Pople$^1$
+		}
 	\end{itemize}
@@
 			\epsilon_{\vec{k}}=
-				\frac{\hbar^2 k^2}{2m} - \sum\limits_{\vec{k}}^{|\vec{k}|< k_f}
+				\frac{\hbar^2 k^2}{2m} - \sum\limits_{\vec{k}'}^{|\vec{k}'|< k_f}
 				\braket{\vec{k}, \vec{k}' |\vec{k}', \vec{k}}
@@
 		}
-	\end{itemize}
-\end{frame}
-
-{%
-\setbeamertemplate{frame footer}{Overhauser, A. W. Phys. Rev. Lett. 1960, 4 (9), 462–465.}
-\begin{frame}{Project Goal}
-	\begin{itemize}[<+->]
-		\item{Can we use the HF-Stability analysis to determine where the HEG is unstable?}
-		\item{Will this predict the known tendency of crystallization at low density?}
-		\item{It is known that the RHF-GHF instability persists at all densities for the HEG$^1$.}
-		\item{Can we show this numerically, and discriminate between RHF-UHF and RHF-GHF instability?}
-		\item{(Future) Can we combine this with to improve the efficacy of correlation theories (CC, MBPT)?}
 	\end{itemize}
@@
 			\item{The \alert{initial guess} eigenvectors}
-			\item{The \alert{condition number} of the matrix}
+			\item{The \alert{condition number} of the eigenvector matrix}
 			\item{The \alert{preconditioner} (Davidson only)}
@@
 			\begin{eqnarray}
-				\kappa \geq \frac{Max(\lambda_i)}{Min(\lambda_j)}
+				\kappa \geq \frac{Max(A_{ii})}{Min(A_{jj})}
 			\end{eqnarray}
@@
 
+{%
+\setbeamertemplate{frame footer}{Overhauser, A. W. Phys. Rev. Lett. 1960, 4 (9), 462–465.}
+\begin{frame}{Project Goal}
+	\begin{itemize}[<+->]
+		\item{Can we use the HF-Stability analysis to determine where the HEG is unstable?}
+		\item{Will this predict the known tendency of crystallization at low density?}
+		\item{It is known that the RHF-GHF instability persists at all densities for the HEG$^1$.}
+		\item{Can we show this numerically, and discriminate between RHF-UHF and RHF-GHF instability?}
+		\item{(Future) Can we combine this with to improve the efficacy of correlation theories (CC, MBPT)?}
+	\end{itemize}
+\end{frame}
+
 \section{Results}
+
+{%
+\setbeamertemplate{frame footer}{}
+
+\begin{frame}{First Brillouin Zone}
+	\begin{columns}[c] % align columns
+		\begin{column}{.4\textwidth}
+			\begin{itemize}
+				\item {Excite Ony in the X direction}
+				\item {-X virtuals matter due to $\vec{k}' = \vec{k} + \vec{G}$}
+			\end{itemize}				
+		\end{column}
+		\hfill
+		\begin{column}{0.6\textwidth}
+		    \begin{overprint}
+			    \onslide<1>\includegraphics[width=\linewidth]{../images/1stBZ.eps}
+
+			\end{overprint}
+		\end{column}	
+	\end{columns}
+\end{frame}
+
+{%
+\setbeamertemplate{frame footer}{}
+
+\begin{frame}{Orbital Energies}
+	\begin{columns}[c] % align columns
+		\begin{column}{.4\textwidth}
+			\begin{itemize}
+				\item {Nk = 57 reproduces the orbital energies reasonably well}
+				\item {Worst towards $\Gamma$, better for higher $|\vec{k}|$}
+			\end{itemize}				
+		\end{column}
+		\hfill
+		\begin{column}{0.6\textwidth}
+		    \begin{overprint}
+			    \onslide<1>\includegraphics[width=\linewidth]{../images/energycompare.eps}
+
+			\end{overprint}
+		\end{column}	
+	\end{columns}
+\end{frame}
+
+{%
+\setbeamertemplate{frame footer}{}
+
+\begin{frame}{Matrix Diagonals}
+	\begin{columns}[c] % align columns
+		\begin{column}{.4\textwidth}
+			\begin{itemize}
+				\item {Spectrum is Dense}
+			\end{itemize}				
+		\end{column}
+		\hfill
+		\begin{column}{0.6\textwidth}
+		    \begin{overprint}
+			    \onslide<1>\includegraphics[width=\linewidth]{../images/exchist.eps}
+
+			\end{overprint}
+		\end{column}	
+	\end{columns}
+\end{frame}
 
@@
 
+{%
+\setbeamertemplate{frame footer}{1) http://mathworld.wolfram.com/StrassenFormulas.html}
+
 \begin{frame}{Davidson Scaling}
@@
 				\item {Full diagonalization is almost cubic.}
+				\item {Matrix multiplication is order${}^1$ $log_2(7) \approx 2.807$}
 			\end{itemize}				
@@
 
+\begin{frame}{Algorithm Wall time}
+	\begin{columns}[c] % align columns
+		\begin{column}{.4\textwidth}
+			\begin{itemize}
+				\item {Roughly quadratic wrt matrix dimension.}
+				\item {Outliers correspond to high condition number}
+			\end{itemize}				
+		\end{column}
+		\hfill
+		\begin{column}{0.6\textwidth}
+		    \includegraphics[width=\linewidth]{../images/overallruntime.eps}
+		\end{column}	
+	\end{columns}
+\end{frame}
+
 \begin{frame}{Efficacy of Davidson's Algorithm}
@@
 			\begin{itemize}
-				\item {Scales as $N_{exc} \times  N_{occ}$ due to momentum conservation}
+				\item {Reproduces Exact result to machine precision in all test cases.}
+				\item {Odd spikes are due to approximating circle by squares}
 			\end{itemize}				
@@
 \begin{frame}{Dependence on r${}_s$}
-	\begin{columns}[c] % align columns
-		\begin{column}{.5\textwidth}
-			\includegraphics[width=0.95\linewidth]{../images/stab_rs.eps}
-			\\
-			My Result
-		\end{column}
-		\hfill
-		\begin{column}{0.5\textwidth}
-			\includegraphics[width=\linewidth]{../images/Bernu_2dEnergyGain.pdf}
-			\\
-			Published Result. Red = Square Lattice, Blue = Triangular Lattice
-		\end{column}	
-	\end{columns}
+	Crossover from stable to unstable agrees with previous results.
+	\includegraphics[width=.95\linewidth]{../images/MeVsBernu.pdf}
 \end{frame}
@@
 {%
-\setbeamertemplate{frame footer}{Supady, A.; Blum, V.; Baldauf, C. J. Chem. Inf. Model. 2015, 55 (11), 2338–2348.}
-\begin{frame}{Concluding Remarks}
-	\begin{itemize}[<+->]
-		\item {Finding all the low energy conformers for a molecule is hard}
-		\item {In order to get accurate energies/structures, computationally expensive methods should be employed}
-		\item {These take time, so we want to minimize how many of these we do}
-		\item {The Genetic Algorithm provides a framework for a refined global search}
-		\item {It shines when asked to find a host of low energy solutions}
-		\item {GA wrapper can be interfaced with a variety of electronic structure packages(NWChem, ORCA) and is available under the GNU Lesser General Public License at \url{https://github.com/adrianasupady/fafoom}}
-
-	\end{itemize}
+\setbeamertemplate{frame footer}{}
+\begin{frame}{Next Steps}
+	\resizebox{\textwidth}{!}{%
+	\begin{tabular}{l c c}
+		Objective                 & Human Time   & Computer Time    \\
+		\midrule
+		Other instabilities in 2D & 30 mins & Week \\
+		All 3D & $\frac{1}{2}$ Day&  $>$Weeks? Parallel?
+	\end{tabular}}
 \end{frame}
@@
 
+{%
+\setbeamertemplate{frame footer}{}
 \begin{frame}[standout]
@@
 
-\begin{frame}[fragile]{Backup slide}
-	Empty Backup
-\end{frame}
-
+%{%
+%\setbeamertemplate{frame footer}{}
+%\begin{frame}[fragile]{Backup slide}
+%	Empty Backup
+%\end{frame}
+%
 \end{document}

### 2016-11-08 src/pyfiles/HFSAnalyzer.py

@@ -215,12 +215,12 @@ def axplot_1stBZ(df, ax, df_idx, spec_alpha, scale, labels):
     vir_states = df.iloc[df_idx]['Virtual States']
     occ_states = df.iloc[df_idx]['Occupied States']
 
-    circle = plt.Circle((0, 0), radius=kf, fc='none', linewidth=1)
+    circle = plt.Circle((0, 0), radius=kf, fc='none', linewidth=1, zorder=4)
     sqrpoints = [[kmax, kmax]
                 ,[kmax, -kmax]
                 ,[-kmax, -kmax]
                 ,[-kmax, kmax]]
-    square =plt.Polygon(sqrpoints, edgecolor=sns.color_palette()[0], fill=None)
+    square =plt.Polygon(sqrpoints, edgecolor=sns.color_palette()[0], fill=None, zorder=4)
     ax.add_patch(circle)
     ax.add_patch(square)
 
@@ -233,21 +233,25 @@ def axplot_1stBZ(df, ax, df_idx, spec_alpha, scale, labels):
     active_virs = kgrid[vir_states[mask2]]
 
     ax.scatter(kgrid[occ_states[:,0]], kgrid[occ_states[:,1]],
-                c=sns.color_palette()[0], label='Occupied')
+                c=sns.color_palette()[0], label='Occupied', s=8, zorder=3, edgecolors='none')
+    vir_color = sns.color_palette()[2]
+    spec_vir_color = (255.0/255, 204./255, 153./255) 
+
     ax.scatter(active_virs[:,0], active_virs[:,1],
-                c=sns.color_palette()[2], label='Virtual')
+                c=vir_color, label='Virtual', s=8, zorder=2, edgecolors='none')
     ax.scatter(spec_virs[:,0], spec_virs[:,1],
-                c=sns.color_palette()[2], alpha=spec_alpha, label='Spectator Virtuals')
+                c=spec_vir_color, alpha=spec_alpha, label='Spectator Virtuals', 
+                s=8, zorder=1, edgecolors='none')
     ax.set_xlim(-scale*kmax, scale*kmax)
     ax.set_ylim(-scale*kmax, scale*kmax)
     rs = df.iloc[df_idx]['rs']
     Nk = df.iloc[df_idx]['Nk']
     ndim = df.iloc[df_idx]['ndim']
-    title = 'rs = ' + str(rs) + ' Nk = ' + str(Nk) + ' ndim = ' + str(ndim)
[…]

### 2016-11-15 src/cppfiles/HFS_matrix_utils.cpp
Starting Hprime matrix vector

@@ -182,4 +182,63 @@ namespace HFS {
         return t;
     }
 
+    void matvec_prod_Hprime(arma::vec& v, arma::vec& Mv) {
+        //MUST BE CALLED WITH MV of LENGTH 8Nexc
+        /*  The matrix-vector multiplication | A'  B' | |v1|  =  | Mv1 |
+                                             | B'* A'*| |v2|     | Mv2 |
+            Factors into 4 matrix vector multiplications (A, B are matrices)
+            Mv1 = A'v1  + B'v2
+            Mv2 = B'*v1 + A'*v2
+
+            This routine is structured to factorize the matrix-vector product to be easier
+            to understand and program, whilst avoiding any copying of vectors, in anticipation
+            that they will become large.
+        */
+
+        // Each matrix is 4*Nexc, the vector has 8Nexc elements.
+        arma::vec v1(&v             , 4*HFS::Nexc, false, true);    // First 4Nexc elements of v
+        arma::vec v2(&v(4*HSF::Nexc), 4*HFS::Nexc, false, true);    // Last 4Nexc elements of v
+        arma::vec Mv1(&Mv             , 4*HFS::Nexc, false, true);  // First 4Nexc elements of Mv
+        arma::vec Mv2(&Mv(4*HSF::Nexc), 4*HFS::Nexc, false, true);  // Last 4Nexc elements of Mv
+
+        /* Each matrix vector product routine *adds* the
+           matrix vector product inplace to the given Mv
+           return vector. Thus the Mv must be
+           initialized, which initializes all Mv1, Mv2. */
+        Mv.zeros();
+        HFS::matvec_prod_Aprime(v1, Mv1);
+        HFS::matvec_prod_Bprime(v2, Mv1);
+
+        HFS::matvec_prod_Bprime(v1, Mv2);
+        HFS::matvec_prod_Aprime(v2, Mv2);
+        // At this point all values in Mv are filled.
+
+    }
 }
+
+    arma::vec matvec_prod_Aprime(arma::vec& v, arma::vec& Mv) {
+        arma::vec Mv(HFS::Nexc, arma::fill::zeros);
+        for (arma::uword s = 0; s < HFS::Nexc; ++s) {
+            arma::uword i = HFS::excitations(s, 0), a = HFS::excitations(s, 1);
+            arma::vec ki(HFS::ndim), ka(HFS::ndim);
+            ki = HFS::occ_idx_to_k(i);
+            ka = HFS::vir_idx_to_k(a);
[…]

### 2016-11-30 src/cppfiles/HFS_debug.cpp
Tested pass by ref/copy. Copy won. Don't know why

@@ -4,9 +4,8 @@ namespace HFS{
 
     arma::mat full_matrix;
     double full_diag_min;
-    double Mv_time;
+    double Mv_time, Mv_time2;
     double full_diag_time;
-    void time_mv();
 
     bool davidson_agrees_fulldiag() {
         arma::wall_clock timer;
@@ -38,10 +37,11 @@ namespace HFS{
 
     void time_mv() {
         arma::wall_clock timer;
-        timer.tic();
         arma::vec v(2*HFS::Nexc, arma::fill::randu);
+        timer.tic();
         arma::vec Mv = HFS::matvec_prod_3H(v);
         HFS::Mv_time = timer.toc();
+        std::cout << "mv1 time = " << HFS::Mv_time << std::endl;
     }
 
     void build_matrix() {

### 2016-11-30 src/cppfiles/HFS_debug.hpp

@@ -13,11 +13,12 @@ namespace HFS{
     extern double full_diag_min;
     extern bool davidson_agrees_fulldiag();
     extern bool mv_is_working();
-    extern double Mv_time;
+    extern double Mv_time, Mv_time2;
     extern double full_diag_time;
     extern bool everything_works();
     extern void build_matrix();
     extern void time_mv();
+    extern void time_mv2();
 }
 
 #endif // HFS_debug_included

### 2016-11-30 src/cppfiles/HFS_main.cpp

@@ -13,21 +13,35 @@ int main(int argc, char* argv[]){
     arma::wall_clock timer;
     timer.tic();
 
-    HFS::rs              = std::stof(argv[1]);
-    HFS::Nk              = std::stoi(argv[2]);
-    HFS::ndim            = std::stoi(argv[3]);
-    HFS::OutputFileName  = argv[4];
-    HFS::Dav_tol         = std::stof(argv[5]);
-    HFS::Dav_maxits      = std::stoi(argv[6]);
-    HFS::Dav_maxsubsize  = std::stoi(argv[7]);
-    HFS::num_guess_evecs = std::stoi(argv[8]);
-    HFS::Dav_blocksize   = std::stoi(argv[9]);
-    HFS::Dav_Num_evals   = std::stoi(argv[10]);
+    #ifdef RELEASE
+        HFS::rs              = std::stof(argv[1]);
+        HFS::Nk              = std::stoi(argv[2]);
+        HFS::ndim            = std::stoi(argv[3]);
+        HFS::OutputFileName  = argv[4];
+        HFS::Dav_tol         = std::stof(argv[5]);
+        HFS::Dav_maxits      = std::stoi(argv[6]);
+        HFS::Dav_maxsubsize  = std::stoi(argv[7]);
+        HFS::num_guess_evecs = std::stoi(argv[8]);
+        HFS::Dav_blocksize   = std::stoi(argv[9]);
+        HFS::Dav_Num_evals   = std::stoi(argv[10]);
+    #else
+        HFS::rs              = 1.2;
+        HFS::Nk              = 15;
+        HFS::ndim            = 2;
+        HFS::OutputFileName  = "profile";
+        HFS::Dav_tol         = 1e-6;
+        HFS::Dav_maxits      = 30;
+        HFS::Dav_maxsubsize  = 1500;
+        HFS::num_guess_evecs = 1;
+        HFS::Dav_blocksize   = 1;
+        HFS::Dav_Num_evals   = 1;
+    #endif // Release
 
     HFS::calc_params();
 
     HFS::time_mv();
 
+    /*
     SLEPc::EpS myeps(2*HFS::Nexc, HFS::void_matvec_prod_3H);
     myeps.SetDimensions(HFS::Dav_Num_evals, HFS::Dav_maxsubsize);
     myeps.SetTol(HFS::Dav_tol, HFS::Dav_maxits);
@@ -36,12 +50,6 @@ int main(int argc, char* argv[]){
[…]

### 2016-11-30 src/cppfiles/HFS_matrix_utils.cpp

@@ -160,63 +160,7 @@ namespace HFS {
         return Mv;
     }
 
-    void void_matvec_prod_3H(arma::vec& v, arma::vec&Mv) {
-        /*  The matrix-vector multiplication | A  B | |v1|  =  | Mv1 |
-                                             | B* A*| |v2|     | Mv2 |
-            Factors into 4 matrix vector multiplications (x, y are vectors; A, B are matrices)
-            Mv1 = A*v1 + B*v2
-            Mv2 = B*v1 + A*v2
-        */
-        arma::vec v1 = v.head(HFS::Nexc);
-        arma::vec v2 = v.tail(HFS::Nexc);
-
-        arma::vec Mv1 = HFS::matvec_prod_3A(v1) + HFS::matvec_prod_3B(v2);
-        arma::vec Mv2 = HFS::matvec_prod_3B(v1) + HFS::matvec_prod_3A(v2);
-        Mv = arma::join_cols(Mv1, Mv2);
-    }
-
-    arma::uword kb_j_to_t(arma::vec& kb, arma::uword j) {
-        arma::uvec b_N_idx =  k_to_index(kb);
-        arma::uword b = HFS::vir_N_to_1_mat(b_N_idx(0), b_N_idx(1));
-        arma::uword t = HFS::inv_exc_mat(j, b);
-        return t;
-    }
-
-    void matvec_prod_Hprime(arma::vec& v, arma::vec& Mv) {
-        //MUST BE CALLED WITH MV of LENGTH 8Nexc
-        /*  The matrix-vector multiplication | A'  B' | |v1|  =  | Mv1 |
-                                             | B'* A'*| |v2|     | Mv2 |
-            Factors into 4 matrix vector multiplications (A, B are matrices)
-            Mv1 = A'v1  + B'v2
-            Mv2 = B'*v1 + A'*v2
-
-            This routine is structured to factorize the matrix-vector product to be easier
-            to understand and program, whilst avoiding any copying of vectors, in anticipation
-            that they will become large.
-        */
-
-        // Each matrix is 4*Nexc, the vector has 8Nexc elements.
-        arma::vec v1(&v             , 4*HFS::Nexc, false, true);    // First 4Nexc elements of v
-        arma::vec v2(&v(4*HSF::Nexc), 4*HFS::Nexc, false, true);    // Last 4Nexc elements of v
[…]

### 2016-11-30 src/cppfiles/HFS_matrix_utils.hpp

@@ -9,7 +9,10 @@ namespace HFS{
     extern arma::vec matvec_prod_3A(arma::vec&);
     extern arma::vec matvec_prod_3B(arma::vec&);
     extern arma::vec matvec_prod_3H(arma::vec&);
-    extern void void_matvec_prod_3H(arma::vec& v, arma::vec&Mv);
+    extern void void_matvec_prod_3H(arma::vec& v, arma::vec& Mv);
+    extern void matvec_prod_Hprime(arma::vec& v, arma::vec& Mv);
+    extern void matvec_prod_Aprime(arma::vec& v, arma::vec& Mv);
+    extern void matvec_prod_Bprime(arma::vec& v, arma::vec& Mv);
     extern double calc_1B(arma::uword, arma::uword);
     extern double calc_3B(arma::uword, arma::uword);
     extern double calc_1A(arma::uword, arma::uword);

### 2016-11-30 src/launch.py

@@ -17,8 +17,9 @@ def get_fname(rs, Nk, ndim):
     fname = tempfile.mktemp(suffix=ext, prefix=pre, dir=outdir)
     return fname
 
-Nk = 57
-rsrange = [0.2, 0.3, 0.4, 0.6, 0.7, 0.8, 0.9, 1.1, 1.3, 1.5]
+Nk = 50
+#rsrange = [0.2, 0.3, 0.4, 0.6, 0.7, 0.8, 0.9, 1.1, 1.3, 1.5]
+rsrange = [0.2]
 ndim = 2
 nguess = 1
 blocksize = 1

### 2017-01-11 doc/papers/workingequations/heg_equations.tex
Reorganized latex documents, each .tex gets its own directory !

--- 2016-07-25 overview/heg_equations.tex
@@
 \usepackage{textcomp}
-\usepackage{minted}
 \usepackage{algorithm}
+\usepackage{booktabs}
 \usepackage[noend]{algpseudocode}
@@
 
-\begin{equation}
+\begin{equation}\label{eq:hf_orb_energy}
 \epsilon_{\vec{k},\sigma}=
@@
 Here we have used the relationship to relate the discrete and continuous quantities, (p.
-15 of \cite{Guiliani2005})
+15 of \cite{Guiliani2005}).
+Note the factor of $\frac{1}{L^D}$ is not in the discrete equation; I have moved that to the definition of the two electron integral for consistency with other resources.
+Note also that $L^D = \Omega$.
 
@@
 Figure \ref{fig:stability_table} is a reproduction of the stability conditions they developed, and more details can be found in the paper.
-\begin{figure}[h]
-   \includegraphics[width=1.0\linewidth]{figures/seeger_stability.pdf}
-  	\caption {Hartree-Fock Stability conditions reproduced from Seeger \& Pople \cite{Seeger1977}}
-  	\label{fig:stability_table}
-\end{figure}
 
@@
 
-\subsection{Implementation}
-\begin{algorithm}[H]
-\caption{Davidson's Algorithm}\label{davidson}
-\begin{algorithmic}[1]
-\State create \bf{V}
-\For {$i = 0, max\text{ }iterations$}
-\State $\bf{\tilde{A}} = \bf{V}^\dag\bf{AV}$
-\State $\tilde{\lambda},\mathbf{\tilde{x}} = eigensystem(\bf{\tilde{A}})$
-\State sort $\tilde{\lambda},\mathbf{\tilde{x}}$
-\If {$i > \textit{stringlen}$} \Return false
-\EndIf
-\State $j \gets \textit{patlen}$
-\If {$\textit{string}(i) = \textit{path}(j)$}
-\State $j \gets j-1$.
-\State $i \gets i-1$.
-\State \textbf{goto} \emph{loop}.
-\State \textbf{close};
-\EndIf
-\State $i \gets i+\max(\textit{delta}_1(\textit{string}(i)),\textit{delta}_2(j))$.
-\State \textbf{goto} \emph{top}.
-\EndFor
-
-\end{algorithmic}
-\end{algorithm}
-
 \section{Code Layout}
 \begin{figure}[H]
-   \includegraphics[width=1.0\linewidth]{figures/hf_stability_diagram.eps}
-   \caption {Layout of code implementation. Red boxes are python, blue are C++ and purple dotted lines require cython. Green are likely to be removed for speed}
-   \label{fig:code_diagram}
+    TODO
 \end{figure}
@@
 \end{document}
+kk

### 2017-01-16 HFS/qsub/scriptgen.py
Added some stuff

@@ -4,8 +4,8 @@ import os
 
 NDIM = 3
 CASE = "cRHF2cUHF"
-rslist = np.linspace(0.5, 10, 20)
-Nklist = [37]
+rslist = [1.2]
+Nklist = [45]
 
 
 f = open("templateqsub.sh", "r")

### 2017-01-16 HFS/qsub/templateqsub.sh

@@ -1,6 +1,7 @@
 #!/bin/bash
 #$ -S /bin/bash            # use bash shell
-#$ -q all.q@compute-0-0,all.q@compute-0-1,all.q@compute-0-2,all.q@compute-0-4,all.q@compute-0-5,all.q@compute-0-6,all.q@compute-0-7   # Queue jobs on any node  
+# -q all.q@compute-0-0,all.q@compute-0-1,all.q@compute-0-2,all.q@compute-0-4,all.q@compute-0-5,all.q@compute-0-6,all.q@compute-0-7   # Queue jobs on any node  
+#$ -q all.q@compute-0-5    # Queue jobs on any node  
 #$ -pe orte 1              # parallel environment: use N cores
 #$ -cwd                    # execute from current working directory
 #$ -e error.out

### 2017-01-16 doc/papers/matrixproperties/MatrixProperties.tex
Started some work on the summary

\documentclass{revtex4}
\usepackage[margin=1in, paperheight=1in, paperwidth=1in]{geometry}  % doesn't compile w/o width, height
\geometry{
 a4paper,
 total={170mm,257mm},
 left=15mm,
 top=5mm,
}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{kbordermatrix}
\usepackage{braket}
\usepackage{xcolor}

\definecolor{myred}{HTML}{CC5803}
\definecolor{myblue}{HTML}{204B57}

\newcommand{\Ap}{\textcolor{myred}{\braket{aj|ib}}}
\newcommand{\App}{\textcolor{myred}{\braket{aj|bi}}}
\newcommand{\Aa}{\textcolor{myred}{\braket{aj||ib}}}
\newcommand{\B}{\textcolor{myblue}{\braket{ab|ij}}}
\newcommand{\Br}{\textcolor{myblue}{\braket{ab|ji}}}
\newcommand{\Ba}{\textcolor{myblue}{\braket{ab||ij}}}

\newcommand{\AtoB}{\mathbf{\alpha\rightarrow\beta}}
\newcommand{\BtoA}{\mathbf{\beta\rightarrow\alpha}}
\newcommand{\AtoA}{\mathbf{\alpha\rightarrow\alpha}}
\newcommand{\BtoB}{\mathbf{\beta\rightarrow\beta}}
\newcommand{\e}{\textcolor{myred}{\left(\epsilon_a-\epsilon_i\right)}}
\newcommand{\diag}{\textcolor{myred}{\delta_{ij}\delta_{ab}}}

\begin{document}
\title{Notes on Matrix Factorization for Hartree-Fock Stability of HEG}
\author{Evan Curtin}
\maketitle

\section{Orbital Hessian Factorization}
According to Seeger and Pople\cite{Seeger1977}, (and many other sources) the molecular orbital
Hessian has the form,
\begin{eqnarray*}
\mathbf{H} =
  \begin{bmatrix}
    \mathbf{A}   & \mathbf{B}   \\
    \mathbf{B^*} & \mathbf{A^*} \\
  \end{bmatrix}
\end{eqnarray*}

Where the matrices denoted by $\mathbf{A}$ and $\mathbf{B}$ are given by,

\begin{eqnarray*}
  A_{st} &=& \e\diag -  \Aa \\
  B_{st} &=& \Ba         \\
\end{eqnarray*}

The color is to help keep track of which portions of the matrices come from
$\mathbf{A}$ and $\mathbf{B}$.
The integration is over spin and spatial coordinates. In the case of
a stationary UHF solution, the matrices $\mathbf{A}$ and $\mathbf{B}$ have the
following forms, after integrating over spin:

\begin{eqnarray*}
  \mathbf{A}&=&\kbordermatrix{
        & \AtoA           & \AtoB           & \BtoA          & \BtoB          \\
  \AtoA & \e\diag + \Aa   & 0               & 0              & \Ap            \\
  \AtoB & 0               & \e\diag - \App  & 0              & 0              \\
  \BtoA & 0               & 0               & \e\diag - \App & 0              \\
  \BtoB & \Ap             & 0               & 0              & \e\diag + \Aa  \\
}
\end{eqnarray*}

\begin{eqnarray*}
  \mathbf{B}&=&\kbordermatrix{
        & \AtoA           & \AtoB           & \BtoA          & \BtoB          \\
  \AtoA & \Ba             & 0               & 0              & \B             \\
  \AtoB & 0               & 0               & -\Br           & 0              \\
  \BtoA & 0               & -\Br            & 0              & 0              \\
  \BtoB & \B              & 0               & 0              & \Ba            \\
}
\end{eqnarray*}
\\
These matrices factorize into ``spin conserved'' $(\mathbf{A', B'})$ and
``spin-unconserved'' $(\mathbf{A'', B''})$ parts, to use the language of Seeger
and Pople. The spin conserved matrices are given by

\begin{eqnarray*}
  \mathbf{A'}&=&\kbordermatrix{
        & \AtoA           & \BtoB          \\
  \AtoA & \e\diag + \Aa   & \Ap            \\
  \BtoB & \Ap             & \e\diag + \Aa  \\
}
\end{eqnarray*}
\begin{eqnarray*}
  \mathbf{B'}&=&\kbordermatrix{
        & \AtoA           & \BtoB          \\
  \AtoA & \Ba             & \B             \\
  \BtoB & \B              & \Ba            \\
}
\end{eqnarray*}
\\
while the spin-unconserved matrices are given by:
\begin{eqnarray*}
  \mathbf{A''}&=&\kbordermatrix{
        & \AtoB           & \BtoA          \\
  \AtoB & \e\diag - \App  & 0              \\
  \BtoA & 0               & \e\diag - \App \\
}
\end{eqnarray*}

\begin{eqnarray*}
  \mathbf{B''}&=&\kbordermatrix{
        & \AtoB           & \BtoA  \\
  \AtoB & 0               & -\Br   \\
  \BtoA & -\Br            & 0      \\
}
\end{eqnarray*}
\\
Thus the spin conserved molecular orbital hessian, $\mathbf{H'}$ is given by:
\begin{eqnarray*}
  \mathbf{H'}&=&\kbordermatrix{
        & \AtoA             & \BtoB            & \AtoA             & \BtoB            \\
  \AtoA & \e\diag + \Aa     & \Ap              & \Ba               & \B               \\
  \BtoB & \Ap               & \e\diag + \Aa    & \B                & \Ba              \\
  \AtoA & \Ba^*             & \B^*             & \e\diag + \Aa^*   & \Ap^*            \\
  \BtoB & \B^*              & \Ba^*            & \Ap^*             & \e\diag + \Aa^*  \\
}
\end{eqnarray*}
\\
and the spin unconserved molecular orbital hessian, $\mathbf{H''}$ is given by:
\begin{eqnarray*}
  \mathbf{H''}&=&\kbordermatrix{
        & \AtoB           & \BtoA              & \AtoB             & \BtoA            \\
  \AtoB & \e\diag - \App  & 0                  & 0                 & -\Br             \\
  \BtoA & 0               & \e\diag - \App     & -\Br              & 0                \\
  \AtoB & 0                 & -\Br^*           & \e\diag - \App^*  & 0                \\
  \BtoA & -\Br^*            & 0                & 0                 & \e\diag - \App^* \\
}
\end{eqnarray*}
\\

This matrix factorizes into to two equivalent matrices,
\begin{eqnarray*}
  \mathbf{H''}&=&\kbordermatrix{
        & \AtoB           &\BtoA            \\
  \AtoB & \e\diag - \App  & -\Br             \\
  \BtoA & -\Br^*          & \e\diag - \App^* \\
}
\end{eqnarray*}

And in this form it is entirely equivalent to the RHF-UHF stability
matrix, $\mathbf{{}^3H'}$ defined in equations 35 and 36 of
Seeger/Pople\cite{Seeger1977}. This is where I suspect I've made a mistake.
\\

\section{Proof of Real-Valued A and B}
In the case of the Homogeneous electron gas,
the two electron integral is given by
(eq. 12 of~\cite{Delyon2008} and p. 16 of~\cite{Guiliani2005}):

\begin{subequations}
\begin{align}
\braket{\vec{k}, \vec{k}'|\vec{k}'',\vec{k} '''}\stackrel{\text{2D, 3D}}{=}&
	\begin{cases}
	\frac{\pi}{\Omega}\frac{2^{D-1}}{|\vec{k}-\vec{k}''|^{D-1}}
	& \vec{k}''' = \vec{k}+\vec{k}'-\vec{k}'' \textbf{ and } |\vec{k}-\vec{k}''| \neq 0 \\
	0
	& \text{else}
	\end{cases}
\\ \nonumber \\
\braket{k, k'|k'',k'''}\stackrel{\text{1D}}{=}&
	\begin{cases}
	e^{|k-k''|^2a^2}\text{Ei}(-|k-k''|^2a^2)\text{;}
	& k''' = k + k'-k'' \textbf{ and } |k-k''| \neq 0 \\
	0\text{;}
	& \text{else}
	\end{cases}
\end{align}
\end{subequations}

The two electron integrals are always real-valued. Therefore
$\mathbf{A} = \mathbf{A}^*$ and $\mathbf{B} = \mathbf{B}^*$

So far I have not used this to simplify anything, but it is true.

\section{References}
\bibliography{../heg_references}
\end{document}

### 2017-01-16 HFS/src/calc_parameters.cpp

@@ -58,7 +58,6 @@ namespace HFS {
                    ) {
         arma::uword N = Nk - 1;  // Unique Brillioun Zone
         arma::uword Nrows = std::pow(N, NDIM);
-        //states.set_size(Nrows, NDIM);
         arma::mat states(Nrows, NDIM);
 
         if (NDIM == 1) {
@@ -167,17 +166,17 @@ namespace HFS {
                                  - HFS::occ_energies(HFS::excitations(i, 0));
         }
 
+        // Sort ascending, these are the diagonals of the orbital hessian
         arma::uvec indices = arma::sort_index(HFS::exc_energies);
         HFS::exc_energies = HFS::exc_energies(indices);
         HFS::excitations = HFS::excitations.rows(indices);
     }
 
-    /* NEED 3D VERSION THO*/
 
     #if NDIM == 2
         void calcVirNTo1Map() {
             HFS::vir_N_to_1_mat.set_size(HFS::Nk-1, HFS::Nk-1);
-            HFS::vir_N_to_1_mat.fill(HFS::Nvir+1); // will make errors if accessing wrong one
+            HFS::vir_N_to_1_mat.fill(HFS::Nvir+1); // this causes indexing errors in the event of misuse to help debug
             for (arma::uword i=0; i < HFS::Nvir; ++i){
                 HFS::vir_N_to_1_mat(HFS::vir_states(i, 0), HFS::vir_states(i, 1)) = i;
             }
@@ -185,7 +184,7 @@ namespace HFS {
     #elif NDIM == 3
         void calcVirNTo1Map() {
         HFS::vir_N_to_1_mat.set_size(HFS::Nk-1, HFS::Nk-1, HFS::Nk-1);
-        HFS::vir_N_to_1_mat.fill(HFS::Nvir+1); // will make errors if accessing wrong one
+        HFS::vir_N_to_1_mat.fill(HFS::Nvir+1); // this causes indexing errors in the event of misuse to help debug
         for (arma::uword i=0; i < HFS::Nvir; ++i){
             HFS::vir_N_to_1_mat(HFS::vir_states(i, 0), HFS::vir_states(i, 1), HFS::vir_states(i, 2)) = i;
             }
@@ -194,7 +193,7 @@ namespace HFS {
 
     void calcInverseExcitationMap() {
         HFS::inv_exc_mat.set_size(HFS::Nocc, HFS::Nvir);
[…]

### 2017-01-16 doc/papers/summary/HFStability-summary.tex

--- 2017-01-16 doc/papers/matrixproperties/MatrixProperties.tex
@@
 \documentclass{revtex4}
-\usepackage[margin=1in, paperheight=1in, paperwidth=1in]{geometry}  % doesn't compile w/o width, height
-\geometry{
- a4paper,
- total={170mm,257mm},
- left=15mm,
- top=5mm,
-}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{kbordermatrix}
-\usepackage{braket}
-\usepackage{xcolor}
-
-\definecolor{myred}{HTML}{CC5803}
-\definecolor{myblue}{HTML}{204B57}
-
-\newcommand{\Ap}{\textcolor{myred}{\braket{aj|ib}}}
-\newcommand{\App}{\textcolor{myred}{\braket{aj|bi}}}
-\newcommand{\Aa}{\textcolor{myred}{\braket{aj||ib}}}
-\newcommand{\B}{\textcolor{myblue}{\braket{ab|ij}}}
-\newcommand{\Br}{\textcolor{myblue}{\braket{ab|ji}}}
-\newcommand{\Ba}{\textcolor{myblue}{\braket{ab||ij}}}
-
-\newcommand{\AtoB}{\mathbf{\alpha\rightarrow\beta}}
-\newcommand{\BtoA}{\mathbf{\beta\rightarrow\alpha}}
-\newcommand{\AtoA}{\mathbf{\alpha\rightarrow\alpha}}
-\newcommand{\BtoB}{\mathbf{\beta\rightarrow\beta}}
-\newcommand{\e}{\textcolor{myred}{\left(\epsilon_a-\epsilon_i\right)}}
-\newcommand{\diag}{\textcolor{myred}{\delta_{ij}\delta_{ab}}}
+%\usepackage{amsmath}
+%\usepackage{amssymb}
+%\usepackage{graphicx}
 
 \begin{document}
-\title{Notes on Matrix Factorization for Hartree-Fock Stability of HEG}
+\title{Summary Hartree-Fock Stability of HEG}
 \author{Evan Curtin}
@@
 
-\section{Orbital Hessian Factorization}
-According to Seeger and Pople\cite{Seeger1977}, (and many other sources) the molecular orbital
-Hessian has the form,
-\begin{eqnarray*}
-\mathbf{H} =
-  \begin{bmatrix}
-    \mathbf{A}   & \mathbf{B}   \\
-    \mathbf{B^*} & \mathbf{A^*} \\
-  \end{bmatrix}
-\end{eqnarray*}
-
-Where the matrices denoted by $\mathbf{A}$ and $\mathbf{B}$ are given by,
-
-\begin{eqnarray*}
-  A_{st} &=& \e\diag -  \Aa \\
-  B_{st} &=& \Ba         \\
-\end{eqnarray*}
-
-The color is to help keep track of which portions of the matrices come from
-$\mathbf{A}$ and $\mathbf{B}$.
-The integration is over spin and spatial coordinates. In the case of
-a stationary UHF solution, the matrices $\mathbf{A}$ and $\mathbf{B}$ have the
-following forms, after integrating over spin:
-
-\begin{eqnarray*}
-  \mathbf{A}&=&\kbordermatrix{
-        & \AtoA           & \AtoB           & \BtoA          & \BtoB          \\
-  \AtoA & \e\diag + \Aa   & 0               & 0              & \Ap            \\
-  \AtoB & 0               & \e\diag - \App  & 0              & 0              \\
-  \BtoA & 0               & 0               & \e\diag - \App & 0              \\
-  \BtoB & \Ap             & 0               & 0              & \e\diag + \Aa  \\
-}
-\end{eqnarray*}
-
-\begin{eqnarray*}
-  \mathbf{B}&=&\kbordermatrix{
-        & \AtoA           & \AtoB           & \BtoA          & \BtoB          \\
-  \AtoA & \Ba             & 0               & 0              & \B             \\
-  \AtoB & 0               & 0               & -\Br           & 0              \\
-  \BtoA & 0               & -\Br            & 0              & 0              \\
-  \BtoB & \B              & 0               & 0              & \Ba            \\
-}
-\end{eqnarray*}
-\\
-These matrices factorize into ``spin conserved'' $(\mathbf{A', B'})$ and
-``spin-unconserved'' $(\mathbf{A'', B''})$ parts, to use the language of Seeger
-and Pople. The spin conserved matrices are given by
-
-\begin{eqnarray*}
-  \mathbf{A'}&=&\kbordermatrix{
-        & \AtoA           & \BtoB          \\
-  \AtoA & \e\diag + \Aa   & \Ap            \\
-  \BtoB & \Ap             & \e\diag + \Aa  \\
-}
-\end{eqnarray*}
-\begin{eqnarray*}
-  \mathbf{B'}&=&\kbordermatrix{
-        & \AtoA           & \BtoB          \\
-  \AtoA & \Ba             & \B             \\
-  \BtoB & \B              & \Ba            \\
-}
-\end{eqnarray*}
-\\
-while the spin-unconserved matrices are given by:
-\begin{eqnarray*}
-  \mathbf{A''}&=&\kbordermatrix{
-        & \AtoB           & \BtoA          \\
-  \AtoB & \e\diag - \App  & 0              \\
-  \BtoA & 0               & \e\diag - \App \\
-}
-\end{eqnarray*}
-
-\begin{eqnarray*}
-  \mathbf{B''}&=&\kbordermatrix{
-        & \AtoB           & \BtoA  \\
-  \AtoB & 0               & -\Br   \\
-  \BtoA & -\Br            & 0      \\
-}
-\end{eqnarray*}
-\\
-Thus the spin conserved molecular orbital hessian, $\mathbf{H'}$ is given by:
-\begin{eqnarray*}
-  \mathbf{H'}&=&\kbordermatrix{
-        & \AtoA             & \BtoB            & \AtoA             & \BtoB            \\
-  \AtoA & \e\diag + \Aa     & \Ap              & \Ba               & \B               \\
-  \BtoB & \Ap               & \e\diag + \Aa    & \B                & \Ba              \\
-  \AtoA & \Ba^*             & \B^*             & \e\diag + \Aa^*   & \Ap^*            \\
-  \BtoB & \B^*              & \Ba^*            & \Ap^*             & \e\diag + \Aa^*  \\
-}
-\end{eqnarray*}
-\\
-and the spin unconserved molecular orbital hessian, $\mathbf{H''}$ is given by:
-\begin{eqnarray*}
-  \mathbf{H''}&=&\kbordermatrix{
-        & \AtoB           & \BtoA              & \AtoB             & \BtoA            \\
-  \AtoB & \e\diag - \App  & 0                  & 0                 & -\Br             \\
-  \BtoA & 0               & \e\diag - \App     & -\Br              & 0                \\
-  \AtoB & 0                 & -\Br^*           & \e\diag - \App^*  & 0                \\
-  \BtoA & -\Br^*            & 0                & 0                 & \e\diag - \App^* \\
-}
-\end{eqnarray*}
-\\
-
-This matrix factorizes into to two equivalent matrices,
-\begin{eqnarray*}
-  \mathbf{H''}&=&\kbordermatrix{
-        & \AtoB           &\BtoA            \\
-  \AtoB & \e\diag - \App  & -\Br             \\
-  \BtoA & -\Br^*          & \e\diag - \App^* \\
-}
-\end{eqnarray*}
-
-And in this form it is entirely equivalent to the RHF-UHF stability
-matrix, $\mathbf{{}^3H'}$ defined in equations 35 and 36 of
-Seeger/Pople\cite{Seeger1977}. This is where I suspect I've made a mistake.
-\\
-
-\section{Proof of Real-Valued A and B}
-In the case of the Homogeneous electron gas,
-the two electron integral is given by
-(eq. 12 of~\cite{Delyon2008} and p. 16 of~\cite{Guiliani2005}):
-
-\begin{subequations}
-\begin{align}
-\braket{\vec{k}, \vec{k}'|\vec{k}'',\vec{k} '''}\stackrel{\text{2D, 3D}}{=}&
-	\begin{cases}
-	\frac{\pi}{\Omega}\frac{2^{D-1}}{|\vec{k}-\vec{k}''|^{D-1}}
-	& \vec{k}''' = \vec{k}+\vec{k}'-\vec{k}'' \textbf{ and } |\vec{k}-\vec{k}''| \neq 0 \\
-	0
-	& \text{else}
-	\end{cases}
-\\ \nonumber \\
-\braket{k, k'|k'',k'''}\stackrel{\text{1D}}{=}&
-	\begin{cases}
-	e^{|k-k''|^2a^2}\text{Ei}(-|k-k''|^2a^2)\text{;}
-	& k''' = k + k'-k'' \textbf{ and } |k-k''| \neq 0 \\
-	0\text{;}
-	& \text{else}
-	\end{cases}
-\end{align}
-\end{subequations}
-
-The two electron integrals are always real-valued. Therefore
-$\mathbf{A} = \mathbf{A}^*$ and $\mathbf{B} = \mathbf{B}^*$
-
-So far I have not used this to simplify anything, but it is true.
+\section{Background}
+\cite{Guiliani2005}
 
@@
 \bibliography{../heg_references}
+
 \end{document}

### 2017-01-16 HFS/src/calc_parameters.cpp
got out of the pickle

@@ -58,6 +58,7 @@ namespace HFS {
                    ) {
         arma::uword N = Nk - 1;  // Unique Brillioun Zone
         arma::uword Nrows = std::pow(N, NDIM);
+        //states.set_size(Nrows, NDIM);
         arma::mat states(Nrows, NDIM);
 
         if (NDIM == 1) {
@@ -166,17 +167,17 @@ namespace HFS {
                                  - HFS::occ_energies(HFS::excitations(i, 0));
         }
 
-        // Sort ascending, these are the diagonals of the orbital hessian
         arma::uvec indices = arma::sort_index(HFS::exc_energies);
         HFS::exc_energies = HFS::exc_energies(indices);
         HFS::excitations = HFS::excitations.rows(indices);
     }
 
+    /* NEED 3D VERSION THO*/
 
     #if NDIM == 2
         void calcVirNTo1Map() {
             HFS::vir_N_to_1_mat.set_size(HFS::Nk-1, HFS::Nk-1);
-            HFS::vir_N_to_1_mat.fill(HFS::Nvir+1); // this causes indexing errors in the event of misuse to help debug
+            HFS::vir_N_to_1_mat.fill(HFS::Nvir+1); // will make errors if accessing wrong one
             for (arma::uword i=0; i < HFS::Nvir; ++i){
                 HFS::vir_N_to_1_mat(HFS::vir_states(i, 0), HFS::vir_states(i, 1)) = i;
             }
@@ -184,7 +185,7 @@ namespace HFS {
     #elif NDIM == 3
         void calcVirNTo1Map() {
         HFS::vir_N_to_1_mat.set_size(HFS::Nk-1, HFS::Nk-1, HFS::Nk-1);
-        HFS::vir_N_to_1_mat.fill(HFS::Nvir+1); // this causes indexing errors in the event of misuse to help debug
+        HFS::vir_N_to_1_mat.fill(HFS::Nvir+1); // will make errors if accessing wrong one
         for (arma::uword i=0; i < HFS::Nvir; ++i){
             HFS::vir_N_to_1_mat(HFS::vir_states(i, 0), HFS::vir_states(i, 1), HFS::vir_states(i, 2)) = i;
             }
@@ -193,7 +194,7 @@ namespace HFS {
 
     void calcInverseExcitationMap() {
         HFS::inv_exc_mat.set_size(HFS::Nocc, HFS::Nvir);
[…]

### 2017-01-20 doc/papers/summary/HFStability-summary.tex
STarted writing thee summary

@@
 \section{Background}
-\cite{Guiliani2005}
+    The Hartree-Fock procedure has been implemented the quantum many-body problem since its inception and remains the basis for many more advanced techniques even today.
+In general, the eigenstates of the Hartree-Fock Hamiltonian are solved self-consistently.
+However, this procedure ensures only that the solution is stationary with respect to the determined orbitals.
+A method for determining the stability of a Hartree-Fock solution was proposed by Thouless in 1960\cite{Thouless1960}.
+The condition for stability of a Hartree-Fock solution is equivalent to the conditions for unstable (complex frequency) many-body oscillations within the Random Phase Approximation (RPA).
+The condition was rederived into the expression familiar to quantum chemists by Čížek and Paldus in 1967\cite{Cizek1967}.
+Furthermore, the stability equations factorize depending on the symmetry of the Hartree-Fock eigenfunctions.
+To this end, Seeger and Pople outlined a hierarchical approach to systematically evaluate the stability of HF states in the restricted, unrestricted and generalized Hartree-Fock procedures\cite{Seeger1977}.
+Recently, the method has been used to aid the in search for the lowest energy Unrestricted Hartree-Fock (UHF) solutions in molecules, as well as the General Hartree-Fock (GHF) solutions in geometrically frustrated hydrogen rings which cannot conform even to the UHF scheme \cite{Pulay2016}\cite{Goings2015}.
+
+    The presence of GHF solutions to the Homogeneous Electron Gas which have lower energy than the RHF solutions was proven in the landmark paper by Overhauser\cite{Overhauser1962}.
+Later still, the ground state energies of the electron gas were found to great accuracy by Ceperley and Alder \cite{Ceperley1980}.
+In the past few years, phase diagrams have been determined for the HEG in 2 and 3 dimensions\cite{Delyon2008}\cite{Bernu2011}\cite{Baguet2013}.
+In all cases (to my knowledge) the phase diagrams are made by computing the energies of the polarized and unpolarized states, and comparing them.
 

### 2017-01-20 doc/html/search/all_0.js

@@ -1,4 +1,4 @@
 var searchData=
 [
-  ['_5f_5ffunct_5f_5f',['__FUNCT__',['../SLEPcWrapper_8hpp.html#ae60511a9aa5cbf216a00a1bb81006bc5',1,'SLEPcWrapper.hpp']]]
+  ['_5f_5ffunct_5f_5f',['__FUNCT__',['../SLEPcWrapper_8cpp.html#ae60511a9aa5cbf216a00a1bb81006bc5',1,'SLEPcWrapper.cpp']]]
 ];

### 2017-01-20 doc/html/search/all_10.js

@@ -8,8 +8,8 @@ var searchData=
   ['setmatrixpropertiesfromcase',['setMatrixPropertiesFromCase',['../namespaceHFS.html#a89be9e6d2bf3960d3d17f1285b81f8fd',1,'HFS']]],
   ['settol',['SetTol',['../classSLEPc_1_1EpS.html#a308c8b31ae0fd83df2efb7ca3ef005e4',1,'SLEPc::EpS']]],
   ['shape',['shape',['../classndMap.html#a9bef976acf4d891f3ed06e4ec5c88e4c',1,'ndMap']]],
-  ['size',['size',['../classSLEPc_1_1EpS.html#afbe54da7b13ba3b8aaa39d8a5b84819c',1,'SLEPc::EpS']]],
   ['slepc',['SLEPc',['../namespaceSLEPc.html',1,'']]],
+  ['slepcwrapper_2ecpp',['SLEPcWrapper.cpp',['../SLEPcWrapper_8cpp.html',1,'']]],
   ['slepcwrapper_2ehpp',['SLEPcWrapper.hpp',['../SLEPcWrapper_8hpp.html',1,'']]],
   ['smallnumber',['SMALLNUMBER',['../parameters_8hpp.html#a012a7b5930f872510b4ffb59ff2ce8f1',1,'parameters.hpp']]],
   ['solve',['Solve',['../classSLEPc_1_1EpS.html#a3131bcf66e91d7449b1cc97179a3e5e8',1,'SLEPc::EpS']]],

### 2017-01-20 doc/html/search/all_12.js

@@ -1,7 +1,6 @@
 var searchData=
 [
   ['vir_5fenergies',['vir_energies',['../namespaceHFS.html#a41112c1039ebb38e01c99f5565a401fd',1,'HFS']]],
-  ['vir_5fn_5fto_5f1_5fmat',['vir_N_to_1_mat',['../namespaceHFS.html#aa9ed0b0fe5edf14a97dd1a41e6f0c7ab',1,'HFS']]],
   ['vir_5fstates',['vir_states',['../namespaceHFS.html#a35c086cdd8d9c5cf5f3853abfb782c9c',1,'HFS']]],
   ['virindextok',['virIndexToK',['../namespaceHFS.html#ab58c841ce2b7acadecc412cb5c5cbd28',1,'HFS']]],
   ['vol',['vol',['../namespaceHFS.html#a88874225b8d87c1f8589daee8b53a498',1,'HFS']]]

### 2017-01-20 doc/html/search/all_7.js

@@ -1,4 +1,5 @@
 var searchData=
 [
+  ['getrowvals',['getRowVals',['../SLEPcWrapper_8cpp.html#ae2d6f5e5869e2bc9422b7249532ef669',1,'getRowVals(std::vector&lt; PetscScalar &gt; &amp;vals, std::vector&lt; PetscInt &gt; &amp;idx, PetscInt irow):&#160;SLEPcWrapper.cpp'],['../SLEPcWrapper_8hpp.html#ae2d6f5e5869e2bc9422b7249532ef669',1,'getRowVals(std::vector&lt; PetscScalar &gt; &amp;vals, std::vector&lt; PetscInt &gt; &amp;idx, PetscInt irow):&#160;SLEPcWrapper.cpp']]],
   ['ground_5fstate_5fdegeneracy',['ground_state_degeneracy',['../namespaceHFS.html#acee61993eb642a4248f00c05d14f9c3b',1,'HFS']]]
 ];

### 2017-01-20 doc/html/search/all_a.js

@@ -4,5 +4,5 @@ var searchData=
   ['kgrid',['kgrid',['../namespaceHFS.html#ae71f0b00606f4ff65d3fe2f791366c9f',1,'HFS']]],
   ['kmax',['kmax',['../namespaceHFS.html#a81a7123519449b323213f54532823651',1,'HFS']]],
   ['kroneckerdelta',['kroneckerDelta',['../namespaceHFS.html#a503d2522f8c6e21699d6d82239a49900',1,'HFS']]],
-  ['ktoindex',['kToIndex',['../namespaceHFS.html#a44f9ae53d29b22abe92f31d7e720cb1f',1,'HFS::kToIndex(arma::vec &amp;k)'],['../namespaceHFS.html#ab92c0ece13e14b19519347acb64c57f8',1,'HFS::kToIndex(arma::mat &amp;k)']]]
+  ['ktoindex',['kToIndex',['../namespaceHFS.html#a1915ca0c3faa2386d4f8aa2241348aa8',1,'HFS::kToIndex(arma::vec &amp;k, arma::uvec &amp;idx)'],['../namespaceHFS.html#ab92c0ece13e14b19519347acb64c57f8',1,'HFS::kToIndex(arma::mat &amp;k)']]]
 ];

### 2017-01-20 doc/html/search/all_b.js

@@ -3,6 +3,7 @@ var searchData=
   ['main',['main',['../main_8cpp.html#a0ddf1224851353fc92bfbff6f499fa97',1,'main(int argc, char *argv[]):&#160;main.cpp'],['../main_8hpp.html#a0ddf1224851353fc92bfbff6f499fa97',1,'main(int argc, char *argv[]):&#160;main.cpp']]],
   ['main_2ecpp',['main.cpp',['../main_8cpp.html',1,'']]],
   ['main_2ehpp',['main.hpp',['../main_8hpp.html',1,'']]],
+  ['matbuild',['MatBuild',['../classSLEPc_1_1EpS.html#a3fb3ca58c318e5b76aad8535e6d7451d',1,'SLEPc::EpS']]],
   ['matrix',['matrix',['../classSLEPc_1_1EpS.html#a9cb123016f1fca63edf9c952a92b2b3f',1,'SLEPc::EpS']]],
   ['matrix_5ffunc',['Matrix_func',['../namespaceHFS.html#a8da52f83851e9a597fdcf48768302e82',1,'HFS']]],
   ['matrix_5futils_2ecpp',['matrix_utils.cpp',['../matrix__utils_8cpp.html',1,'']]],
@@ -18,7 +19,8 @@ var searchData=
   ['matrixvectorproductbprimeoffdiag',['matrixVectorProductBprimeOffDiag',['../namespaceHFS.html#a57f02f7dc50865617202e93020ca52ae',1,'HFS']]],
   ['matrixvectorproducthprime',['matrixVectorProductHprime',['../namespaceHFS.html#a68f0b2cadc41bdb31a43c7dc9140b71d',1,'HFS']]],
   ['matrixvectorproductworks',['matrixVectorProductWorks',['../namespaceHFS.html#aacb6df6ae8713b9229429ff0fc135832',1,'HFS']]],
-  ['matvec_5fproduct',['matvec_product',['../namespaceSLEPc.html#ad4b71020e03f0ae8edabbeaf4719a94d',1,'SLEPc']]],
+  ['matsetrowvalues',['MatSetRowValues',['../classSLEPc_1_1EpS.html#a6d36f3d319bb855a073de66286b000d7',1,'SLEPc::EpS']]],
+  ['matvec_5fproduct',['matvec_product',['../namespaceSLEPc.html#acb4c95effb133acddb51349b1f42bc89',1,'SLEPc']]],
[…]

### 2017-01-20 doc/html/search/all_c.js

@@ -15,6 +15,7 @@ var searchData=
   ['nk',['Nk',['../namespaceHFS.html#ac59f2cad29a15b4cdae8c6dce68a7ac4',1,'HFS']]],
   ['nmat',['Nmat',['../namespaceHFS.html#aac6e3546513e6cb2d94f7a3e16777a5f',1,'HFS']]],
   ['nocc',['Nocc',['../namespaceHFS.html#af2aad894a643614991187b63833924dc',1,'HFS']]],
+  ['nprocs',['nprocs',['../classSLEPc_1_1EpS.html#a61db342ee803f0b2d41770cc04c2f946',1,'SLEPc::EpS']]],
   ['num_5fguess_5fevecs',['num_guess_evecs',['../namespaceHFS.html#a3dbdbd199fc80d4585e65d44bf6d899b',1,'HFS']]],
   ['nvir',['Nvir',['../namespaceHFS.html#a64210d2084db946dd9b8a43e16e2a64a',1,'HFS']]]
 ];

### 2017-01-20 doc/html/search/all_d.js

@@ -2,7 +2,7 @@ var searchData=
 [
   ['occ_5fenergies',['occ_energies',['../namespaceHFS.html#a66cb01f79511cbb0e41978af17da3081',1,'HFS']]],
   ['occ_5fstates',['occ_states',['../namespaceHFS.html#a3a60013223811e72fa7e96b21e4bcd08',1,'HFS']]],
-  ['occindextok',['occIndexToK',['../namespaceHFS.html#aba6a1bc0264cb57d63459162509b4869',1,'HFS']]],
+  ['occindextok',['occIndexToK',['../namespaceHFS.html#a0d2a21a1c3ec762459fe24b99cfb59de',1,'HFS']]],
   ['operator_28_29',['operator()',['../classndMap.html#a0c509bca728e381885952d7df5dd1c98',1,'ndMap']]],
   ['outputfilename',['OutputFileName',['../namespaceHFS.html#afe22eb3e75352bdc6b10c71df0c18065',1,'HFS']]]
 ];

### 2017-01-20 doc/html/search/all_e.js

@@ -3,7 +3,7 @@ var searchData=
   ['parameters_2ecpp',['parameters.cpp',['../parameters_8cpp.html',1,'']]],
   ['parameters_2ehpp',['parameters.hpp',['../parameters_8hpp.html',1,'']]],
   ['petsc_5fmatvecprod',['Petsc_MatVecProd',['../namespaceSLEPc.html#a6432301c8ecfaa2bdb1bbdb5ab6ff5cf',1,'SLEPc']]],
-  ['petscmatcreate',['PETSCMatCreate',['../classSLEPc_1_1EpS.html#a69cdc4e49343d6226785543b1b56f81e',1,'SLEPc::EpS']]],
+  ['petscmatshellcreate',['PETSCMatShellCreate',['../classSLEPc_1_1EpS.html#a83a18f165a05e576355d281b149d76c8',1,'SLEPc::EpS']]],
   ['pi',['PI',['../parameters_8hpp.html#a598a3330b3c21701223ee0ca14316eca',1,'parameters.hpp']]],
   ['print',['print',['../classndMap.html#ae6cbee96a5519b0cfc3ef1777a2d5bf9',1,'ndMap::print()'],['../classSLEPc_1_1EpS.html#ac57a23eae487e3cd00268fbf3b9c4bf9',1,'SLEPc::EpS::print()'],['../fileIO_8cpp.html#ad61844ab25ea35139950e67e9693bc9f',1,'PRINT():&#160;fileIO.cpp']]],
   ['printevals',['PrintEvals',['../classSLEPc_1_1EpS.html#a76d8479274e15f6062a48fdd7f139cbb',1,'SLEPc::EpS']]],

### 2017-01-20 doc/html/search/files_7.js

@@ -1,4 +1,5 @@
 var searchData=
 [
+  ['slepcwrapper_2ecpp',['SLEPcWrapper.cpp',['../SLEPcWrapper_8cpp.html',1,'']]],
   ['slepcwrapper_2ehpp',['SLEPcWrapper.hpp',['../SLEPcWrapper_8hpp.html',1,'']]]
 ];

### 2017-01-20 doc/html/search/functions_10.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['writeoutput',['writeOutput',['../namespaceHFS.html#ae9c1c188d58d8d87e679d14ce1ee5cf5',1,'HFS']]]
+];

### 2017-01-20 doc/html/search/functions_5.js

@@ -1,4 +1,4 @@
 var searchData=
 [
-  ['isoccupied',['isOccupied',['../namespaceHFS.html#adeeab45bb53af395c9615975611aa498',1,'HFS']]]
+  ['getrowvals',['getRowVals',['../SLEPcWrapper_8cpp.html#ae2d6f5e5869e2bc9422b7249532ef669',1,'getRowVals(std::vector&lt; PetscScalar &gt; &amp;vals, std::vector&lt; PetscInt &gt; &amp;idx, PetscInt irow):&#160;SLEPcWrapper.cpp'],['../SLEPcWrapper_8hpp.html#ae2d6f5e5869e2bc9422b7249532ef669',1,'getRowVals(std::vector&lt; PetscScalar &gt; &amp;vals, std::vector&lt; PetscInt &gt; &amp;idx, PetscInt irow):&#160;SLEPcWrapper.cpp']]]
 ];

### 2017-01-20 doc/html/search/functions_6.js

@@ -1,5 +1,4 @@
 var searchData=
 [
-  ['kroneckerdelta',['kroneckerDelta',['../namespaceHFS.html#a503d2522f8c6e21699d6d82239a49900',1,'HFS']]],
-  ['ktoindex',['kToIndex',['../namespaceHFS.html#a44f9ae53d29b22abe92f31d7e720cb1f',1,'HFS::kToIndex(arma::vec &amp;k)'],['../namespaceHFS.html#ab92c0ece13e14b19519347acb64c57f8',1,'HFS::kToIndex(arma::mat &amp;k)']]]
+  ['isoccupied',['isOccupied',['../namespaceHFS.html#adeeab45bb53af395c9615975611aa498',1,'HFS']]]
 ];

### 2017-01-20 doc/html/search/functions_7.js

@@ -1,15 +1,5 @@
 var searchData=
 [
-  ['main',['main',['../main_8cpp.html#a0ddf1224851353fc92bfbff6f499fa97',1,'main(int argc, char *argv[]):&#160;main.cpp'],['../main_8hpp.html#a0ddf1224851353fc92bfbff6f499fa97',1,'main(int argc, char *argv[]):&#160;main.cpp']]],
-  ['matrixvectorproduct3a',['matrixVectorProduct3A',['../namespaceHFS.html#a1101164c383e43fda467247c753f24c4',1,'HFS']]],
-  ['matrixvectorproduct3b',['matrixVectorProduct3B',['../namespaceHFS.html#a2249a9e7a8d56695759507726ddc3b3a',1,'HFS']]],
-  ['matrixvectorproduct3h',['matrixVectorProduct3H',['../namespaceHFS.html#a11a0c36d5352f01f0ca7777d456b8a51',1,'HFS']]],
-  ['matrixvectorproductaprime',['matrixVectorProductAprime',['../namespaceHFS.html#a0e2adcb057f31e95cefc39cb1f624baa',1,'HFS']]],
-  ['matrixvectorproductaprimediag',['matrixVectorProductAprimeDiag',['../namespaceHFS.html#a62ed5c22c1e833d6255bf9967c541409',1,'HFS']]],
-  ['matrixvectorproductaprimeoffdiag',['matrixVectorProductAprimeOffDiag',['../namespaceHFS.html#ae03a2f2d7f2d3c68c5d62bf1b1dec42b',1,'HFS']]],
-  ['matrixvectorproductbprime',['matrixVectorProductBprime',['../namespaceHFS.html#ad59b5f5d10eff6d81d06d9e5d2bc0097',1,'HFS']]],
-  ['matrixvectorproductbprimediag',['matrixVectorProductBprimeDiag',['../namespaceHFS.html#a50fd8b726825cceb3689534d9cc56d21',1,'HFS']]],
-  ['matrixvectorproductbprimeoffdiag',['matrixVectorProductBprimeOffDiag',['../namespaceHFS.html#a57f02f7dc50865617202e93020ca52ae',1,'HFS']]],
-  ['matrixvectorproducthprime',['matrixVectorProductHprime',['../namespaceHFS.html#a68f0b2cadc41bdb31a43c7dc9140b71d',1,'HFS']]],
[…]

### 2017-01-20 doc/html/search/functions_8.js

@@ -1,4 +1,17 @@
 var searchData=
 [
-  ['ndmap',['ndMap',['../classndMap.html#ad75afaa1c4fdfd4e4bf7979dc542ed51',1,'ndMap']]]
+  ['main',['main',['../main_8cpp.html#a0ddf1224851353fc92bfbff6f499fa97',1,'main(int argc, char *argv[]):&#160;main.cpp'],['../main_8hpp.html#a0ddf1224851353fc92bfbff6f499fa97',1,'main(int argc, char *argv[]):&#160;main.cpp']]],
+  ['matbuild',['MatBuild',['../classSLEPc_1_1EpS.html#a3fb3ca58c318e5b76aad8535e6d7451d',1,'SLEPc::EpS']]],
+  ['matrixvectorproduct3a',['matrixVectorProduct3A',['../namespaceHFS.html#a1101164c383e43fda467247c753f24c4',1,'HFS']]],
+  ['matrixvectorproduct3b',['matrixVectorProduct3B',['../namespaceHFS.html#a2249a9e7a8d56695759507726ddc3b3a',1,'HFS']]],
+  ['matrixvectorproduct3h',['matrixVectorProduct3H',['../namespaceHFS.html#a11a0c36d5352f01f0ca7777d456b8a51',1,'HFS']]],
+  ['matrixvectorproductaprime',['matrixVectorProductAprime',['../namespaceHFS.html#a0e2adcb057f31e95cefc39cb1f624baa',1,'HFS']]],
+  ['matrixvectorproductaprimediag',['matrixVectorProductAprimeDiag',['../namespaceHFS.html#a62ed5c22c1e833d6255bf9967c541409',1,'HFS']]],
+  ['matrixvectorproductaprimeoffdiag',['matrixVectorProductAprimeOffDiag',['../namespaceHFS.html#ae03a2f2d7f2d3c68c5d62bf1b1dec42b',1,'HFS']]],
+  ['matrixvectorproductbprime',['matrixVectorProductBprime',['../namespaceHFS.html#ad59b5f5d10eff6d81d06d9e5d2bc0097',1,'HFS']]],
+  ['matrixvectorproductbprimediag',['matrixVectorProductBprimeDiag',['../namespaceHFS.html#a50fd8b726825cceb3689534d9cc56d21',1,'HFS']]],
[…]

### 2017-01-20 doc/html/search/functions_9.js

@@ -1,5 +1,4 @@
 var searchData=
 [
-  ['occindextok',['occIndexToK',['../namespaceHFS.html#aba6a1bc0264cb57d63459162509b4869',1,'HFS']]],
-  ['operator_28_29',['operator()',['../classndMap.html#a0c509bca728e381885952d7df5dd1c98',1,'ndMap']]]
+  ['ndmap',['ndMap',['../classndMap.html#ad75afaa1c4fdfd4e4bf7979dc542ed51',1,'ndMap']]]
 ];

### 2017-01-20 doc/html/search/functions_a.js

@@ -1,8 +1,5 @@
 var searchData=
 [
-  ['petsc_5fmatvecprod',['Petsc_MatVecProd',['../namespaceSLEPc.html#a6432301c8ecfaa2bdb1bbdb5ab6ff5cf',1,'SLEPc']]],
-  ['petscmatcreate',['PETSCMatCreate',['../classSLEPc_1_1EpS.html#a69cdc4e49343d6226785543b1b56f81e',1,'SLEPc::EpS']]],
-  ['print',['print',['../classndMap.html#ae6cbee96a5519b0cfc3ef1777a2d5bf9',1,'ndMap::print()'],['../classSLEPc_1_1EpS.html#ac57a23eae487e3cd00268fbf3b9c4bf9',1,'SLEPc::EpS::print()']]],
-  ['printevals',['PrintEvals',['../classSLEPc_1_1EpS.html#a76d8479274e15f6062a48fdd7f139cbb',1,'SLEPc::EpS']]],
-  ['printevecs',['PrintEvecs',['../classSLEPc_1_1EpS.html#a39447a80d7ec660a073c4f60759bf030',1,'SLEPc::EpS']]]
+  ['occindextok',['occIndexToK',['../namespaceHFS.html#a0d2a21a1c3ec762459fe24b99cfb59de',1,'HFS']]],
+  ['operator_28_29',['operator()',['../classndMap.html#a0c509bca728e381885952d7df5dd1c98',1,'ndMap']]]
 ];

### 2017-01-20 doc/html/search/functions_b.js

@@ -1,4 +1,8 @@
 var searchData=
 [
-  ['recursiveprint',['recursivePrint',['../classndMap.html#aadc1dea9baff4c814b564e775f0b02e8',1,'ndMap']]]
+  ['petsc_5fmatvecprod',['Petsc_MatVecProd',['../namespaceSLEPc.html#a6432301c8ecfaa2bdb1bbdb5ab6ff5cf',1,'SLEPc']]],
+  ['petscmatshellcreate',['PETSCMatShellCreate',['../classSLEPc_1_1EpS.html#a83a18f165a05e576355d281b149d76c8',1,'SLEPc::EpS']]],
+  ['print',['print',['../classndMap.html#ae6cbee96a5519b0cfc3ef1777a2d5bf9',1,'ndMap::print()'],['../classSLEPc_1_1EpS.html#ac57a23eae487e3cd00268fbf3b9c4bf9',1,'SLEPc::EpS::print()']]],
+  ['printevals',['PrintEvals',['../classSLEPc_1_1EpS.html#a76d8479274e15f6062a48fdd7f139cbb',1,'SLEPc::EpS']]],
+  ['printevecs',['PrintEvecs',['../classSLEPc_1_1EpS.html#a39447a80d7ec660a073c4f60759bf030',1,'SLEPc::EpS']]]
 ];

### 2017-01-20 doc/html/search/functions_c.js

@@ -1,11 +1,4 @@
 var searchData=
 [
-  ['setblocksize',['SetBlockSize',['../classSLEPc_1_1EpS.html#a025b7ff78bea12b9703f5259723f0051',1,'SLEPc::EpS']]],
-  ['setdimensions',['SetDimensions',['../classSLEPc_1_1EpS.html#aebab063f863b3d0f06c6ecde32967e2c',1,'SLEPc::EpS']]],
-  ['setfromoptions',['SetFromOptions',['../classSLEPc_1_1EpS.html#ad1c775b02de040e8a2d0830e60fac468',1,'SLEPc::EpS']]],
-  ['setinitialspace',['SetInitialSpace',['../classSLEPc_1_1EpS.html#a61ecf73b341c1fafce98b64e507f34ad',1,'SLEPc::EpS']]],
-  ['setmatrixpropertiesfromcase',['setMatrixPropertiesFromCase',['../namespaceHFS.html#a89be9e6d2bf3960d3d17f1285b81f8fd',1,'HFS']]],
-  ['settol',['SetTol',['../classSLEPc_1_1EpS.html#a308c8b31ae0fd83df2efb7ca3ef005e4',1,'SLEPc::EpS']]],
-  ['solve',['Solve',['../classSLEPc_1_1EpS.html#a3131bcf66e91d7449b1cc97179a3e5e8',1,'SLEPc::EpS']]],
-  ['sttokikakjkb',['stToKiKaKjKb',['../namespaceHFS.html#a2f6abad39638c2049f3b4efacbff0544',1,'HFS']]]
+  ['recursiveprint',['recursivePrint',['../classndMap.html#aadc1dea9baff4c814b564e775f0b02e8',1,'ndMap']]]
 ];

### 2017-01-20 doc/html/search/functions_d.js

@@ -1,7 +1,11 @@
 var searchData=
 [
-  ['timematrixvectorproduct',['timeMatrixVectorProduct',['../namespaceHFS.html#aa84635b59cd45e7d90024bebcd7d8120',1,'HFS']]],
-  ['tofirstbrillouinzone',['toFirstBrillouinZone',['../namespaceHFS.html#a726bc0d67b1d7bad563af54054cac9de',1,'HFS']]],
-  ['twoelectron',['twoElectron',['../namespaceHFS.html#aebf2d4bfc246a61f45550177dcb3e3bf',1,'HFS']]],
-  ['twoelectronsafe',['twoElectronSafe',['../namespaceHFS.html#ae39771f18471b751fb03a15ba0f4d964',1,'HFS']]]
+  ['setblocksize',['SetBlockSize',['../classSLEPc_1_1EpS.html#a025b7ff78bea12b9703f5259723f0051',1,'SLEPc::EpS']]],
+  ['setdimensions',['SetDimensions',['../classSLEPc_1_1EpS.html#aebab063f863b3d0f06c6ecde32967e2c',1,'SLEPc::EpS']]],
+  ['setfromoptions',['SetFromOptions',['../classSLEPc_1_1EpS.html#ad1c775b02de040e8a2d0830e60fac468',1,'SLEPc::EpS']]],
+  ['setinitialspace',['SetInitialSpace',['../classSLEPc_1_1EpS.html#a61ecf73b341c1fafce98b64e507f34ad',1,'SLEPc::EpS']]],
+  ['setmatrixpropertiesfromcase',['setMatrixPropertiesFromCase',['../namespaceHFS.html#a89be9e6d2bf3960d3d17f1285b81f8fd',1,'HFS']]],
+  ['settol',['SetTol',['../classSLEPc_1_1EpS.html#a308c8b31ae0fd83df2efb7ca3ef005e4',1,'SLEPc::EpS']]],
+  ['solve',['Solve',['../classSLEPc_1_1EpS.html#a3131bcf66e91d7449b1cc97179a3e5e8',1,'SLEPc::EpS']]],
+  ['sttokikakjkb',['stToKiKaKjKb',['../namespaceHFS.html#a2f6abad39638c2049f3b4efacbff0544',1,'HFS']]]
 ];

### 2017-01-20 doc/html/search/functions_e.js

@@ -1,4 +1,7 @@
 var searchData=
 [
-  ['virindextok',['virIndexToK',['../namespaceHFS.html#ab58c841ce2b7acadecc412cb5c5cbd28',1,'HFS']]]
+  ['timematrixvectorproduct',['timeMatrixVectorProduct',['../namespaceHFS.html#aa84635b59cd45e7d90024bebcd7d8120',1,'HFS']]],
+  ['tofirstbrillouinzone',['toFirstBrillouinZone',['../namespaceHFS.html#a726bc0d67b1d7bad563af54054cac9de',1,'HFS']]],
+  ['twoelectron',['twoElectron',['../namespaceHFS.html#aebf2d4bfc246a61f45550177dcb3e3bf',1,'HFS']]],
+  ['twoelectronsafe',['twoElectronSafe',['../namespaceHFS.html#ae39771f18471b751fb03a15ba0f4d964',1,'HFS']]]
 ];

### 2017-01-20 doc/html/search/functions_f.js

@@ -1,4 +1,4 @@
 var searchData=
 [
-  ['writeoutput',['writeOutput',['../namespaceHFS.html#ae9c1c188d58d8d87e679d14ce1ee5cf5',1,'HFS']]]
+  ['virindextok',['virIndexToK',['../namespaceHFS.html#ab58c841ce2b7acadecc412cb5c5cbd28',1,'HFS']]]
 ];

### 2017-01-20 doc/html/search/searchdata.js

@@ -4,7 +4,7 @@ var indexSectionsWithContent =
   1: "en",
   2: "hs",
   3: "bcdfmnps",
-  4: "bcdefikmnoprstvw",
+  4: "bcdefgikmnoprstvw",
   5: "abcdefgikmnorstv",
   6: "_cehnpsw"
 };

### 2017-01-20 doc/html/search/variables_9.js

@@ -2,7 +2,7 @@ var searchData=
 [
   ['matrix',['matrix',['../classSLEPc_1_1EpS.html#a9cb123016f1fca63edf9c952a92b2b3f',1,'SLEPc::EpS']]],
   ['matrix_5ffunc',['Matrix_func',['../namespaceHFS.html#a8da52f83851e9a597fdcf48768302e82',1,'HFS']]],
-  ['matvec_5fproduct',['matvec_product',['../namespaceSLEPc.html#ad4b71020e03f0ae8edabbeaf4719a94d',1,'SLEPc']]],
+  ['matvec_5fproduct',['matvec_product',['../namespaceSLEPc.html#acb4c95effb133acddb51349b1f42bc89',1,'SLEPc']]],
   ['matvecproduct_5ffunc',['MatVecProduct_func',['../namespaceHFS.html#aeb892e3cb99f1f05467b63f923d3d9cb',1,'HFS']]],
   ['maxits',['maxits',['../classSLEPc_1_1EpS.html#a52c72a69548918f132ad0489ec68bb3e',1,'SLEPc::EpS']]],
   ['mv_5ftime',['Mv_time',['../namespaceHFS.html#abaa5d85b550c5d45be1ddadca4c10226',1,'HFS']]],

### 2017-01-20 doc/html/search/variables_a.js

@@ -12,6 +12,7 @@ var searchData=
   ['nk',['Nk',['../namespaceHFS.html#ac59f2cad29a15b4cdae8c6dce68a7ac4',1,'HFS']]],
   ['nmat',['Nmat',['../namespaceHFS.html#aac6e3546513e6cb2d94f7a3e16777a5f',1,'HFS']]],
   ['nocc',['Nocc',['../namespaceHFS.html#af2aad894a643614991187b63833924dc',1,'HFS']]],
+  ['nprocs',['nprocs',['../classSLEPc_1_1EpS.html#a61db342ee803f0b2d41770cc04c2f946',1,'SLEPc::EpS']]],
   ['num_5fguess_5fevecs',['num_guess_evecs',['../namespaceHFS.html#a3dbdbd199fc80d4585e65d44bf6d899b',1,'HFS']]],
   ['nvir',['Nvir',['../namespaceHFS.html#a64210d2084db946dd9b8a43e16e2a64a',1,'HFS']]]
 ];

### 2017-01-20 doc/html/search/variables_d.js

@@ -1,5 +1,4 @@
 var searchData=
 [
-  ['shape',['shape',['../classndMap.html#a9bef976acf4d891f3ed06e4ec5c88e4c',1,'ndMap']]],
-  ['size',['size',['../classSLEPc_1_1EpS.html#afbe54da7b13ba3b8aaa39d8a5b84819c',1,'SLEPc::EpS']]]
+  ['shape',['shape',['../classndMap.html#a9bef976acf4d891f3ed06e4ec5c88e4c',1,'ndMap']]]
 ];

### 2017-01-20 doc/html/search/variables_f.js

@@ -1,7 +1,6 @@
 var searchData=
 [
   ['vir_5fenergies',['vir_energies',['../namespaceHFS.html#a41112c1039ebb38e01c99f5565a401fd',1,'HFS']]],
-  ['vir_5fn_5fto_5f1_5fmat',['vir_N_to_1_mat',['../namespaceHFS.html#aa9ed0b0fe5edf14a97dd1a41e6f0c7ab',1,'HFS']]],
   ['vir_5fstates',['vir_states',['../namespaceHFS.html#a35c086cdd8d9c5cf5f3853abfb782c9c',1,'HFS']]],
   ['vol',['vol',['../namespaceHFS.html#a88874225b8d87c1f8589daee8b53a498',1,'HFS']]]
 ];

### 2017-02-01 HFS/src/calc_parameters.cpp
Edited the matrixproperties a bit and a few parameters testing

@@ -139,7 +139,8 @@ namespace HFS {
         Nexc = 0;
         for (arma::uword i = 0; i < occ_states.n_cols; ++i) {
             // Excite only in +x direction
-            for (arma::uword j = 1; j < Nk-1; ++j) {
+            //for (arma::uword j = 1; j < Nk-1; ++j) {
+            for (arma::uword j = 1; j < 3; ++j) {
                 kexc = kgrid(occ_states.col(i));
                 kexc(0) += deltaK * j;
                 HFS::toFirstBrillouinZone(kexc);
@@ -157,8 +158,8 @@ namespace HFS {
 
             }
         }
-        excitations  = excitations.head_cols(Nexc);
-        exc_energies = exc_energies.head(Nexc);
+        excitations  = excitations.head_cols(Nexc); // excitations is now full
+        exc_energies = exc_energies.head(Nexc);  // set the size of exc_energies
     }
 
     void calcExcitationEnergies() {

### 2017-02-01 HFS/src/main.cpp

@@ -42,7 +42,7 @@ int main(int argc, char* argv[]){
         HFS::mycase          = argv[3];
     #else
         HFS::rs              = 1.2;
-        HFS::Nk              = 12;
+        HFS::Nk              = 15;
         HFS::OutputFileName  = "test.log";
         HFS::mycase          = "cRHF2cUHF";
     #endif // Release
@@ -78,7 +78,7 @@ int main(int argc, char* argv[]){
         vecs[i] = arma::conv_to< std::vector<double> >::from(guessvec);
     }
 
-
+    HFS::davidsonAgreesWithFullDiag();
 
     myeps.SetInitialSpace(vecs);
     arma::wall_clock davtimer;
@@ -92,10 +92,11 @@ int main(int argc, char* argv[]){
     HFS::Dav_nconv = myeps.nconv;
     HFS::cond_number = HFS::exc_energies(HFS::exc_energies.n_elem-1) / HFS::exc_energies(0);
     HFS::Dav_final_val = HFS::dav_vals.min();
-    HFS::writeOutput(true);
+    HFS::writeOutput(false);
 
     myeps.clean();
     fclose(stdout);
+
 
     #ifndef NDEBUG
         //if (HFS::Nmat < 1500) {

### 2017-02-13 doc/papers/matrixproperties/MatrixProperties.tex
got out of the pickle
Edited the matrixproperties a bit and a few parameters testing
Add stability equation derivation mathematica notebook
A few more tweaks and the entirety of the stability derivations
will be in the notebook.

@@
 
-\definecolor{myred}{HTML}{CC5803}
-\definecolor{myblue}{HTML}{204B57}
+\definecolor{myred}{HTML}{990000}
+\definecolor{myblue}{HTML}{002299}
 
-\newcommand{\Ap}{\textcolor{myred}{\braket{aj|ib}}}
-\newcommand{\App}{\textcolor{myred}{\braket{aj|bi}}}
-\newcommand{\Aa}{\textcolor{myred}{\braket{aj||ib}}}
-\newcommand{\B}{\textcolor{myblue}{\braket{ab|ij}}}
-\newcommand{\Br}{\textcolor{myblue}{\braket{ab|ji}}}
-\newcommand{\Ba}{\textcolor{myblue}{\braket{ab||ij}}}
+\newcommand{\Ap}{\textcolor{myred}{\left(aj|ib\right)}}
+\newcommand{\App}{\textcolor{myred}{\left(aj|bi\right)}}
+\newcommand{\Aa}{\textcolor{myred}{\left(aj||ib\right)}}
+\newcommand{\B}{\textcolor{myblue}{\left(ab|ij\right)}}
+\newcommand{\Br}{\textcolor{myblue}{\left(ab|ji\right)}}
+\newcommand{\Ba}{\textcolor{myblue}{\left(ab||ij\right)}}
 
@@
 \end{eqnarray*}
-
 Where the matrices denoted by $\mathbf{A}$ and $\mathbf{B}$ are given by,
-
 \begin{eqnarray*}
-  A_{st} &=& \e\diag -  \Aa \\
-  B_{st} &=& \Ba         \\
+  A_{st} &=& \e\diag +  \textcolor{myred}{\braket{aj||ib}} \\
+  B_{st} &=& \textcolor{myblue}{\braket{ab||ij}}         
 \end{eqnarray*}
-
 The color is to help keep track of which portions of the matrices come from
@@
 following forms, after integrating over spin:
-
+\begin{eqnarray*}
+  A_{st} &=& \e\diag \textcolor{myred}{+ \delta_{\sigma_i\sigma_a}\delta_{\sigma_j\sigma_b}\Ap
+                     - \delta_{\sigma_a\sigma_b}\delta_{\sigma_i\sigma_j}\App} \\
+  B_{st} &=& \textcolor{myblue}{\delta_{\sigma_a\sigma_i}\delta_{\sigma_b\sigma_j}\B 
+             - \delta_{\sigma_a\sigma_b}\delta_{\sigma_i\sigma_j}\Br} 
+\end{eqnarray*}
+In matrix form, 
 \begin{eqnarray*}
@@
   \BtoA & 0               & 0               & \e\diag - \App & 0              \\
-  \BtoB & \Ap             & 0               & 0              & \e\diag + \Aa  \\
+  \BtoB & \Ap             & 0               & 0              & \e\diag + \Aa  
 }
 \end{eqnarray*}
-
 \begin{eqnarray*}
@@
   \BtoA & 0               & -\Br            & 0              & 0              \\
-  \BtoB & \B              & 0               & 0              & \Ba            \\
+  \BtoB & \B              & 0               & 0              & \Ba            
 }

### 2017-02-13 HFS/src/calc_parameters.cpp

@@ -137,10 +137,11 @@ namespace HFS {
         excitations.set_size(2, Nocc * Nvir);
         exc_energies.set_size(Nocc * Nvir);
         Nexc = 0;
+
+
         for (arma::uword i = 0; i < occ_states.n_cols; ++i) {
             // Excite only in +x direction
-            //for (arma::uword j = 1; j < Nk-1; ++j) {
-            for (arma::uword j = 1; j < 3; ++j) {
+            for (arma::uword j = 1; j < Nk-1; ++j) {
                 kexc = kgrid(occ_states.col(i));
                 kexc(0) += deltaK * j;
                 HFS::toFirstBrillouinZone(kexc);

### 2017-02-13 HFS/src/matrix_utils.cpp

@@ -1,5 +1,4 @@
 #include "matrix_utils.hpp"
-//#include <omp.h>
 
 namespace HFS {
 
@@ -93,7 +92,9 @@ namespace HFS {
 
     void matrixVectorProduct3H(arma::vec& v, arma::vec& Mv) {
         Mv.zeros();
-        factorize2by2MatrixVectorProduct(v, Mv, matrixVectorProduct3A, matrixVectorProduct3B, matrixVectorProduct3B, matrixVectorProduct3A);
+        //factorize2by2MatrixVectorProduct(v, Mv, matrixVectorProduct3A, matrixVectorProduct3B, matrixVectorProduct3B, matrixVectorProduct3A);
+        matrixVectorProduct3A(v, Mv);
+        matrixVectorProduct3B(v, Mv);
     }
 
     void matrixVectorProduct3A(arma::vec& v, arma::vec& Mv) {
@@ -138,7 +139,7 @@ namespace HFS {
                 if (arma::norm(kb) > (HFS::kf + SMALLNUMBER)) {
                     // only if momentum conserving state is virtual
                     arma::uword t = HFS::calcTfromKbAndJ(kb, j);
-                    Mv(s) += -1.0 * HFS::twoElectron(ka, kj) * v(t);
+                    Mv(s) += 1.0 * HFS::twoElectron(ka, kj) * v(t);
                 }
             }
         }
@@ -406,7 +407,7 @@ namespace HFS {
         if (HFS::mycase == "cRHF2cUHF") {
             HFS::MatVecProduct_func = HFS::matrixVectorProduct3H;
             HFS::Matrix_func = HFS::calcFromIndices3H;
-            HFS::Nmat = 2 * HFS::Nexc;
+            HFS::Nmat = HFS::Nexc;
         } else if (HFS::mycase == "cUHF2cUHF") {
             HFS::MatVecProduct_func = HFS::matrixVectorProductHprime;
             HFS::Matrix_func = HFS::calcFromIndicesHprime;

### 2017-03-08 doc/presentations/GroupMeeting_Fall2016.tex
Modified presentation for Van voorhis lunch

--- 2016-11-08 presentations/GroupMeeting_Fall2016.tex
@@
 \usepackage{amsmath}
+\usepackage{verbatim}
 
@@
 
+\begin{comment}
 {%
@@
 
+\end{comment}
+
 {%
@@
 				  \midrule
-				  Real RHF    & ${}^1\mathbf{A}' + {}^1\mathbf{B}'$ & ${}^1\mathbf{A}' - {}^1\mathbf{B}'$ & ${}^3\mathbf{A}' + {}^3\mathbf{B}'$ & & & \\
-				  Complex RHF & - & ${}^1\mathbf{H}'$ & - & \alert{${}^3\mathbf{H}'$} & - & \\
-				  Real UHF    & - & - & $\mathbf{A}' + \mathbf{B}'$ & $\mathbf{A}' - \mathbf{B}'$ & $\mathbf{A}'' + \mathbf{B}''$ &  \\
+				  Real RHF    & ${}^1\mathbf{A}' + {}^1\mathbf{B}'$ & ${}^1\mathbf{A}' - {}^1\mathbf{B}'$ & ${}^3\mathbf{A}' + {}^3\mathbf{B}'$ & - & - & -  \\
+				  Complex RHF & - & ${}^1\mathbf{H}'$ & - & \alert{${}^3\mathbf{H}'$} & - & - \\
+				  Real UHF    & - & - & $\mathbf{A}' + \mathbf{B}'$ & $\mathbf{A}' - \mathbf{B}'$ & $\mathbf{A}'' + \mathbf{B}''$ & - \\
 				  Complex UHF & - & - & - &  $\mathbf{H}'$ & - & $\mathbf{H}'$ \\
@@
 
+\begin{comment}
 \section{Notes on Iterative Subspace Eigenvalue Methods}
@@
 \end{frame}
+\end{comment}
 
@@
 				\item {$N_{occ}$ and $N_{vir}$ both scale with $N_{kpoints}^D$}
+				\item {Use an iterative subspace method }
+				\item {Jacobi-Davidson(-Liu)}
 			\end{itemize}
@@
 
+\begin{comment}
 \begin{frame}{Algorithm Wall time}
@@
 
+{%
+\setbeamertemplate{frame footer}{}
+\begin{frame}{Dependence on r${}_s$}
+	3D data is currently inconclusive. 
+	\includegraphics[width=.95\linewidth]{../images/2d3dstability.eps}
+\end{frame}
+
+{%
+\setbeamertemplate{frame footer}{}
+\begin{frame}[standout]
+  Questions?
+\end{frame}
+
+\begin{comment}
 \section{Concluding Remarks}
-
 {%
@@
 }
-
-{%
-\setbeamertemplate{frame footer}{}
-\begin{frame}[standout]
-  Questions?
-\end{frame}
+\end{comment}
 

### 2017-03-08 analysis/pyfiles/HFSAnalyzer.py

@@ -250,13 +250,14 @@ def subplotByDfList(dflist, fig, axplot, shape=None):
     n = len(dflist)
     nrows, ncols = subplt_shaper(n, shape) 
     gs = gridspec.GridSpec(nrows, ncols)
+    axes = [[None for col in range(ncols)] for row in range(nrows)]
     for i, dfi in enumerate(dflist):
         irow = math.floor(i / ncols)
         icol = i - irow * ncols
-        ax = plt.subplot(gs[irow, icol])
-        axplot(dfi, ax)
+        axes[irow][icol] = plt.subplot(gs[irow, icol])
+        axplot(dfi, axes[irow][icol])
     plt.tight_layout()
-    return gs
+    return axes, gs
 
 def df_ApplyAxplotToRows(df, shape, axplot_func, *args, **kwargs):
     N = len(df)

### 2017-03-31 doc/papers/matrixproperties/MatrixProperties.tex
Updated matrix properties

@@
 \usepackage{xcolor}
+\usepackage{graphicx}
 
-\definecolor{myred}{HTML}{990000}
-\definecolor{myblue}{HTML}{002299}
+%\definecolor{myred}{HTML}{990000}
+%\definecolor{myblue}{HTML}{002299}
+\definecolor{myred}{HTML}{000000}
+\definecolor{myblue}{HTML}{000000}
 
@@
 Hessian has the form,
-\begin{eqnarray*}
+\begin{eqnarray}\label{basic}
 \mathbf{H} =
@@
   \end{bmatrix}
-\end{eqnarray*}
+\end{eqnarray}
 Where the matrices denoted by $\mathbf{A}$ and $\mathbf{B}$ are given by,
-\begin{eqnarray*}
+\begin{eqnarray}
   A_{st} &=& \e\diag +  \textcolor{myred}{\braket{aj||ib}} \\
   B_{st} &=& \textcolor{myblue}{\braket{ab||ij}}         
-\end{eqnarray*}
-The color is to help keep track of which portions of the matrices come from
-$\mathbf{A}$ and $\mathbf{B}$.
-The integration is over spin and spatial coordinates. In the case of
-a stationary UHF solution, the matrices $\mathbf{A}$ and $\mathbf{B}$ have the
+\end{eqnarray}
+and the two electron integral used here is defined as, 
+\begin{eqnarray}
+  \braket{pq|rs} &=& \int\int \chi^*_p(1) \chi^*_q(2) \frac{1}{r_{12}} \chi^*_r(1) 
+  \chi^*_s(2)
+  d\tau d\sigma \\
+  \braket{pq||rs} &=& \braket{pq|rs} - \braket{pq|sr} \\
+  (pq|rs) &=& \int\int \chi^*_p(1) \chi^*_q(2) \frac{1}{r_{12}} \chi^*_r(1) 
+  \chi^*_s(2)
+  d\tau \\
+  (pq||rs) &=& (pq|rs) - (pq|sr)
+\end{eqnarray}
+Where $\sigma$ is the spin coordinate and $d\tau$ is the volume element in all spatial coordinates.
+Additionally, the convention of $a, b$ being virtual states, $i, j$ being occupied states and 
+$p, q, r, s$ being any state is followed.
+
+The solution is said to be unstable when the lowest eigenvalue is strictly negative. The
+corresponding eigenvector points downhill in energy in the case of instability. Defining
+the eigenvector as $\mathbf{D}$, the eigenvalue problem can be written as
+\begin{eqnarray}
+  \mathbf{HD = \lambda D}
+\end{eqnarray}
+In many cases, the matrix $\mathbf{H}$ factorizes into various components. The following
+form of a similarity transformed eigenvalue problem is useful to keep in mind:
+\begin{eqnarray}
+  \mathbf{S^{-1} H S S^{-1} D} &=& \mathbf{\lambda S^{-1} D} \\
+  \mathbf{\tilde H \tilde D} &=& \mathbf{\lambda \tilde D}   
+\end{eqnarray}
+
+Thus if the matrix $\mathbf{H}$ can be transformed via a similarity transformation defined
+by $\mathbf{S}$ into $\mathbf{\tilde H}$, then the corresponding eigenvector which satisfies the 
+eigenvalue problem
+has the form $\mathbf{\tilde D} = \mathbf{S^{-1}D}$.  
+Writing the eigenvalue problem in the form of Seeger \& Pople (eq. 18 in \cite{Seeger1977}), 
+we get
+\begin{eqnarray}
+  \begin{bmatrix}
+    \mathbf{A} & \mathbf{B} \\
+    \mathbf{B^*} & \mathbf{A^*} 
+  \end{bmatrix}
+  \begin{bmatrix}
+    \mathbf{d} \\
+    \mathbf{d^*} 
+  \end{bmatrix}
+  = 2E_2
+  \begin{bmatrix}
+    \mathbf{d} \\
+    \mathbf{d^*} 
+  \end{bmatrix}
+\end{eqnarray}
+We can now apply the similarity transform defined by the Unitary matrix 
+\begin{eqnarray}
+  \mathbf{U} = \frac{1}{\sqrt{2}}
+  \begin{bmatrix}
+    \mathbf{I} & -\mathbf{I} \\
+    \mathbf{I} & \mathbf{I} 
+  \end{bmatrix}
+\end{eqnarray}
+after which the transformed eigenvalue problem has the form
+\begin{eqnarray}
+  \frac{1}{2}
+  \begin{bmatrix}
+    \mathbf{A + B + A^* + B^*} & \mathbf{-A + A^* + B - B^*} \\
+    \mathbf{-A + A^* - B + B^*} & \mathbf{A^* + A - B - B^*} 
+  \end{bmatrix}
+  \begin{bmatrix}
+    \mathbf{d + d^*} \\
+    \mathbf{d - d^*} 
+  \end{bmatrix}
+  &=& 2E_2
+  \begin{bmatrix}
+    \mathbf{d + d^*} \\
+    \mathbf{d - d^*} 
+  \end{bmatrix} \\
+  &=& 2E_2
+  \begin{bmatrix}
+    \mathbf{Re(d)} \\
+    \mathbf{Im(d)} 
+  \end{bmatrix}
+\end{eqnarray}
+If $\mathbf{A}$ and $\mathbf{B}$ are both real, $\mathbf{A = A^*}$ and $\mathbf{B = B^*}$ and the 
+above simplifies to 
+\begin{eqnarray}
+  \begin{bmatrix}
+    \mathbf{A + B} & \mathbf{0} \\
+    \mathbf{0} & \mathbf{A - B} 
+  \end{bmatrix}
+  \begin{bmatrix}
+    \mathbf{Re(d)} \\
+    \mathbf{Im(d)} 
+  \end{bmatrix}
+  &=& 2E_2   
+  \begin{bmatrix}
+    \mathbf{Re(d)} \\
+    \mathbf{Im(d)} 
+  \end{bmatrix}
+\end{eqnarray}
+Clearly, the matrix factorizes into $\mathbf{A+B}$ and $\mathbf{A-B}$. The eigenvectors factorize
+into the real and imaginary displacements of the orbitals, respectively. This is equivalent to the 
+condition derived in and around eq. 20 for internal and external instabilities of real
+GHF solutions \cite{Seeger1977}, however this approach applies to any matrix with the same
+form as equation \ref{basic}.
+
+\section{Forms of equations with UHF wavefunction}
+In the case of a stationary UHF solution, the matrices $\mathbf{A}$ and $\mathbf{B}$ have the
 following forms, after integrating over spin:
-\begin{eqnarray*}
+\begin{eqnarray}
   A_{st} &=& \e\diag \textcolor{myred}{+ \delta_{\sigma_i\sigma_a}\delta_{\sigma_j\sigma_b}\Ap
@@
   B_{st} &=& \textcolor{myblue}{\delta_{\sigma_a\sigma_i}\delta_{\sigma_b\sigma_j}\B 
-             - \delta_{\sigma_a\sigma_b}\delta_{\sigma_i\sigma_j}\Br} 
-\end{eqnarray*}
+             - \delta_{\sigma_a\sigma_j}\delta_{\sigma_b\sigma_i}\Br} 
+\end{eqnarray}
 In matrix form, 
-\begin{eqnarray*}
+\begin{eqnarray}
   \mathbf{A}&=&\kbordermatrix{
@@
 }
-\end{eqnarray*}
-\begin{eqnarray*}
+\end{eqnarray}
+\begin{eqnarray}
   \mathbf{B}&=&\kbordermatrix{
@@
 }
-\end{eqnarray*}
+\end{eqnarray}
 \\
@@
 
-\begin{eqnarray*}
+\begin{eqnarray}
   \mathbf{A'}&=&\kbordermatrix{
@@
 }
-\end{eqnarray*}
-\begin{eqnarray*}
+\end{eqnarray}
+\begin{eqnarray}
   \mathbf{B'}&=&\kbordermatrix{
@@
 }
-\end{eqnarray*}
+\end{eqnarray}
 \\
 while the spin-unconserved matrices are given by:
-\begin{eqnarray*}
+\begin{eqnarray}
   \mathbf{A''}&=&\kbordermatrix{
@@
 }
-\end{eqnarray*}
+\end{eqnarray}
 
-\begin{eqnarray*}
+\begin{eqnarray}
   \mathbf{B''}&=&\kbordermatrix{
@@
 }
-\end{eqnarray*}
+\end{eqnarray}
 \\
-Thus the spin conserved molecular orbital hessian, $\mathbf{H'}$ is given by:
+Thus the spin conserved molecular orbital hessian, 
+\begin{eqnarray}
+\mathbf{H}' =
+  \begin{bmatrix}
+    \mathbf{A}'   & \mathbf{B}'   \\
+    \mathbf{B}'^* & \mathbf{A}'^* \\
+  \end{bmatrix}
+\end{eqnarray}
+is given by
 \begin{eqnarray*}
@@
 \\
-and the spin unconserved molecular orbital hessian, $\mathbf{H''}$ is given by:
+and the spin unconserved molecular orbital hessian, 
+\begin{eqnarray}
+\mathbf{H}'' =
+  \begin{bmatrix}
+    \mathbf{A}''   & \mathbf{B}''   \\
+    \mathbf{B}''^* & \mathbf{A}''^* \\
+  \end{bmatrix}
+\end{eqnarray}
+is given by:
 \begin{eqnarray*}
@@
 \\
+The eigenvalue equation defining $\mathbf{D}''$ is, 
+\begin{eqnarray}
+  \mathbf{H''D''} = 
+  \mathbf{H''}
+  \begin{bmatrix}
+    \mathbf{d_\AtoB} \\
+    \mathbf{d_\BtoA} \\
+    \mathbf{d^*_\AtoB} \\        
+    \mathbf{d^*_\BtoA} 
+  \end{bmatrix}
+  = 2E_2
+  \begin{bmatrix}
+    \mathbf{d_\AtoB} \\
+    \mathbf{d_\BtoA} \\
+    \mathbf{d^*_\AtoB} \\        
+    \mathbf{d^*_\BtoA} 
+  \end{bmatrix}
+\end{eqnarray}
 
-This matrix factorizes into to two equivalent matrices,
+Transforming the equation with the similarity transform defined by the following Unitary 
+matrix, 
+\begin{eqnarray}
+  \mathbf{U} = \frac{1}{\sqrt{2}}
+  \begin{bmatrix}
+    \mathbf{I} & 0 & 0 & -\mathbf{I} \\
+     0 & \mathbf{I} & -\mathbf{I} & 0 \\ 
+     0 & \mathbf{I} & \mathbf{I} & 0 \\
+    \mathbf{I} & 0 & 0 & \mathbf{I} \\  
+  \end{bmatrix}
+\end{eqnarray}
+The transformed Hessian is ($e = \e\diag$, $C.C.$ is the complex conjugate of the rest of the 
+expression). 
 \begin{eqnarray*}
-  \mathbf{H''}&=&\kbordermatrix{
-        & \AtoB           &\BtoA            \\
-  \AtoB & \e\diag - \App  & -\Br             \\
-  \BtoA & -\Br^*          & \e\diag - \App^* \\
+\hspace{-1.45cm}
+  &\mathbf{\tilde{H}''}& = \\
+  \hspace{-1.45cm} 
+  &\frac{1}{2}& \kbordermatrix{
+        & \AtoB           & \BtoA              & \AtoB             & \BtoA            \\
+  \AtoB & e - \App -\Br + C.C.  & 0 & 0  & -e + \App -\Br - C.C.             \\
+  \BtoA & 0               & e - \App -\Br + C.C.     & -e + \App -\Br - C.C. & 0  \\
+  \AtoB & 0 & -e + \App +\Br - C.C. & e - \App +\Br + C.C.  & 0                \\
+  \BtoA & -e + \App +\Br - C.C.    & 0  & 0  & e - \App +\Br +  C.C. \\
 }
 \end{eqnarray*}
+While the corresponding transformed eigenvector has the following form:
+\begin{eqnarray*}
+  \mathbf{\tilde{D}''} = 
+  \begin{bmatrix}
+    d_\AtoB + d^*_\BtoA \\
+    d_\BtoA + d^*_\AtoB \\
+    -d_\BtoA + d^*_\AtoB \\
+    -d_\AtoB + d^*_\BtoA \\
+  \end{bmatrix}
+\end{eqnarray*}
 
-And in this form it is entirely equivalent to the RHF-UHF stability
-matrix, $\mathbf{{}^3H'}$ defined in equations 35 and 36 of
-Seeger/Pople\cite{Seeger1977}. This is where I suspect I've made a mistake.
-\\
+If the two electron integrals and energies are all real, we have for the form 
+of $\mathbf{H''}$, 
+\begin{eqnarray*}
+\hspace{-1cm}
+  \mathbf{\tilde{H}''} = 
+  \kbordermatrix{
+        & \AtoB           & \BtoA              & \AtoB             & \BtoA        \\
+  \AtoB & \e - \App -\Br  & 0                  & 0                 & 0            \\
+  \BtoA & 0               & \e - \App -\Br     & 0                  & 0  \\
+  \AtoB & 0 & 0 & \e - \App + \Br  & 0                \\
+  \BtoA & 0    & 0  & 0  &\e - \App + \Br \\
+}
+\end{eqnarray*}
+Furthermore, if the solution we started with was an RHF solution, the $\AtoB$ and 
+$\BtoA$ are identical. Letting $d_\AtoB = d_\BtoA = d$, we get the following forms 
+of the transformed eigenvectors, 
+\begin{eqnarray}\label{rhfvecs}
+  \mathbf{\tilde{D}''} = 
+  \begin{bmatrix}
+    d + d^*  \\
+    d + d^*  \\
+    -d + d^* \\
+    -d + d^* \\
+  \end{bmatrix}
+  =
+  \begin{bmatrix}
+    Re(d)  \\
+    Re(d)  \\
+    Im(d)  \\
+    Im(d)  \\
+  \end{bmatrix}
+\end{eqnarray}
+At this point the only assumptions we made are that the two electron integrals and the
+energies are real-valued and that the solution we started with was an RHF solution. From
+this it immediately follows that the eigenvectors have the form of equation \ref{rhfvecs}.
+
+Clearly, the eigensystem defined by $\mathbf{H}''\mathbf{D}'' = 2E_2\mathbf{D}''$ is a
+doubly degenerate set of the following equations:
+\begin{eqnarray}
+  \left[ \mathbf{A+B} \right] Re(d) &=& 2E_2 Re(d) \\
+  \left[ \mathbf{A-B} \right] Im(d) &=& 2E_2 Im(d) 
+\end{eqnarray}
+Where $\mathbf{A}$ and $\mathbf{B}$ are defined such that
+\begin{eqnarray}
+  A_{ia, jb} &=& \e\diag - \App \\
+  B_{ia, jb} &=& -\Br 
+\end{eqnarray}
+These matrices are exactly equivalent to ${}^3\mathbf{A}'$ and ${}^3\mathbf{B}'$ (eq 35 in Seeger
+\& Pople). Thus, when the matrices $\mathbf{A}$ and $\mathbf{B}$ are real, and the solution
+is an RHF solution, the eigenvalue problem is doubly degenerate, and factorizes into the equation
+characterized by the triplet instability equation.
 

### 2017-03-31 HFS/src/fileIO.cpp

@@ -3,9 +3,6 @@
 #include <chrono>
 #include <ctime>
 
-#define JSONVAL(x) output << ",\n\"" << #x << "\" : " << x
-#define JSONSTR(x) output << ",\n\"" << #x << "\" : \"" << x << "\""
-
 namespace HFS {
 
     template <class T>
@@ -48,7 +45,6 @@ namespace HFS {
 
         output.open(fname.c_str());
 
-
         using namespace HFS;
         if (output.is_open() && output.good()) {
 
@@ -72,6 +68,8 @@ namespace HFS {
             computation_finished.pop_back();
 
             // Begin output
+            #define JSONVAL(x) output << ",\n\"" << #x << "\" : " << x
+            #define JSONSTR(x) output << ",\n\"" << #x << "\" : \"" << x << "\""
             output << "{\"File\" : \"" << fname << "\"";
             JSONSTR(total_calculation_time);
             JSONSTR(computation_started);
@@ -109,6 +107,8 @@ namespace HFS {
             JSONVAL(dav_max_subsize);
             JSONVAL(dav_min_eval);
             JSONVAL(dav_time);
+            #undef JSONVAL
+            #undef JSONSTR
 
             if (detail) {
                 writeArmaVecToJSON(output, occ_energies, "occ_energies");

### 2017-04-05 doc/papers/matrixproperties/MatrixProperties.tex
Checkpoint for similarity transform explanation
Added cRHF2cRHF (singlet instability) functionality

@@
 \usepackage{graphicx}
+\usepackage{verbatim}
 
@@
 \title{Notes on Matrix Factorization for Hartree-Fock Stability of HEG}
-\author{Evan Curtin}
+%\author{Evan Curtin}
 \maketitle
 
-\section{Orbital Hessian Factorization}
+\section{Definitions}
 According to Seeger and Pople\cite{Seeger1977}, (and many other sources) the molecular orbital
@@
 \begin{eqnarray}
-  \braket{pq|rs} &=& \int\int \chi^*_p(1) \chi^*_q(2) \frac{1}{r_{12}} \chi^*_r(1) 
-  \chi^*_s(2)
+  \braket{pq|rs} &=& \int\int \chi^*_p(1) \chi^*_q(2) \frac{1}{r_{12}} \chi_r(1) 
+  \chi_s(2)
   d\tau d\sigma \\
   \braket{pq||rs} &=& \braket{pq|rs} - \braket{pq|sr} \\
-  (pq|rs) &=& \int\int \chi^*_p(1) \chi^*_q(2) \frac{1}{r_{12}} \chi^*_r(1) 
-  \chi^*_s(2)
+  (pq|rs) &=& \int\int \chi^*_p(1) \chi^*_q(2) \frac{1}{r_{12}} \chi_r(1) 
+  \chi_s(2)
   d\tau \\
@@
 
-The solution is said to be unstable when the lowest eigenvalue is strictly negative. The
+The solution is said to be unstable when the lowest eigenvalue of $\mathbf{H}$
+is strictly negative. The
 corresponding eigenvector points downhill in energy in the case of instability. Defining
@@
 \end{eqnarray}
+
+\section{Transforming H Dictates the form of D}
 In many cases, the matrix $\mathbf{H}$ factorizes into various components. The following
@@
 has the form $\mathbf{\tilde D} = \mathbf{S^{-1}D}$.
+
+This approach is commonly used in the paper to transform into the basis that separates
+the real and complex contributions of the eigenvectors when $\mathbf{A}$ and $\mathbf{B}$ are real.
 Writing the eigenvalue problem in the form of Seeger \& Pople (eq. 18 in \cite{Seeger1977}), 
@@
     \mathbf{d + d^*} \\
-    \mathbf{d - d^*} 
+    \mathbf{-d + d^*} 
   \end{bmatrix} \\
@@
 into the real and imaginary displacements of the orbitals, respectively. This is equivalent to the 
-condition derived in and around eq. 20 for internal and external instabilities of real
+condition derived in and around eq. 20 in Seeger/Pople for internal and external instabilities of 
+real
 GHF solutions \cite{Seeger1977}, however this approach applies to any matrix with the same
@@
 
-\section{Forms of equations with UHF wavefunction}
-In the case of a stationary UHF solution, the matrices $\mathbf{A}$ and $\mathbf{B}$ have the
-following forms, after integrating over spin:
+\section{Forms of equations with UHF Solution}
+In the case of a stationary UHF solution, the elements of matrices $\mathbf{A}$ and $\mathbf{B}$ 
+have the following forms, after integrating over spin:
 \begin{eqnarray}
-  A_{st} &=& \e\diag \textcolor{myred}{+ \delta_{\sigma_i\sigma_a}\delta_{\sigma_j\sigma_b}\Ap
+  A_{i \rightarrow a, j \rightarrow b} &=& \e\diag \textcolor{myred}{+ 
+  \delta_{\sigma_i\sigma_a}\delta_{\sigma_j\sigma_b}\Ap
                      - \delta_{\sigma_a\sigma_b}\delta_{\sigma_i\sigma_j}\App} \\
-  B_{st} &=& \textcolor{myblue}{\delta_{\sigma_a\sigma_i}\delta_{\sigma_b\sigma_j}\B 
+  B_{i \rightarrow a,j \rightarrow b} &=& 
+  \textcolor{myblue}{\delta_{\sigma_a\sigma_i}\delta_{\sigma_b\sigma_j}\B 
              - \delta_{\sigma_a\sigma_j}\delta_{\sigma_b\sigma_i}\Br} 
 \end{eqnarray}
-In matrix form, 
-\begin{eqnarray}
+Writing down the matrices, where the row index corresponds to $i \rightarrow a$ excitations  and 
+the column index corresponds to $j \rightarrow b$ excitations:
+\begin{eqnarray*}
   \mathbf{A}&=&\kbordermatrix{
@@
 }
-\end{eqnarray}
-\begin{eqnarray}
+\end{eqnarray*}
+\begin{eqnarray*}
   \mathbf{B}&=&\kbordermatrix{
@@
 }
-\end{eqnarray}
+\end{eqnarray*}
 \\
@@
 ``spin-unconserved'' $(\mathbf{A'', B''})$ parts, to use the language of Seeger
-and Pople. The spin conserved matrices are given by
+and Pople. Similarly, $\mathbf{H}$ factorizes, with no approximations, into
+$\mathbf{H}'$ and $ \mathbf{H}''$
+\begin{eqnarray}
+\mathbf{H}' =
+  \begin{bmatrix}
+    \mathbf{A}'   & \mathbf{B}'   \\
+    \mathbf{B}'^* & \mathbf{A}'^* \\
+  \end{bmatrix}
+\end{eqnarray}
+\begin{eqnarray}
+\mathbf{H}'' =
+  \begin{bmatrix}
+    \mathbf{A}''   & \mathbf{B}''   \\
+    \mathbf{B}''^* & \mathbf{A}''^* \\
+  \end{bmatrix}
+\end{eqnarray}
+The spin conserved matrices are given by
 
@@
 \\
-Thus the spin conserved molecular orbital hessian, 
-\begin{eqnarray}
-\mathbf{H}' =
-  \begin{bmatrix}
-    \mathbf{A}'   & \mathbf{B}'   \\
-    \mathbf{B}'^* & \mathbf{A}'^* \\
-  \end{bmatrix}
-\end{eqnarray}
-is given by
+Thus the spin conserved molecular orbital hessian, is given by
 \begin{eqnarray*}
@@
 \\
-and the spin unconserved molecular orbital hessian, 
-\begin{eqnarray}
-\mathbf{H}'' =
-  \begin{bmatrix}
-    \mathbf{A}''   & \mathbf{B}''   \\
-    \mathbf{B}''^* & \mathbf{A}''^* \\
-  \end{bmatrix}
-\end{eqnarray}
-is given by:
+and the spin unconserved molecular orbital hessian, is given by:
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-\\
+
+The eigenvalue equation defining $\mathbf{D}'$ is, 
+\begin{eqnarray}\label{hppeval}
+  \mathbf{H'D'} = 
+  \mathbf{H'}
+  \begin{bmatrix}
+    \mathbf{d_\AtoA} \\
+    \mathbf{d_\BtoB} \\
+    \mathbf{d^*_\AtoA} \\        
+    \mathbf{d^*_\BtoB} 
+  \end{bmatrix}
+  = 2E_2
+  \begin{bmatrix}
+    \mathbf{d_\AtoA} \\
+    \mathbf{d_\BtoB} \\
+    \mathbf{d^*_\AtoA} \\        
+    \mathbf{d^*_\BtoB} 
+  \end{bmatrix}
+\end{eqnarray}
+
+Applying the transformation defined by the unitary matrix, 
+\begin{eqnarray}
+  \mathbf{U} = \frac{1}{\sqrt{2}} 
+  \begin{bmatrix}
+    \mathbf{1} & -\mathbf{1} & 0 &  0 \\
+    \mathbf{1} &  \mathbf{1} & 0 &  0 \\
+    0 &  0 & \mathbf{1} & -\mathbf{1} \\
+    0 &  0 & \mathbf{1} &  \mathbf{1} \\
+  \end{bmatrix}
+\end{eqnarray}
+
+With no further assumptions, this transformation doesn't do much. However, if the spatial
+orbitals corresponding to $\alpha$ and $\beta$ are assumed equivalent, the 
+transformed $\mathbf{H}'$ is
+\begin{eqnarray*}
+  \hspace{-1cm}
+  \mathbf{U^{-1}H'U} =
+  \begin{bmatrix}
+    \e + \Aa + \Ap & 0              & \Ba + \B            & 0            \\
+    0                    & \e + \Aa - \Ap    & 0                & \Ba - \B              \\
+    \Ba^* + \B^*         & 0                & \e+ \Aa^* + \Ap^*   & 0                     \\
+    0                    & \Ba^* - \B^*     & 0                 & \e+ \Aa^* - \Ap^*  \\
+  \end{bmatrix}
+\end{eqnarray*}
+
+while the corresponding eigenvectors are 
+\begin{eqnarray*}
+  \mathbf{U^{-1}D'} = \frac{1}{\sqrt{2}}
+  \begin{bmatrix}
+    \mathbf{d_\AtoA + d_\BtoB} \\
+    \mathbf{d_\AtoA - d_\BtoB} \\
+    \mathbf{d^*_\AtoA + d^*_\BtoB} \\        
+    \mathbf{d^*_\AtoA - d^*_\BtoB} 
+  \end{bmatrix}
+\end{eqnarray*}
+
+In this basis the equations clearly factorize into the following sets of eigenvalue equations:  
+\begin{eqnarray}\label{1Heval}
+  \begin{bmatrix}
+    \e + \Aa + \Ap & \Ba + \B          \\
+    \Ba^* + \B^*   & \e+ \Aa^* + \Ap^* \\
+  \end{bmatrix}
+  \begin{bmatrix}
+    \mathbf{d_\AtoA + d_\BtoB} \\
+    \mathbf{d^*_\AtoA + d^*_\BtoB} \\        
+  \end{bmatrix}
+  = 2E_2
+  \begin{bmatrix}
+    \mathbf{d_\AtoA + d_\BtoB} \\
+    \mathbf{d^*_\AtoA + d^*_\BtoB} \\        
+  \end{bmatrix}
+  \vspace{5mm}
+  \\ \label{3Heval}
+  \begin{bmatrix}
+    \e + \Aa - \Ap & \Ba - \B          \\
+    \Ba^* - \B^*   & \e+ \Aa^* - \Ap^* \\
+  \end{bmatrix}
+  \begin{bmatrix}
+    \mathbf{d_\AtoA - d_\BtoB} \\
+    \mathbf{d^*_\AtoA - d^*_\BtoB} \\        
+  \end{bmatrix}
+  = 2E_2
+  \begin{bmatrix}
+    \mathbf{d_\AtoA - d_\BtoB} \\
+    \mathbf{d^*_\AtoA - d^*_\BtoB} \\        
+  \end{bmatrix}
+\end{eqnarray}
+Equation \ref{3Heval} defines the matrix ${{}^3\mathbf{H}'}$, the triplet instability matrix,
+while \ref{1Heval} defines the matrix ${{}^1\mathbf{H}'}$, which defines instabilities that mix 
+singlet states. The only assumption made until this point in the analysis of ${\mathbf{H}'}$ was
+that the original solution was a complex RHF solution. No assumption was made about the outside 
+space towards which the eigenvector points. Even still, the eigenvectors can be shown to have the
+form given in equations \ref{1Heval} and \ref{3Heval}. Thus, the space in which the eigenvectors
+of ${\mathbf{H}'}$ point can only be that of UHF solutions.
+
+Now, the other part of the general form of the stability matrix is ${\mathbf{H}''}$.
 The eigenvalue equation defining $\mathbf{D}''$ is, 
-\begin{eqnarray}
+\begin{eqnarray}\label{hppeval}
   \mathbf{H''D''} = 
@@
 
-Transforming the equation with the similarity transform defined by the following Unitary 
-matrix, 
-\begin{eqnarray}
-  \mathbf{U} = \frac{1}{\sqrt{2}}
+Equation \ref{hppeval} clearly factors into the following two eigenvalue equations:
+\begin{eqnarray}\label{b2aa2b}
+    \kbordermatrix{
+          & \BtoA              & \AtoB            \\
+    \BtoA & \e\diag - \App     & -\Br             \\
+    \AtoB & -\Br^*           & \e\diag - \App^* \\
+  }
   \begin{bmatrix}
-    \mathbf{I} & 0 & 0 & -\mathbf{I} \\
-     0 & \mathbf{I} & -\mathbf{I} & 0 \\ 
-     0 & \mathbf{I} & \mathbf{I} & 0 \\
-    \mathbf{I} & 0 & 0 & \mathbf{I} \\  
+    \mathbf{d_\BtoA} \\
+    \mathbf{d^*_\AtoB} \\        
+  \end{bmatrix} 
+  &=& 2E_2
+  \begin{bmatrix}
+    \mathbf{d_\BtoA} \\
+    \mathbf{d^*_\AtoB} \\        
+  \end{bmatrix}
+  \\
+  \label{a2bb2a}
+    \kbordermatrix{
+          & \AtoB              & \BtoA            \\
+    \AtoB & \e\diag - \App     & -\Br             \\
+    \BtoA & -\Br^*           & \e\diag - \App^* \\
+  }
+  \begin{bmatrix}
+    \mathbf{d_\AtoB} \\
+    \mathbf{d^*_\BtoA} \\        
+  \end{bmatrix} 
+  &=& 2E_2
+  \begin{bmatrix}
+    \mathbf{d_\AtoB} \\
+    \mathbf{d^*_\BtoA} \\        
   \end{bmatrix}
 \end{eqnarray}
-The transformed Hessian is ($e = \e\diag$, $C.C.$ is the complex conjugate of the rest of the 
-expression). 
-\begin{eqnarray*}
-\hspace{-1.45cm}
-  &\mathbf{\tilde{H}''}& = \\
-  \hspace{-1.45cm} 
-  &\frac{1}{2}& \kbordermatrix{
-        & \AtoB           & \BtoA              & \AtoB             & \BtoA            \\
-  \AtoB & e - \App -\Br + C.C.  & 0 & 0  & -e + \App -\Br - C.C.             \\
-  \BtoA & 0               & e - \App -\Br + C.C.     & -e + \App -\Br - C.C. & 0  \\
-  \AtoB & 0 & -e + \App +\Br - C.C. & e - \App +\Br + C.C.  & 0                \\
-  \BtoA & -e + \App +\Br - C.C.    & 0  & 0  & e - \App +\Br +  C.C. \\
-}
-\end{eqnarray*}
-While the corresponding transformed eigenvector has the following form:
-\begin{eqnarray*}
-  \mathbf{\tilde{D}''} = 
+
+Equations \ref{b2aa2b} and \ref{a2bb2a} are complex conjugates in the general case. If however, 
+the solution is an RHF solution, the spatial orbitals for $\alpha$ and $\beta$ spins are identical
+by definition. In this case, the matrices in both equation \ref{b2aa2b} and equation \ref{a2bb2a}
+are equivalent to the triplet instability matrix defined by Seeger and Pople:
+
+\begin{eqnarray}
+  \mathbf{{}^3H} =
   \begin{bmatrix}
-    d_\AtoB + d^*_\BtoA \\
-    d_\BtoA + d^*_\AtoB \\
-    -d_\BtoA + d^*_\AtoB \\
-    -d_\AtoB + d^*_\BtoA \\
-  \end{bmatrix}
-\end{eqnarray*}
-
-If the two electron integrals and energies are all real, we have for the form 
-of $\mathbf{H''}$, 
-\begin{eqnarray*}
-\hspace{-1cm}
-  \mathbf{\tilde{H}''} = 
-  \kbordermatrix{
-        & \AtoB           & \BtoA              & \AtoB             & \BtoA        \\
-  \AtoB & \e - \App -\Br  & 0                  & 0                 & 0            \\
-  \BtoA & 0               & \e - \App -\Br     & 0                  & 0  \\
-  \AtoB & 0 & 0 & \e - \App + \Br  & 0                \\
-  \BtoA & 0    & 0  & 0  &\e - \App + \Br \\
-}
-\end{eqnarray*}
-Furthermore, if the solution we started with was an RHF solution, the $\AtoB$ and 
-$\BtoA$ are identical. Letting $d_\AtoB = d_\BtoA = d$, we get the following forms 
-of the transformed eigenvectors, 
-\begin{eqnarray}\label{rhfvecs}
-  \mathbf{\tilde{D}''} = 
-  \begin{bmatrix}
-    d + d^*  \\
-    d + d^*  \\
-    -d + d^* \\
-    -d + d^* \\
-  \end{bmatrix}
-  =
-  \begin{bmatrix}
-    Re(d)  \\
-    Re(d)  \\
-    Im(d)  \\
-    Im(d)  \\
+    \e \diag - (aj|bi) & -(ab | ji )           \\
+    -(ab | ji )^*        & \e \diag - (aj|bi)^* \\        
   \end{bmatrix} 
 \end{eqnarray}
-At this point the only assumptions we made are that the two electron integrals and the
-energies are real-valued and that the solution we started with was an RHF solution. From
-this it immediately follows that the eigenvectors have the form of equation \ref{rhfvecs}.
 
-Clearly, the eigensystem defined by $\mathbf{H}''\mathbf{D}'' = 2E_2\mathbf{D}''$ is a
-doubly degenerate set of the following equations:
+The implication of equations \ref{b2aa2b}, \ref{a2bb2a} and \ref{3Heval} is that the following 
+sets of eigenvectors comprise a degenerate manifold when the solution is an RHF wavefunction.
 \begin{eqnarray}
-  \left[ \mathbf{A+B} \right] Re(d) &=& 2E_2 Re(d) \\
-  \left[ \mathbf{A-B} \right] Im(d) &=& 2E_2 Im(d) 
+  \begin{bmatrix}
+    \mathbf{d_\BtoA} \\
+    \mathbf{d^*_\AtoB} \\        
+  \end{bmatrix}
+  , 
+  \begin{bmatrix}
+    \mathbf{d_\AtoB} \\
+    \mathbf{d^*_\BtoA} \\        
+  \end{bmatrix}
+  ,
+  \begin{bmatrix}
+    \mathbf{d_\AtoA - d_\BtoB} \\
+    \mathbf{d^*_\AtoA - d^*_\BtoB} \\        
+  \end{bmatrix}
 \end{eqnarray}
-Where $\mathbf{A}$ and $\mathbf{B}$ are defined such that
-\begin{eqnarray}
-  A_{ia, jb} &=& \e\diag - \App \\
-  B_{ia, jb} &=& -\Br 
-\end{eqnarray}
-These matrices are exactly equivalent to ${}^3\mathbf{A}'$ and ${}^3\mathbf{B}'$ (eq 35 in Seeger
-\& Pople). Thus, when the matrices $\mathbf{A}$ and $\mathbf{B}$ are real, and the solution
-is an RHF solution, the eigenvalue problem is doubly degenerate, and factorizes into the equation
-characterized by the triplet instability equation.
+As such, the RHF-GHF instability eigenvectors can always be transformed into eigenvectors having the
+form of the RHF-UHF instability. On the other hand, if the solution is not an RHF solution, this is
+not the case and the eigenvalues/vectors and corresponding instabilities are distinct.
 
+\section{Numerical result}
+To verify numerically, the diagonalization of the matrices $\mathbf{H}, \mathbf{H}'$ and 
+${}^3\mathbf{H}'$ were implemented independently of one another. No factorizations or 
+simplifications were performed. The lowest eigenvalue of each is shown below for a constant number
+of K-points and a varying density. The results are equivalent within the convergence criteria of 
+Davidson's Algorithm.  
+\begin{figure}[h]
+  \includegraphics[width=0.75\linewidth]{../../images/Matrix_Compare.pdf}
+\end{figure}
+
+\begin{comment}
 \section{Proof of Real-Valued A and B}
@@
 So far I have not used this to simplify anything, but it is true.
-
+\end{comment}
 \section{References}

### 2017-04-05 HFS/src/matrix_gen.cpp

@@ -106,6 +106,25 @@ arma::mat HFS::Matrix::Gen::TripletH() {
     return buildMatrixFromFunctionList(HFS::Nmat, Ndivisions, locs, funcs);
 }
 
+arma::mat HFS::Matrix::Gen::SingletH() {
+    uint Ndivisions = 2;
+    std::vector<std::pair<uint, uint>> locs(4);
+    std::vector<scalar (*)(uint, uint)> funcs(4);
+
+    locs[0] = std::make_pair(0, 0);
+    funcs[0] = HFS::Matrix::Gen::A_E_delta_ij_delta_ab_plus_2aj_ib_minus_ajbi;
+
+    locs[1] = std::make_pair(0, 1);
+    funcs[1] = HFS::Matrix::Gen::B_minus_abji_plus_2abij;
+
+    locs[2] = std::make_pair(1, 0);
+    funcs[2] = HFS::Matrix::Gen::B_minus_abji_plus_2abij;
+
+    locs[3] = std::make_pair(1, 1);
+    funcs[3] = HFS::Matrix::Gen::A_E_delta_ij_delta_ab_plus_2aj_ib_minus_ajbi;
+    return buildMatrixFromFunctionList(HFS::Nmat, Ndivisions, locs, funcs);
+}
+
 scalar HFS::Matrix::Gen::A_E_delta_ij_delta_ab_plus_aj_ib_antisym(uint s, uint t) {
     std::vector<arma::vec> klist(4);
     klist = HFS::stToKiKaKjKb(s, t);
@@ -118,6 +137,33 @@ scalar HFS::Matrix::Gen::A_E_delta_ij_delta_ab_plus_aj_ib_antisym(uint s, uint t
     scalar A1 = HFS::kroneckerDelta(s, t) * HFS::exc_energies(s)
         + HFS::twoElectronSafe(ka, kj, ki, kb) - HFS::twoElectronSafe(ka, kj, kb, ki);
     return A1;
+}
+
+scalar HFS::Matrix::Gen::A_E_delta_ij_delta_ab_plus_2aj_ib_minus_ajbi(uint s, uint t) {
+    std::vector<arma::vec> klist(4);
+    klist = HFS::stToKiKaKjKb(s, t);
+    arma::vec ki(NDIM), kj(NDIM), ka(NDIM), kb(NDIM);
+    ki = klist[0];
+    ka = klist[1];
+    kj = klist[2];
[…]

### 2017-04-05 HFS/src/matrix_gen.hpp

@@ -25,14 +25,17 @@ namespace Gen {
                                                  std::vector<std::pair<uint, uint>> locs,
                                                  std::vector<scalar (*)(uint, uint)> Mfuncs);
     extern arma::mat TripletH();
+    extern arma::mat SingletH();
     extern arma::mat Hprime();
     extern arma::mat H();
     extern arma::mat buildHFromAandB(arma::mat& A, arma::mat& B);
 
     extern scalar A_E_delta_ij_delta_ab_plus_aj_ib_antisym(uint s, uint t);
+    extern scalar A_E_delta_ij_delta_ab_plus_2aj_ib_minus_ajbi(uint s, uint t);
     extern scalar A_aj_ib(uint s, uint t);
     extern scalar A_E_delta_ij_delta_ab_minus_aj_bi(uint s, uint t);
     extern scalar B_ab_ij_antisym(uint s, uint t);
+    extern scalar B_minus_abji_plus_2abij(uint s, uint t);
     extern scalar B_ab_ij(uint s, uint t);
     extern scalar B_minus_ab_ji(uint s, uint t);
 

### 2017-04-05 HFS/src/matrix_vectorproducts.cpp

@@ -15,6 +15,16 @@ void TripletH(arma::vec& v, arma::vec& Mv) {
     ApplyMvFxnsToSubMatrices(v, Mv, 2, MvList);
 }
 
+void SingletH(arma::vec& v, arma::vec& Mv) {
+    Mv.zeros();
+    std::vector<std::tuple<uint, uint, void (*)(arma::vec&, arma::vec&)>> MvList (4);
+
+    MvList[0] = std::make_tuple(0, 0, E_delta_st_plus_2aj_ib_minus_ajbi);
+    MvList[1] = std::make_tuple(0, 1, minus_abji_plus_2ab_ij);
+    MvList[2] = std::make_tuple(1, 0, minus_abji_plus_2ab_ij);
+    MvList[3] = std::make_tuple(1, 1, E_delta_st_plus_2aj_ib_minus_ajbi);
+    ApplyMvFxnsToSubMatrices(v, Mv, 2, MvList);
+}
 
 void Hprime(arma::vec& v, arma::vec& Mv) {
     Mv.zeros();
@@ -105,6 +115,27 @@ void E_delta_st_plus_aj_ib_antisym(arma::vec& v, arma::vec& Mv) {
     }
 }
 
+void E_delta_st_plus_2aj_ib_minus_ajbi(arma::vec& v, arma::vec& Mv) {
+    for (uint s = 0; s < HFS::Nexc; ++s) {
+        uint i = HFS::excitations(0, s), a = HFS::excitations(1, s);
+        arma::vec ki(NDIM), ka(NDIM);
+        HFS::occIndexToK(i, ki);
+        ka = HFS::virIndexToK(a);
+        for (uint j = 0; j < HFS::Nocc; ++j) {
+            arma::vec kj(NDIM), kb(NDIM);
+            HFS::occIndexToK(j, kj);
+            kb = ka + kj - ki; // Momentum conservation for <aj|ib> or <aj|bi>
+            HFS::toFirstBrillouinZone(kb);
+            if (arma::norm(kb) > (HFS::kf + SMALLNUMBER)) {
+                // only if momentum conserving state is virtual
+                uint t = HFS::Matrix::calcTfromKbAndJ(kb, j);
+                Mv(s) += (HFS::kroneckerDelta(s, t) * HFS::exc_energies(s)
+                        + 2 * HFS::twoElectron(ka, ki) - HFS::twoElectron(ka, kb)) * v(t);
+            }
[…]

### 2017-04-05 HFS/src/matrix_vectorproducts.hpp

@@ -27,8 +27,10 @@ namespace MatrixVectorProduct {
 
     extern void E_delta_st_plus_aj_ib_antisym(arma::vec& v, arma::vec& Mv);
     extern void E_delta_st_minus_aj_bi(arma::vec& v, arma::vec& Mv);
+    extern void E_delta_st_plus_2aj_ib_minus_ajbi(arma::vec& v, arma::vec& Mv);
     extern void aj_ib(arma::vec& v, arma::vec& Mv);
     extern void ab_ij_antisym(arma::vec& v, arma::vec& Mv);
+    extern void minus_abji_plus_2ab_ij(arma::vec& v, arma::vec& Mv);
     extern void ab_ij(arma::vec& v, arma::vec& Mv);
     extern void minus_ab_ji(arma::vec& v, arma::vec& Mv);
 

### 2017-04-05 doc/papers/matrixproperties/MatrixProperties.tex
Added eigenvalue histograms and updated matrixproperties.

@@
 \begin{eqnarray}
-  A_{st} &=& \e\diag +  \textcolor{myred}{\braket{aj||ib}} \\
-  B_{st} &=& \textcolor{myblue}{\braket{ab||ij}}         
+  A_{i \rightarrow a, j \rightarrow b} &=& \e\diag +  \textcolor{myred}{\braket{aj||ib}} \\
+  B_{i \rightarrow a, j \rightarrow b} &=& \textcolor{myblue}{\braket{ab||ij}}         
 \end{eqnarray}
@@
 ``spin-unconserved'' $(\mathbf{A'', B''})$ parts, to use the language of Seeger
-and Pople. Similarly, $\mathbf{H}$ factorizes, with no approximations, into
+and Pople. Similarly, $\mathbf{H}$ factorizes, with no further approximations, into
 $\mathbf{H}'$ and $ \mathbf{H}''$
@@
     0 &  0 & \mathbf{1} &  \mathbf{1} \\
-  \end{bmatrix}
+  \end{bmatrix},
 \end{eqnarray}
-
-With no further assumptions, this transformation doesn't do much. However, if the spatial
-orbitals corresponding to $\alpha$ and $\beta$ are assumed equivalent, the 
-transformed $\mathbf{H}'$ is
+and assuming the spatial orbitals corresponding to $\alpha$ and $\beta$ are equivalent (ie RHF), 
+the transformed $\mathbf{H}'$ is
 \begin{eqnarray*}
@@
     \mathbf{d^*_\AtoA - d^*_\BtoB} 
-  \end{bmatrix}
+  \end{bmatrix}.
 \end{eqnarray*}
@@
 \section{Numerical result}
-To verify numerically, the diagonalization of the matrices $\mathbf{H}, \mathbf{H}'$ and 
+To verify numerically, the brute force diagonalization of the matrices $\mathbf{H}, \mathbf{H}'$ 
+and 
 ${}^3\mathbf{H}'$ were implemented independently of one another. No factorizations or 
-simplifications were performed. The lowest eigenvalue of each is shown below for a constant number
-of K-points and a varying density. The results are equivalent within the convergence criteria of 
-Davidson's Algorithm.  
-\begin{figure}[h]
-  \includegraphics[width=0.75\linewidth]{../../images/Matrix_Compare.pdf}
+simplifications were performed. Let $\lambda_{\mathbf{M}}$ be the 
+set\footnote{Technically a multiset, as a set has only unique elements.} of eigenvalues of 
+square matrix $\mathbf{M}$, repeated according to their multiplicity, such that 
+\begin{eqnarray*}
+  \lambda_{\mathbf{H}} &=& \{ \text{All eigenvalues of } \mathbf{H}  \} \\
+  \lambda_{\mathbf{H'}} &=& \{ \text{All eigenvalues of } \mathbf{H'}  \} \\
+  \lambda_{\mathbf{{}^3H'}} &=& \{ \text{All eigenvalues of } \mathbf{{}^3H'}  \} \\
+  \lambda_{\mathbf{{}^1H'}} &=& \{ \text{All eigenvalues of } \mathbf{{}^1H'}  \} 
+\end{eqnarray*}
+To machine precision, the calculated eigenspectrum of  $\mathbf{H}'$ is
+equivalent to the union of the eigenvalues of ${}^3\mathbf{H}'$ and the eigenvalues of
+${}^1\mathbf{H}'$.
+\begin{equation}
+  \lambda_{\mathbf{H}'} = \lambda_{\mathbf{{}^3H}'} \cup \lambda_{\mathbf{{}^1H}'}  
+\end{equation}
+Similarly, the calculated eigenspectrum of $\mathbf{H}$ is equivalent to
+the union of the eigenvalues of ${}^1\mathbf{H}'$ and thrice-repeated eigenvalues
+of ${}^3\mathbf{H}'$ (two coming from the RHF limit of $\mathbf{H}''$ and one coming from
+$\mathbf{H}'$)
+\begin{equation}
+  \lambda_{\mathbf{H}} = \lambda_{\mathbf{{}^3H}'} \cup
+                              \lambda_{\mathbf{{}^3H}'} \cup
+                              \lambda_{\mathbf{{}^3H}'} \cup
+                               \lambda_{\mathbf{{}^1H}'}
+\end{equation}
+Visually, this information is presented in figure 1. This shows numerically that the RHF-GHF 
+instability is indistinguishable from the RHF-UHF instability, given an RHF wavefunction. 
+Lifting the symmetry of spatial orbitals between $\alpha$ and $\beta$ spin states will remove the
+degeneracies seen here, and the resulting UHF-GHF instability will become distinct from the RHF-UHF
+instability.  
+\begin{figure}[h]\label{histograms}
+  \includegraphics[width=\linewidth]{../../images/matrix_factor_histograms.pdf}
+  \caption{ Histogram of the calculated eigenspectra of stability matrices and factorizations. 
+  \newline \textbf{[Left]} The eigenspectrum of $\mathbf{H}$ (black outline, no fill) is equivalent 
+  to the 
+  set formed by combining the eigenspectra of $\mathbf{{}^3H'}$ (green), repeated thrice, and 
+  $\mathbf{{}^1H'}$ 
+  (blue).
+  \newline \textbf{[Right]} The eigenspectrum of $\mathbf{H'}$ (black outline, no fill) is 
+  equivalent to the 
+  set formed by combining the eigenspectra of $\mathbf{{}^3H'}$ (green) and $\mathbf{{}^1H'}$ 
+  (blue).  
+  \newline Although not apparent due to binning, all eigenvalues of factorized matrices agree
+  with eigenvalues of the unfactored matrix to machine precision. 
+  }
 \end{figure}

### 2017-04-05 HFS/src/debug.cpp

@@ -15,7 +15,7 @@ bool davidsonAgreesWithFullDiag() {
     arma::eig_sym(eigvals, eigvecs, matrix);
     HFS::full_diag_min = eigvals.min();
     HFS::full_diag_time = timer.toc();
-
+    HFS::exact_evals = eigvals;
     return true;
 }
 

### 2017-04-05 HFS/src/fileIO.cpp

@@ -100,6 +100,7 @@ namespace HFS {
             if (fabs(full_diag_min) > 1e-6) {
                 JSONVAL(full_diag_min);
                 JSONVAL(full_diag_time);
+                writeArmaVecToJSON(output, exact_evals, "exact_evals");
             }
 
             JSONVAL(dav_tol);
@@ -109,8 +110,8 @@ namespace HFS {
             JSONVAL(dav_time);
             #undef JSONVAL
             #undef JSONSTR
-
             if (detail) {
+
                 writeArmaVecToJSON(output, occ_energies, "occ_energies");
                 writeArmaVecToJSON(output, vir_energies, "vir_energies");
                 writeArmaVecToJSON(output, exc_energies, "exc_energies");

### 2017-04-05 HFS/src/main.cpp

@@ -97,8 +97,6 @@ int main(int argc, char* argv[]){
     HFS::dav_min_eval = HFS::dav_vals.min();
 
     // Finish up, write and test for problems.
-    HFS::writeJSON(HFS::OutputFileName, true);
-
     #ifndef NDEBUG
         if (HFS::Nmat < 1500) {
             HFS::davidsonAgreesWithFullDiag();
@@ -107,6 +105,8 @@ int main(int argc, char* argv[]){
             exit(EXIT_FAILURE);
         }
     #endif //NDEBUG
+
+    HFS::writeJSON(HFS::OutputFileName, true);
 
     return 0;
 }

### 2017-04-05 HFS/src/parameters.cpp

@@ -37,6 +37,7 @@ namespace HFS{
     arma::umat inv_exc_mat;
     void (*MatVecProduct_func)(arma::vec& v, arma::vec& Mv);
     arma::mat (*Matrix_generator)();
+    arma::vec exact_evals;
     uint dav_its;
     arma::vec dav_vals;
     uint num_guess_evecs;

### 2017-04-05 HFS/src/parameters.hpp

@@ -66,6 +66,7 @@ namespace HFS{
     extern uint dav_its;                  /**< Number of iterations to converge in Davidson's Algorithm  */
     extern arma::vec dav_vals;                /**< All eigenvalues returned by the last iteration of Davidson's Algorithm. */
     extern uint num_guess_evecs;          /**< Number of eigenvectors used as initial guess for Davidson's Algorithm. */
+    extern arma::vec exact_evals;         /**< Only used in debug mode, holds the full eigenvalue spectra of the matrix from HFS::Matrix_generator */
     extern uint dav_blocksize;            /**< Block size Davidson's Algorithm. */
     extern uint dav_num_evals;            /**< Number of eigenvalues requested for Davidson's Algorithm. */
     extern uint dav_nconv;                /**< Number of converged eigenpairs returned by Davidson's Algorithm. */

### 2017-04-08 HFS/src/base_funcs.cpp
Added 1D support

@@ -8,6 +8,9 @@
 
 
 #include "base_funcs.hpp"
+# if NDIM == 1
+#include <boost/math/special_functions/expint.hpp>
+# endif  // NDIM
 
 namespace HFS {
 
@@ -35,9 +38,12 @@ namespace HFS {
         if (norm < SMALLNUMBER) {
             return 0.0;
         }else{
-            #if NDIM == 2
+            # if NDIM == 1
+                return exp(norm * norm * HFS::two_e_const * HFS::two_e_const)
+                            * boost::math::expint(-norm * norm * HFS::two_e_const * HFS::two_e_const);
+            # elif NDIM == 2
                 return HFS::two_e_const / norm;
-            #elif NDIM == 3
+            # elif NDIM == 3
                 return HFS::two_e_const / (norm * norm);
             #endif
         }
@@ -64,23 +70,22 @@ namespace HFS {
         if (norm < SMALLNUMBER) {
             return 0.0;
         }else{
-            return HFS::two_e_const / std::pow(norm, NDIM - 1);
+            # if NDIM == 1
+                return exp(norm * norm * HFS::two_e_const * HFS::two_e_const)
+                            * boost::math::expint(-norm * norm * HFS::two_e_const * HFS::two_e_const);
+            # elif NDIM == 2
+                return HFS::two_e_const / norm;
+            # elif NDIM == 3
+                return HFS::two_e_const / (norm * norm);
+            #endif
         }
     }
-/*
-    arma::uvec kToIndex(arma::vec& k) {
-        arma::vec uint = arma::round((k + HFS::kmax) / HFS::deltaK);
-        arma::uvec indices = arma::conv_to<arma::uvec>::from(uint);
-        return indices;
-    }
-*/
+
     void kToIndex(arma::vec& k, arma::uvec& idx) {
         for (uint i = 0; i < NDIM; ++i) {
             idx[i] = std::round((k[i] + HFS::kmax) / HFS::deltaK);
         }
     }
-
-
 
     arma::umat kToIndex(arma::mat& k) {
         arma::mat idx = arma::round((k + HFS::kmax) / HFS::deltaK);

### 2017-04-08 HFS/src/calc_parameters.cpp

@@ -39,13 +39,14 @@ namespace HFS {
 
     void calcVolAndTwoEConst (uint N_elec, scalar rs, scalar& Vol, scalar& TwoEConst) {
         if (NDIM == 1) {
-            HFS::vol = HFS::N_elec * 2.0 * HFS::rs;
+            vol = N_elec * rs;
+            two_e_const = 0.01;    // 'a' for the exponential integral, radius of cylinder.
         } else if (NDIM == 2) {
-            HFS::vol = HFS::N_elec * PI * std::pow(HFS::rs, 2);
-            HFS::two_e_const = 2.0 * PI / HFS::vol;
+            vol = N_elec * PI * std::pow(rs, 2);
+            two_e_const = 2.0 * PI / vol;
         } else if (NDIM == 3) {
-            HFS::vol = HFS::N_elec * 4.0 / 3.0 * PI * std::pow(HFS::rs, 3);
-            HFS::two_e_const = 4.0 * PI / HFS::vol;
+            vol = N_elec * 4.0 / 3.0 * PI * std::pow(rs, 3);
+            two_e_const = 4.0 * PI / vol;
         }
     }
 
@@ -133,7 +134,7 @@ namespace HFS {
                         ,arma::umat& excitations
                         ,arma::vec&  exc_energies
                         ,uint& Nexc) {
-        arma::vec kexc(NDIM);
+        arma::vec  kexc(NDIM);
         arma::uvec vir_uint(NDIM);
         arma::uvec exc_uint(NDIM);
         excitations.set_size(2, Nocc * Nvir);
@@ -147,7 +148,6 @@ namespace HFS {
                 kexc = kgrid(occ_states.col(i));
                 kexc(0) += deltaK * j;
                 HFS::toFirstBrillouinZone(kexc);
-                //exc_uint = HFS::kToIndex(kexc);
                 HFS::kToIndex(kexc, exc_uint);
                 // Find the vir state
                 for (uint k = 0; k < vir_states.n_cols; ++k) {
@@ -161,8 +161,8 @@ namespace HFS {
 
             }
         }
-        excitations  = excitations.head_cols(Nexc); // excitations is now full
-        exc_energies = exc_energies.head(Nexc);  // set the size of exc_energies
+        excitations  = excitations.head_cols(Nexc); // clip size
[…]

### 2017-04-08 HFS/src/calc_parameters.hpp

@@ -131,7 +131,7 @@ namespace HFS {
     /**< \brief Create the Map to convert between 3/2-index and 1-index representation of virtual state.
 
     The NDIM compiler directory determines if this is an arma::ucube (3d) or arma::umat
-    (2d).
+    (2d) or arma::uvec (1d).
     @see NDIM
     @see vir_N_to_1_mat
     @see vir_states

### 2017-04-08 HFS/src/fileIO.cpp

@@ -88,6 +88,7 @@ namespace HFS {
             JSONVAL(Nocc);
             JSONVAL(Nvir);
             JSONVAL(Nexc);
+            JSONVAL(Nmat);
             JSONVAL(ground_state_degeneracy);
             JSONVAL(dav_its);
             JSONVAL(num_guess_evecs);

### 2017-04-08 HFS/src/main.cpp

@@ -33,7 +33,7 @@ int main(int argc, char* argv[]){
 
     // Defaults
     HFS::rs              = 1.2;
-    HFS::Nk              = 12;
+    HFS::Nk              = 22;
     HFS::mycase          = "cRHF2cUHF";
     HFS::OutputFileName  = "HFS.json";
 
@@ -62,39 +62,53 @@ int main(int argc, char* argv[]){
     /* Calculation starts here */
     HFS::calcParameters();
     HFS::Matrix::setMatrixPropertiesFromCase(); // RHF-UHF etc instability, matrix dimension
-    HFS::timeMatrixVectorProduct();
 
-    SLEPc::EpS myeps(HFS::Nmat, HFS::MatVecProduct_func);
-    int nprocs = 1;
-    //MPI_Comm_size(MPI_COMM_WORLD, &nprocs);
-    myeps.nprocs = nprocs;
-    myeps.SetDimensions(HFS::dav_num_evals, HFS::dav_max_subsize);
-    myeps.SetTol(HFS::dav_tol, HFS::dav_maxits);
-    myeps.SetBlockSize(HFS::dav_blocksize);
+    # if NDIM != 1
+        HFS::timeMatrixVectorProduct();
 
-    // Choose guess eigenvectors for davidson. Weight by how close diags are.
-    std::vector< std::vector<scalar> > vecs(HFS::num_guess_evecs, std::vector<scalar>(HFS::Nmat, 0.0));
-    for (uint i = 0; i < HFS::num_guess_evecs; ++i) {
-        arma::vec guessvec;
-        arma::vec temp = arma::abs(HFS::exc_energies[i] - HFS::exc_energies) + 1;
-        guessvec = (1.0 / temp);
-        guessvec /= arma::norm(guessvec);
-        vecs[i] = arma::conv_to< std::vector<scalar> >::from(guessvec);
-    }
+        SLEPc::EpS myeps(HFS::Nmat, HFS::MatVecProduct_func);
+        int nprocs = 1;
+        //MPI_Comm_size(MPI_COMM_WORLD, &nprocs);
+        myeps.nprocs = nprocs;
+        myeps.SetDimensions(HFS::dav_num_evals, HFS::dav_max_subsize);
+        myeps.SetTol(HFS::dav_tol, HFS::dav_maxits);
+        myeps.SetBlockSize(HFS::dav_blocksize);
 
-    // Davidson Algorithm
[…]

### 2017-04-08 HFS/src/main.hpp

@@ -7,6 +7,7 @@ taken as command line input.
 @date Wednesday, 04 Jan, 2017
 */
 
+#define __STDCPP_WANT_MATH_SPEC_FUNCS__
 #include <iostream>
 #include <cmath>
 #include <assert.h>

### 2017-04-08 HFS/src/matrix_vectorproducts.cpp

@@ -298,11 +298,15 @@ void ApplyMvFxnsToSubMatrices(
 
 uint calcTfromKbAndJ(arma::vec& kb, uint j) {
     arma::uvec b_N_uint(NDIM); kToIndex(kb, b_N_uint);
-    #if NDIM == 2
+    # if NDIM == 1
+        uint b = HFS::vir_N_to_1_mat(b_N_uint(0));
+    # endif
+    # if NDIM == 2
         uint b = HFS::vir_N_to_1_mat(b_N_uint(0), b_N_uint(1));
-    #elif NDIM == 3
+    # endif
+    # if NDIM == 3
         uint b = HFS::vir_N_to_1_mat(b_N_uint(0), b_N_uint(1), b_N_uint(2));
-    #endif // NDIM
+    #endif
     uint t = HFS::inv_exc_mat(j, b);
     return t;
 }

### 2017-04-08 HFS/src/parameters.cpp

@@ -29,11 +29,15 @@ namespace HFS{
     arma::umat occ_states;
     arma::umat vir_states;
     arma::umat excitations;
-    #if NDIM == 2
+    # if NDIM == 1
+      arma::uvec vir_N_to_1_mat;
+    # endif
+    # if NDIM == 2
       arma::umat vir_N_to_1_mat;
-    #elif NDIM == 3
+    # endif
+    # if NDIM == 3
       arma::ucube vir_N_to_1_mat;
-    #endif // NDIM;
+    #endif
     arma::umat inv_exc_mat;
     void (*MatVecProduct_func)(arma::vec& v, arma::vec& Mv);
     arma::mat (*Matrix_generator)();

### 2017-04-08 HFS/src/parameters.hpp

@@ -11,6 +11,8 @@
 #ifndef HFS_PARAMS_INCLUDED
 #define HFS_PARAMS_INCLUDED
 
+#define __STDCPP_WANT_MATH_SPEC_FUNCS__
+
 #ifndef PI
     #define PI 3.14159265358979323846264338327
 #endif
@@ -55,11 +57,15 @@ namespace HFS{
     extern arma::umat occ_states;             /**< Matrix where the i'th row contains the indices for kgrid of the i'th occupied state. */
     extern arma::umat vir_states;             /**< Matrix where the i'th row contains the indices for kgrid of the i'th virtual state. */
     extern arma::umat excitations;            /**< Matrix where the i'th row contains the indices for the corresponding [occupied, virtual] states. */
-    #if NDIM == 2
+    # if NDIM == 1
+      extern arma::uvec vir_N_to_1_mat;
+    # endif
+    # if NDIM == 2
       extern   arma::umat vir_N_to_1_mat;       /**< Matrix/Cube where the value is the virtual state index */
-    #elif NDIM == 3
+    # endif
+    # if NDIM == 3
       extern   arma::ucube vir_N_to_1_mat;
-    #endif // NDIM;
+    #endif
     extern arma::umat inv_exc_mat;            /**< The [i,a]'th element is s, where s labels the excitation i -> a.  */
     extern void (*MatVecProduct_func)(arma::vec& v, arma::vec& Mv); /**< Function pointer for the matrix-vector product. Is set by HFS::setMatrixPropertiesFromCase */
     extern arma::mat (*Matrix_generator)();   /**< Function pointer for the matrix elements. Is set by HFS::setMatrixPropertiesFromCase */

### 2017-04-10 doc/presentations/GroupMeeting_Fall2016/GroupMeeting_Fall2016.tex
Added grp meet for spring

--- 2017-03-08 doc/presentations/GroupMeeting_Fall2016.tex
@@
 \institute{University of Illinois at Urbana-Champaign}
-\titlegraphic{\hfill\includegraphics[height=1.5cm]{../images/imark_bold.eps}}
+\titlegraphic{\hfill\includegraphics[height=1.5cm]{../../images/imark_bold.eps}}
 
@@
 	\begin{center}
-		\includegraphics[width=0.5\textwidth, trim={3cm, 2cm, 3cm, 2cm}, clip]{../images/1d_extrema.pdf}
+		\includegraphics[width=0.5\textwidth]{../../images/1d_extrema.pdf}
 	\end{center}
@@
 		    \begin{overprint}
-			    \onslide<1>\includegraphics[width=0.9\linewidth, trim={7cm, 2cm, 7cm, 3cm}, clip]{../images/const_opt_globalmin.jpeg}
-				\onslide<2>\includegraphics[width=0.9\linewidth, trim={7cm, 1cm, 7cm, 1cm}, clip]{../images/const_opt_saddle.jpeg}
-				\onslide<3>\includegraphics[width=0.9\linewidth, trim={7cm, 2cm, 7cm, 3cm}, clip]{../images/const_opt_nonstationary.jpeg}
+			    \onslide<1>\includegraphics[width=0.9\linewidth, trim={7cm, 2cm, 7cm, 3cm}, clip]{../../images/const_opt_globalmin.jpeg}
+				\onslide<2>\includegraphics[width=0.9\linewidth, trim={7cm, 1cm, 7cm, 1cm}, clip]{../../images/const_opt_saddle.jpeg}
+				\onslide<3>\includegraphics[width=0.9\linewidth, trim={7cm, 2cm, 7cm, 3cm}, clip]{../../images/const_opt_nonstationary.jpeg}
 			\end{overprint}
@@
 		    \begin{overprint}
-			    \onslide<1>\includegraphics[width=\linewidth]{../images/1stBZ.eps}
+			    \onslide<1>\includegraphics[width=\linewidth]{../../images/1stBZ.eps}
 
@@
 		    \begin{overprint}
-			    \onslide<1>\includegraphics[width=\linewidth]{../images/energycompare.eps}
+			    \onslide<1>\includegraphics[width=\linewidth]{../../images/energycompare.eps}
 
@@
 		    \begin{overprint}
-			    \onslide<1>\includegraphics[width=\linewidth]{../images/exchist.eps}
+			    \onslide<1>\includegraphics[width=\linewidth]{../../images/exchist.eps}
 
@@
 		    \begin{overprint}
-			    \onslide<1>\includegraphics[width=\linewidth]{../images/matscale.eps}
+			    \onslide<1>\includegraphics[width=\linewidth]{../../images/matscale.eps}
 
@@
 		    \begin{overprint}
-			    \onslide<1>\includegraphics[width=\linewidth]{../images/mvscaling.eps}
+			    \onslide<1>\includegraphics[width=\linewidth]{../../images/mvscaling.eps}
 
@@
 		    \begin{overprint}
-			    \onslide<1>\includegraphics[width=\linewidth]{../images/dav_vs_exact_scaling.eps}
+			    \onslide<1>\includegraphics[width=\linewidth]{../../images/dav_vs_exact_scaling.eps}
 
@@
 		\begin{column}{0.6\textwidth}
-		    \includegraphics[width=\linewidth]{../images/overallruntime.eps}
+		    \includegraphics[width=\linewidth]{../../images/overallruntime.eps}
 		\end{column}
@@
 		    \begin{overprint}
-			    \onslide<1>\includegraphics[width=\linewidth]{../images/dav_vs_exact.eps}
+			    \onslide<1>\includegraphics[width=\linewidth]{../../images/dav_vs_exact.eps}
 
@@
 	Crossover from stable to unstable agrees with previous results.
-	\includegraphics[width=.95\linewidth]{../images/MeVsBernu.pdf}
+	\includegraphics[width=.95\linewidth]{../../images/MeVsBernu.pdf}
 \end{frame}
@@
 	3D data is currently inconclusive. 
-	\includegraphics[width=.95\linewidth]{../images/2d3dstability.eps}
+	\includegraphics[width=.95\linewidth]{../../images/2d3dstability.eps}
 \end{frame}

### 2017-04-10 doc/presentations/GroupMeeting_Spring2017/GroupMeeting_Fall2017.tex
Added grp meet for spring

--- 2017-04-10 doc/presentations/GroupMeeting_Fall2016/GroupMeeting_Fall2016.tex
@@
 		    \begin{overprint}
-			    \onslide<1>\includegraphics[width=0.9\linewidth, trim={7cm, 2cm, 7cm, 3cm}, clip]{../../images/const_opt_globalmin.jpeg}
-				\onslide<2>\includegraphics[width=0.9\linewidth, trim={7cm, 1cm, 7cm, 1cm}, clip]{../../images/const_opt_saddle.jpeg}
-				\onslide<3>\includegraphics[width=0.9\linewidth, trim={7cm, 2cm, 7cm, 3cm}, clip]{../../images/const_opt_nonstationary.jpeg}
+			    \onslide<1>\includegraphics[width=0.9\linewidth, trim={7cm, 2cm, 7cm, 3cm}, 
+			    clip]{../../images/const_opt_globalmin.jpeg}
+				\onslide<2>\includegraphics[width=0.9\linewidth, trim={7cm, 1cm, 7cm, 1cm}, 
+				clip]{../../images/const_opt_saddle.jpeg}
+				\onslide<3>\includegraphics[width=0.9\linewidth, trim={7cm, 2cm, 7cm, 3cm}, 
+				clip]{../../images/const_opt_nonstationary.jpeg}
 			\end{overprint}
@@
 {%
+	\setbeamertemplate{frame footer}{}
+
+\begin{frame}{Matrix Factorizations}
+\vspace{-6mm}
+\begin{eqnarray*}
+  \begin{bmatrix}
+    \mathbf{A} & \mathbf{B} \\
+    \mathbf{B^*} & \mathbf{A^*} 
+  \end{bmatrix}
+  \begin{bmatrix}
+    \mathbf{d} \\
+    \mathbf{d^*} 
+  \end{bmatrix}
+  = 2E_2
+  \begin{bmatrix}
+    \mathbf{d} \\
+    \mathbf{d^*} 
+  \end{bmatrix}
+\end{eqnarray*}
+We can now apply the similarity transform defined by the Unitary matrix 
+\begin{eqnarray*}
+  \mathbf{U} = \frac{1}{\sqrt{2}}
+  \begin{bmatrix}
+    \mathbf{I} & -\mathbf{I} \\
+    \mathbf{I} & \mathbf{I} 
+  \end{bmatrix}
+\end{eqnarray*}
+after which the transformed eigenvalue problem has the form
+\begin{eqnarray*}
+  \frac{1}{2}
+  \begin{bmatrix}
+    \mathbf{A + B + A^* + B^*} & \mathbf{-A + A^* + B - B^*} \\
+    \mathbf{-A + A^* - B + B^*} & \mathbf{A^* + A - B - B^*} 
+  \end{bmatrix}
+  \begin{bmatrix}
+    \mathbf{d + d^*} \\
+    \mathbf{d - d^*} 
+  \end{bmatrix}
+  &=& 2E_2
+  \begin{bmatrix}
+    \mathbf{d + d^*} \\
+    \mathbf{-d + d^*} 
+  \end{bmatrix} \\
+  &=& 2E_2
+  \begin{bmatrix}
+    \mathbf{Re(d)} \\
+    \mathbf{Im(d)} 
+  \end{bmatrix}
+\end{eqnarray*}
+If $\mathbf{A}$ and $\mathbf{B}$ are both real, $\mathbf{A = A^*}$ and $\mathbf{B = B^*}$ and the 
+above simplifies to 
+\begin{eqnarray*}
+  \begin{bmatrix}
+    \mathbf{A + B} & \mathbf{0} \\
+    \mathbf{0} & \mathbf{A - B} 
+  \end{bmatrix}
+  \begin{bmatrix}
+    \mathbf{Re(d)} \\
+    \mathbf{Im(d)} 
+  \end{bmatrix}
+  &=& 2E_2   
+  \begin{bmatrix}
+    \mathbf{Re(d)} \\
+    \mathbf{Im(d)} 
+  \end{bmatrix}
+\end{eqnarray*}
+\end{frame}
+
+{%
 	\setbeamertemplate{frame footer}{1) Seeger, R.; Pople, J. A. J. Chem. Phys. 1977, 66 (7), 3045.}
@@
 	\begin{itemize}
-		\item[]{The eigenvalue equation can be factorized depending on symmetry.} \\~\\
+		\item[]{Doing this for all cases yields} \\~\\
 		\item[]{
@@
 				  \midrule
-				  Real RHF    & ${}^1\mathbf{A}' + {}^1\mathbf{B}'$ & ${}^1\mathbf{A}' - {}^1\mathbf{B}'$ & ${}^3\mathbf{A}' + {}^3\mathbf{B}'$ & - & - & -  \\
-				  Complex RHF & - & ${}^1\mathbf{H}'$ & - & \alert{${}^3\mathbf{H}'$} & - & - \\
-				  Real UHF    & - & - & $\mathbf{A}' + \mathbf{B}'$ & $\mathbf{A}' - \mathbf{B}'$ & $\mathbf{A}'' + \mathbf{B}''$ & - \\
+				  Real RHF    & ${}^1\mathbf{A}' + {}^1\mathbf{B}'$ & ${}^1\mathbf{A}' - {}^1\mathbf{B}'$ & 
+				  ${}^3\mathbf{A}' + {}^3\mathbf{B}'$ & ${}^3\mathbf{A}' - {}^3\mathbf{B}'$ & 
+				  ${}^3\mathbf{A}' + {}^3\mathbf{B}'$ & ${}^3\mathbf{A}' - {}^3\mathbf{B}'$  \\
+				  Complex RHF & - & \alert{${}^1\mathbf{H}'$} & - & \alert{${}^3\mathbf{H}'$} & - & 
+				  ${}^3\mathbf{H}'$ \\
+				  Real UHF    & - & - & $\mathbf{A}' + \mathbf{B}'$ & $\mathbf{A}' - \mathbf{B}'$ & 
+				  $\mathbf{A}'' + \mathbf{B}''$ & $\mathbf{A}'' - \mathbf{B}''$ \\
 				  Complex UHF & - & - & - &  $\mathbf{H}'$ & - & $\mathbf{H}'$ \\
@@
 				\begin{cases}
-				e^{|k-k''|^2a^2}\text{Ei}(-|k-k''|^2a^2)\text{ ;}
+				\frac{\pi}{V}e^{|k-k''|^2a^2}\text{Ei}(-|k-k''|^2a^2)\text{ ;}
 				& k''' = k+k'-k'' \\
@@
 
-\begin{comment}
-\section{Notes on Iterative Subspace Eigenvalue Methods}
+{%
+	\setbeamertemplate{frame footer}{Ceperley, D. M.; Alder, B. J. Phys. Rev. Lett. 1980, 45 (7), 
+		566–569.}
+
+\begin{frame}{Exact Results}
+  \centering
+	QMC Energies for various phases
+	\includegraphics[width=.85\linewidth]{../../images/Ceperley_PhaseDiag.png}
+\end{frame}
+
+\section{Iterative Subspace Eigenvalue Methods}
 {%
@@
  2. Davidson, E. R. J. Comput. Phys. 1975, 17 (1), 87–94.}
-\begin{frame}{Subspace Methods in 1 Slide}
-	\begin{itemize}
-		\item{Sometimes the eigenvalue problem is too large to solve completely, and only a few eigenpairs are needed}
-		\item{Subspace methods allow for finding some eigenpairs without full diagonalization}.
-		\item{They need only a matrix-vector product (maybe diagonal elements too).}
-		\item{A small subspace is constructed, then expanded slowly until the eigenpair residual norm,
-			\begin{eqnarray}
-				||\mathbf{Ax} - \lambda \mathbf{x}||,
-			\end{eqnarray}
-		is below some threshold.
-		}
-		\item{The \alert{Lanczos} and \alert{Arnoldi} methods are the most commonly used$^1$, while the \alert{Davidson}$^2$ method is likely more useful in a majority of chemical applications. }
-	\end{itemize}
+\begin{frame}{Davidson's Algorithm}
+  \begin{tabular}{l r}
+    $\bf{Ax}=\lambda\bf{x}$         & Eigenvalue Problem \\
+    $\bf{V}=[\bf{v_1,v_2,...,v_M}]$	& Guess vectors \\
+    $\bf{\tilde{A}} = \bf{V}^\dag\bf{AV}$  & Transform into subspace\\ 
+    $\bf{\tilde{A}\tilde{x}}=\tilde{\lambda}\bf{\tilde{x}}$ & Solve the subspace problem\\
+  	$\mathbf{x_i} \approx \mathbf{x}_i^R = \mathbf{V\tilde{x}}_i$ & Approximate eigenvectors\\
+  	$\lambda_i \approx \lambda_i^R = \tilde{\lambda}_i$ & Approximate eigenvalues \\
+    $\mathbf{r}_i=\left(\mathbf{A}-\lambda_i\mathbf{I}\right)\mathbf{x}_i^R $ & Calculate the 
+    residue \\
+    $\mathbf{\delta}_i = c_i\mathbf{r}_i$ & Correction vectors \\
+    $c_i = \frac{1}{\lambda_i\mathbf{I}-\mathbf{D}}$ & Diagonal Precondition \\
+    $\mathbf{V} = 
+    [\mathbf{v_1,v_2,...,v_M}\mathbf{,\delta}_1\mathbf{,\delta}_2,...\mathbf{,\delta}_l]$ & Append 
+    to guess and restart \\ 
+    $\mathbf{V} = orthonormalized(\mathbf{V})$ & Ensure orthonormal projection
+  \end{tabular}
 \end{frame}
@@
 			\item{The \alert{initial guess} eigenvectors}
-			\item{The \alert{condition number} of the eigenvector matrix}
+			%\item{The \alert{condition number} of the eigenvector matrix}
 			\item{The \alert{preconditioner} (Davidson only)}
 		\end{itemize}
-		\item{They can \alert{converge to an incorrect answer} if:}
+		\item{They can \alert{converge to an eigenvalue other than the target} if:}
 		\begin{itemize}
@@
 
-\begin{comment}
 {%
@@
 \end{frame}
-\end{comment}
 
@@
 \end{frame}
+
+\end{comment}
 
@@
 \begin{frame}{Dependence on r${}_s$}
-	Crossover from stable to unstable agrees with previous results.
+	Crossover from stable to unstable in 2D agrees with previous results.
 	\includegraphics[width=.95\linewidth]{../../images/MeVsBernu.pdf}
@@
 \begin{frame}{Dependence on r${}_s$}
-	3D data is currently inconclusive. 
-	\includegraphics[width=.95\linewidth]{../../images/2d3dstability.eps}
+\centering
+	3D data implies some stability at high density 
+	\includegraphics[width=.65\linewidth]{../../images/3dstab.pdf}
+\end{frame}
+
+{%
+\setbeamertemplate{frame footer}{}
+\begin{frame}{Dependence on r${}_s$}
+  \centering
+	Preliminary data for 1D shows some stability 
+	\includegraphics[width=.65\linewidth]{../../images/1dstab.pdf}
 \end{frame}

### 2017-04-10 HFS/launch.py

@@ -11,11 +11,11 @@ def getFilename(rs, Nk, ndim, case):
     return fname
 
 exe = './bin/HFSrelease1D'
-Nklist = list(range(62, 162, 10))
-rslist = np.linspace(0.1, 20, 20)
+Nklist = list(range(22, 112, 10))
+rslist = np.logspace(-3, 1.4, 10)
 caselist = ['cRHF2cRHF', 'cRHF2cUHF']
 
-jobrank = itertools.cycle([1,2,3])
+jobrank = itertools.cycle([1,2])
 
 count = 1
 lines = []
@@ -25,7 +25,7 @@ for nk in Nklist:
             cmd = exe + ' --Nk ' + str(nk) + ' --rs ' + str(rs) + ' --mycase ' + case
             cmd += ' --fname ' + getFilename(rs, nk, 1, case) + '.json &\n'
             lines.append(cmd)
-            if next(jobrank) == 3:
+            if next(jobrank) == 2:
                 lines.append('echo ----------------Running set \#' + str(count) + ' -----------------------------\n')
                 count += 1
                 lines.append('wait\n')

### 2017-04-10 HFS/launch.sh

@@ -1,266 +1,360 @@
-./bin/HFSrelease1D --Nk 22 --rs 0.1 --mycase cRHF2cRHF --fname ./000000.100_00022_1_cRHF2cRHF_2ve0e6td.json &
-./bin/HFSrelease1D --Nk 22 --rs 0.1 --mycase cRHF2cUHF --fname ./000000.100_00022_1_cRHF2cUHF_7iq1ahc5.json &
-./bin/HFSrelease1D --Nk 22 --rs 1.14736842105 --mycase cRHF2cRHF --fname ./000001.147_00022_1_cRHF2cRHF_a0rfmzgk.json &
+./bin/HFSrelease1D --Nk 22 --rs 0.001 --mycase cRHF2cRHF --fname ./000000.001_00022_1_cRHF2cRHF_fbcjsbh6.json &
+./bin/HFSrelease1D --Nk 22 --rs 0.001 --mycase cRHF2cUHF --fname ./000000.001_00022_1_cRHF2cUHF_44vn9s9o.json &
 echo ----------------Running set \#1 -----------------------------
 wait
-./bin/HFSrelease1D --Nk 22 --rs 1.14736842105 --mycase cRHF2cUHF --fname ./000001.147_00022_1_cRHF2cUHF_oot_x2j6.json &
-./bin/HFSrelease1D --Nk 22 --rs 2.19473684211 --mycase cRHF2cRHF --fname ./000002.195_00022_1_cRHF2cRHF_ml829f9m.json &
-./bin/HFSrelease1D --Nk 22 --rs 2.19473684211 --mycase cRHF2cUHF --fname ./000002.195_00022_1_cRHF2cUHF_c6xmhc6x.json &
+./bin/HFSrelease1D --Nk 22 --rs 0.00308239923975 --mycase cRHF2cRHF --fname ./000000.003_00022_1_cRHF2cRHF_qcqi6qen.json &
+./bin/HFSrelease1D --Nk 22 --rs 0.00308239923975 --mycase cRHF2cUHF --fname ./000000.003_00022_1_cRHF2cUHF_su10jlhb.json &
 echo ----------------Running set \#2 -----------------------------
 wait
-./bin/HFSrelease1D --Nk 22 --rs 3.24210526316 --mycase cRHF2cRHF --fname ./000003.242_00022_1_cRHF2cRHF_o79hgp57.json &
[…]

### 2017-04-10 HFS/src/calc_parameters.cpp

@@ -40,7 +40,8 @@ namespace HFS {
     void calcVolAndTwoEConst (uint N_elec, scalar rs, scalar& Vol, scalar& TwoEConst) {
         if (NDIM == 1) {
             vol = N_elec * rs;
-            two_e_const = 0.01;    // 'a' for the exponential integral, radius of cylinder.
+            scalar a = 0.01;
+            two_e_const = a * PI / vol;    // 'a' for the exponential integral, radius of cylinder.
         } else if (NDIM == 2) {
             vol = N_elec * PI * std::pow(rs, 2);
             two_e_const = 2.0 * PI / vol;

### 2017-04-10 analysis/pyfiles/HFSAnalyzer.py

@@ -358,7 +358,7 @@ def plot_mvproduct_scaling(df, ax, scale=2):
     x = Nexcs * Noccs
 
 #ax.set_title('Matrix - Vector Product Scaling')
-    if len(df > 2):
+    if len(df) > 2:
     	x_split = np.array_split(x, 2)[1]
     	mvtimes_split = np.array_split(mvtimes, 2)[1]
 

### 2017-05-19 doc/papers/paper_skeleton/paper_skeleton.tex
Fixed high density segfault in 1D. Added skeleton

\documentclass{revtex4}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{braket}

\newcommand{\ki}{\mathbf{k}_{i}}
\newcommand{\kj}{\mathbf{k}_{j}}
\newcommand{\ka}{\mathbf{k}_{a}}
\newcommand{\kb}{\mathbf{k}_{b}}
\newcommand{\kp}{\mathbf{k}_{p}}
\newcommand{\kq}{\mathbf{k}_{q}}
\newcommand{\kr}{\mathbf{k}_{r}}
\newcommand{\ks}{\mathbf{k}_{s}}

\makeatletter
\makeatother

\begin{document}
\title{Hartree-Fock Stability Analysis of the Paramagnetic Homogeneous Electron Gas in
1, 2 and 3 Dimensions.}
\author{Evan Curtin, So Hirata}
\maketitle

\section{Abstract}

\section{Introduction}

\section{Methods}
We consider the paramagnetic state of the Homogeneous Electron Gas (HEG) in a $D$-dimensional
box of length $L$. All states below the fermi wave vector, $k_f$ are doubly occupied, and all
above are virtual. According to Guiliani and Vignale\cite{Guiliani2005}, $k_f$ is given by equation 
\ref{kf} for 1, 2 and 3 dimensions.

\begin{eqnarray} \label{kf}
k_f
=\begin{cases} 
  (3\pi^2n)^{\frac{1}{3}} = \left(\frac{9\pi}{4}\right)^{\frac{1}{3}}\frac{1}{r_sa_0} & 3D \\ \\
  (2\pi n)^{\frac{1}{2}} = \frac{\sqrt{2}}{r_sa_0}  & 2D \\
  \\
  \frac{\pi}{2}n = \frac{\pi}{4 r_s a_0}   & 1D 
 \end{cases} 
\end{eqnarray}

The Hartree-Fock Hamiltonian  is defined in the usual way for the HEG in that the positive
background charge exactly cancels the electron-electron coulomb interaction. One solution of the 
Hartree-Fock equation is a set of plane waves,

\begin{eqnarray} \label {planewave}
  \phi_k(\vec{r}) = \frac{ e^ {i \bf{k} \cdot \bf{r}}} {\sqrt{D^N}},  
\end{eqnarray}

defined with periodic boundary conditions\cite{Phillips2012}. Do determine the stability of these
RHF solutions, we use the method introduced by Thouless \cite{Thouless1960}, and further 
chatagerized by Seeger and Pople \cite{Seeger1977}. The solutions of the Hartree-Fock equations are 
unstable when the Molecular Orbital Hessian,

\begin{eqnarray} \label{H}
  \bf{H} = 
  \begin{bmatrix}
    \bf{A}   & \bf{B} \\
    \bf{B^*} & \bf{A^*}\\
  \end{bmatrix},
\end{eqnarray}

has any strictly negative eigenvalues. An unstable HF solution is one that is a stationary solution
to the HF equations, but has a negative second-order variation in the energy with respect to 
electronic oscillations. Thus, a solution being
unstable is a sufficient condition for another solution of lower energy existing.

The square matrices $\bf{A}$ and $\bf{B}$ are defined in 
terms of the excitations of the system, and thus have the size of the number of possible 
excitations. Their elements are

\begin{eqnarray} \label{A_B}
	A_{\ki\rightarrow \ka, \kj\rightarrow \kb} &=& 
	(\epsilon_{\ka} - \epsilon_{\ki})\delta_{\ki\kj}\delta_{\ka\kb} + \braket{\ka\kj||\ki\kb}\\
	B_{\ki\rightarrow \ka, \kj\rightarrow \kb} &=& \braket{\ka\kb||\ki\kj},  \nonumber
\end{eqnarray}

where $\epsilon_{\ki}$ is the $i$'th eigenvalue of the one-electron Fock operator. 
The convention for the two electron integrals is,

\begin{eqnarray} \label{TwoElectron}
  \braket{\kp\kq|\kr\ks}  &=& \int\int \phi_{\kp}^*(\mathbf{x}_1) \phi_{\kq}^*(\mathbf{x}_2) 
                              \frac{1}{r_{12}} 
                              \phi_{\kr}(\mathbf{x}_1) \phi_{\ks}(\mathbf{x}_2) 
                              \mathrm{d}\mathbf{x}_1  \mathrm{d}\mathbf{x}_2, \\
  \braket{\kp\kq||\kr\ks} &=& \braket{\kp\kq|\kr\ks} - \braket{\kp\kq|\ks\kr}                  
\end{eqnarray}

and the integration is over both Cartesian and spin coordinates. The analytic form of the two 
electron integral for the case of the HEG is given by

\begin{subequations} 
  \begin{eqnarray} \label{TwoElectronAnalytic}
    \braket{\kp\kq||\kr\ks}\stackrel{\text{2D, 3D}}{=}
    	\begin{cases} 
      	\frac{\pi}{\Omega} \frac{2^{D-1}}{ |\kp - \kr|^{D-1} } 
      	& \ks + \kr = \kp + \kq  \mathrm{~and~} | \kp - \kr | \neq 0 \\
      	0 
      	& \text{else}
    	\end{cases}
    \\ \nonumber \\
    \braket{\kp\kq||\kr\ks}\stackrel{\text{1D}}{=}
    	\begin{cases} 
      	e^{ |\kp - \kr|^2a^2 }  \text{Ei} (-|\kp - \kr|^2a^2)
      	& \ks + \kr = \kp + \kq \mathrm{~and~} | \kp - \kr | \neq 0 \\
      	0 
      	& \text{else}
    	\end{cases},
  \end{eqnarray}
\end{subequations}

where $\Omega$ is the direct lattice volume. \cite{Delyon2008} \cite{Guiliani2005}. Ei(x) 
denotes the exponential integral function and the parameter $a$ in 1D is the radius of a cylinder
that approximates a 1D system (For more details we refer the reader to reference 
\cite{Guiliani2005}). The eigenenergies of the one particle Fock operator can be determined by
evaluating

\begin{equation} \label{eq:hf_orb_energy}
  \epsilon_{\kp}=
  	\frac{\hbar^2|\kp|^2}{2m} - \sum\limits_{\ki}^{occ}
    n_{\ki} \braket{\kp, \ki | \ki, \kp}
\end{equation}
Where $n_{\ki}$ is the occupation number of the state $\ki$ and spin \cite{Guiliani2005}.

A program was implemented to calculate the stability of the HEG with a simple cubic lattice in 1, 2
and 3 dimensions. As we are only interested in the presence of any number of negative eigenvalues, 
it suffices to calculate the lowest eigenvalue and determine its sign. Due to the sparse and 
diagonally dominant nature of $\mathbf{H}$, this is a natural candidate for the Jacobi-Davidson 
Algorithm \cite{Davidson1975}. The algorithm was implented using the SLEPc package, an extension of 
the PETSc suite \cite{Hernandez2005}\cite{petsc-web-page}.

\section{Discussion}

\section{Conclusion}

\section{Acknowledgements}

\section{References}
\bibliography{paper_skeleton}
\end{document}

### 2017-05-19 HFS/launch.py

@@ -11,10 +11,10 @@ def getFilename(rs, Nk, ndim, case):
     return fname
 
 exe = './bin/HFSrelease1D'
-Nklist = [80]
-rslist = np.logspace(0, 1.4, 10)
-caselist = ['cRHF2cRHF']
-use_delta = 'false'
+Nklist = [300, 350, 400, 450, 500]
+rslist = np.logspace(-3, 2, 10)
+caselist = ['cRHF2cUHF', 'cRHF2cRHF']
+use_deltas = ['false', 'true']
 paramlist = np.linspace(1, 10, 9)
 
 jobrank = itertools.cycle([1,2,3])
@@ -25,14 +25,15 @@ for nk in Nklist:
     for rs in rslist:
         for case in caselist:
             for param in paramlist:
-                cmd = exe + ' --Nk ' + str(nk) + ' --rs ' + str(rs) + ' --mycase ' + case
-                cmd += ' --use_delta_1D ' + use_delta + ' --twoE_parameter_1dCase ' + str(param)
-                cmd += ' --fname ' + getFilename(rs, nk, 1, case) + '.json &\n'
-                lines.append(cmd)
-                if next(jobrank) == 2:
-                    lines.append('echo ----------------Running set \#' + str(count) + ' -----------------------------\n')
-                    count += 1
-                    lines.append('wait\n')
+                for use_delta in use_deltas:
+                    cmd = exe + ' --Nk ' + str(nk) + ' --rs ' + str(rs) + ' --mycase ' + case
+                    cmd += ' --use_delta_1D ' + use_delta + ' --twoE_parameter_1dCase ' + str(param)
+                    cmd += ' --fname ' + getFilename(rs, nk, 1, case) + '.json &\n'
+                    lines.append(cmd)
+                    if next(jobrank) == 2:
+                        lines.append('echo ----------------Running set \#' + str(count) + ' -----------------------------\n')
+                        count += 1
+                        lines.append('wait\n')
 
 with open('launch.sh', 'w') as f:
     for line in lines:

### 2017-05-19 HFS/src/base_funcs.cpp

@@ -25,7 +25,7 @@ namespace HFS {
             for (uint j = 0; j < NDIM; ++j) {
                 k2(j) = HFS::kgrid(HFS::occ_states(j, k));
             }
-            exch += HFS::twoElectron(ki, k2);
+            exch += HFS::twoElectronSafe(ki, k2, k2, ki);
         }
         exch *= -1.0;
         return exch;
@@ -42,8 +42,13 @@ namespace HFS {
                 if (use_delta_1D == true) {
                     return HFS::two_e_const;
                 } else {
-                    return exp(norm * norm * HFS::two_e_const * HFS::two_e_const)
-                            * boost::math::expint(-norm * norm * HFS::two_e_const * HFS::two_e_const);
+                    scalar arg = -norm * norm * HFS::two_e_const * HFS::two_e_const;
+                    if (arg < -30.0) { // Ei(-30) = -3.02 x 10^-15, causes nan for low numbers, just do 0.
+                        return 0;
+                    } else {
+                        return exp(norm * norm * HFS::two_e_const * HFS::two_e_const)
+                                * boost::math::expint(arg);
+                    }
                 }
             # elif NDIM == 2
                 return HFS::two_e_const / norm;
@@ -78,8 +83,13 @@ namespace HFS {
                 if (use_delta_1D == true) {
                     return HFS::two_e_const;
                 } else {
-                return exp(norm * norm * HFS::two_e_const * HFS::two_e_const)
-                            * boost::math::expint(-norm * norm * HFS::two_e_const * HFS::two_e_const);
+                    scalar arg = -norm * norm * HFS::two_e_const * HFS::two_e_const;
+                    if (arg < -30.0) { // Ei(-30) = -3.02 x 10^-15, causes nan for low numbers, just do 0.
+                        return 0;
+                    } else {
+                        return exp(norm * norm * HFS::two_e_const * HFS::two_e_const)
+                                * boost::math::expint(arg);
+                    }
                 }
             # elif NDIM == 2
                 return HFS::two_e_const / norm;

### 2017-05-19 HFS/src/main.cpp

@@ -32,8 +32,8 @@ int main(int argc, char* argv[]){
     timer.tic();
 
     // Defaults
-    HFS::rs              = 1.2;
-    HFS::Nk              = 22;
+    HFS::rs              = 0.01;
+    HFS::Nk              = 20;
     HFS::mycase          = "cRHF2cUHF";
     HFS::OutputFileName  = "HFS.json";
 
@@ -60,16 +60,14 @@ int main(int argc, char* argv[]){
     parser.set_val(HFS::dav_blocksize, "--Dav_blocksize", false);
     parser.set_val(HFS::dav_num_evals, "--Dav_num_evals", false);
     parser.set_val(HFS::twoE_parameter_1dCase, "--twoE_parameter_1dCase", false);
-    //parser.set_val(HFS::use_delta_1D, "--use_delta_1D", false);
-
-    std::cout << HFS::OutputFileName << std::endl;
+    parser.set_val(HFS::use_delta_1D, "--use_delta_1D", false);
 
 
     /* Calculation starts here */
     HFS::calcParameters();
     HFS::Matrix::setMatrixPropertiesFromCase(); // RHF-UHF etc instability, matrix dimension
 
-    # if NDIM != 1
+   // # if NDIM != 1
         HFS::timeMatrixVectorProduct();
 
         SLEPc::EpS myeps(HFS::Nmat, HFS::MatVecProduct_func);
@@ -102,7 +100,10 @@ int main(int argc, char* argv[]){
         HFS::dav_nconv = myeps.nconv;
         HFS::cond_number = HFS::exc_energies(HFS::exc_energies.n_elem-1) / HFS::exc_energies(0);
         HFS::dav_min_eval = HFS::dav_vals.min();
-    #endif // NDIM != 1
+
+
+    //#endif // NDIM != 1
+    /*
     # if NDIM == 1
         arma::wall_clock eval_timer;
         eval_timer.tic();
@@ -114,6 +115,7 @@ int main(int argc, char* argv[]){
         HFS::full_diag_time = eval_timer.toc();
         HFS::exact_evals = eigvals;
     # endif // NDIM
+    */
     HFS::Total_Calculation_Time = timer.toc();
 
     // Finish up, write and test for problems.

### 2017-10-04 doc/presentations/Fall_2017/Fall2017.tex
Added presentation for Norskov lunch

--- 2017-04-10 doc/presentations/GroupMeeting_Spring2017/GroupMeeting_Fall2017.tex
@@
 
-\title{Hartree-Fock Stability}
-\subtitle{Applications to the Homogeneous Electron Gas}
+\title{Hartree-Fock Stability of the Electron Gas}
+% \subtitle{Applied to the Electron Gas}
 \date{\today}
@@
 
+\begin{comment}
   {%
@@
   \end{frame}
+\end{comment}
 
@@
 	\begin{itemize}
-		\item[]{Doing this for all cases yields} \\~\\
+		\item[]{The Matrix Equation Factorizes} \\~\\
 		\item[]{
@@
 
+{%
+\setbeamertemplate{frame footer}{Overhauser, A. W. Phys. Rev. Lett. 1960, 4 (9), 462–465.}
+\begin{frame}{Project Goal}
+	\begin{itemize}[<+->]
+		\item{Can we use the HF-Stability analysis to determine where the HEG is unstable?}
+		\item{Will this predict the known tendency of crystallization at low density?}
+		\item{It is known that the GHF solution persists at all densities for the HEG$^1$.}
+		\item{Can we show this numerically?}
+		\item{(Future) Can we combine this with to improve the efficacy of correlation theories (CC, MBPT)?}
+	\end{itemize}
+\end{frame}
+
+\section{Results}
+
+{%
+\setbeamertemplate{frame footer}{}
+
+\begin{frame}{First Brillouin Zone}
+	\begin{columns}[c] % align columns
+		\begin{column}{.4\textwidth}
+			\begin{itemize}
+				\item {Excite Ony in one direction}
+				\item {Consider only First BZ due to $\vec{k}' = \vec{k} + \vec{G}$}
+			\end{itemize}
+		\end{column}
+		\hfill
+		\begin{column}{0.6\textwidth}
+		    \begin{overprint}
+			    \onslide<1>\includegraphics[width=\linewidth]{../../images/1stBZ.eps}
+
+			\end{overprint}
+		\end{column}
+	\end{columns}
+\end{frame}
+
+{%
+\setbeamertemplate{frame footer}{}
+
+\begin{frame}{Orbital Energies}
+	\begin{columns}[c] % align columns
+		\begin{column}{.4\textwidth}
+			\begin{itemize}
+				\item {57 grid points per dimension reproduces the orbital energies reasonably well}
+				\item {Worst towards $\Gamma$, better for higher $|\vec{k}|$}
+			\end{itemize}
+		\end{column}
+		\hfill
+		\begin{column}{0.6\textwidth}
+		    \begin{overprint}
+			    \onslide<1>\includegraphics[width=\linewidth]{../../images/energycompare.eps}
+
+			\end{overprint}
+		\end{column}
+	\end{columns}
+\end{frame}
+
+\begin{comment}
+{%
+\setbeamertemplate{frame footer}{}
+
+\begin{frame}{Matrix Diagonals}
+	\begin{columns}[c] % align columns
+		\begin{column}{.4\textwidth}
+			\begin{itemize}
+				\item {Spectrum is Dense}
+			\end{itemize}
+		\end{column}
+		\hfill
+		\begin{column}{0.6\textwidth}
+		    \begin{overprint}
+			    \onslide<1>\includegraphics[width=\linewidth]{../../images/exchist.eps}
+
+			\end{overprint}
+		\end{column}
+	\end{columns}
+\end{frame}
+\end{comment}
+
+\begin{frame}{Convergence of Stability Curves}
+	\includegraphics[width=.95\linewidth]{../../images/singlet_onset.eps}
+	\\
+	\includegraphics[width=.95\linewidth]{../../images/triplet_onset.eps}
+\end{frame}
+
+{%
+\setbeamertemplate{frame footer}{Bernu, B.; Delyon, F.; Holzmann, M.; Baguet, L. Phys. Rev. B 2011, 84 (11), 115115.}
+\begin{frame}{Dependence on r${}_s$}
+	Previously reported transition in 2d: $rs \approx 0.8 $
+  \begin{center}
+  	\includegraphics[width=.6\linewidth]{../../images/Bernu_2dEnergyGain.pdf}
+	\end{center}
+\end{frame}
+
+\begin{frame}{Final Stability Curves}
+  \vspace{-0.5in}
+	\includegraphics[width=\linewidth]{../../images/stability.pdf}
+\end{frame}
+
+\section{Concluding Remarks}
+{%
+\setbeamertemplate{frame footer}{}
+\begin{frame}{Conclusions}
+  \begin{itemize}
+    \item {Numerical studies likely support Overhauser's theorem in 1D}
+    \item {Stability corresponds with direct phase calculations in 2D}
+    \item {In 3D, predicts transition at higher density than is currently known via
+    other methods.}
+  \end{itemize}
+\end{frame}
+}
+
+{%
+\setbeamertemplate{frame footer}{}
+\begin{frame}{Next Steps}
+  \begin{itemize}
+    \item {Directly calculate more exotic spin phases of HEG within HF theory}
+    \item {Use those as starting points for CC, MBPT theories}
+    \item {Apply a similar approach to finite molecular systems}
+  \end{itemize}
+\end{frame}
+}
+
+{%
+\setbeamertemplate{frame footer}{}
+\begin{frame}[standout]
+  Questions?
+\end{frame}
+
+\appendix
+
 \section{Iterative Subspace Eigenvalue Methods}
@@
 			\item{The \alert{initial guess} eigenvectors}
-			%\item{The \alert{condition number} of the eigenvector matrix}
 			\item{The \alert{preconditioner} (Davidson only)}
 		\end{itemize}
-		\item{They can \alert{converge to an eigenvalue other than the target} if:}
+		\item{They can \alert{have convergence issues} if:}
 		\begin{itemize}
@@
 
-\begin{comment}
+{%
+\setbeamertemplate{frame footer}{1) http://mathworld.wolfram.com/StrassenFormulas.html}
+
+\begin{frame}{Davidson Scaling}
+	\begin{columns}[c] % align columns
+		\begin{column}{.4\textwidth}
+			\begin{itemize}
+				\item {Davidson is Asymptotically quadratic.}
+				\item {Full diagonalization is almost cubic.}
+				\item {Matrix multiplication is order${}^1$ $log_2(7) \approx 2.807$}
+			\end{itemize}
+		\end{column}
+		\hfill
+		\begin{column}{0.6\textwidth}
+		    \begin{overprint}
+			    \onslide<1>\includegraphics[width=\linewidth]{../../images/dav_vs_exact_scaling.eps}
+
+			\end{overprint}
+		\end{column}
+	\end{columns}
+\end{frame}
+
+{%
+\setbeamertemplate{frame footer}{}
+\begin{frame}{Efficacy of Davidson's Algorithm}
+	\begin{columns}[c] % align columns
+		\begin{column}{.4\textwidth}
+			\begin{itemize}
+				\item {Reproduces Exact result to machine precision in all test cases.}
+				\item {Odd spikes are due to approximating circle by squares}
+			\end{itemize}
+		\end{column}
+		\hfill
+		\begin{column}{0.6\textwidth}
+		    \begin{overprint}
+			    \onslide<1>\includegraphics[width=\linewidth]{../../images/dav_vs_exact.eps}
+
+			\end{overprint}
+		\end{column}
+	\end{columns}
+\end{frame}
+
 {%
@@
 \end{frame}
-\end{comment}
 
-{%
-\setbeamertemplate{frame footer}{Overhauser, A. W. Phys. Rev. Lett. 1960, 4 (9), 462–465.}
-\begin{frame}{Project Goal}
-	\begin{itemize}[<+->]
-		\item{Can we use the HF-Stability analysis to determine where the HEG is unstable?}
-		\item{Will this predict the known tendency of crystallization at low density?}
-		\item{It is known that the RHF-GHF instability persists at all densities for the HEG$^1$.}
-		\item{Can we show this numerically, and discriminate between RHF-UHF and RHF-GHF instability?}
-		\item{(Future) Can we combine this with to improve the efficacy of correlation theories (CC, MBPT)?}
-	\end{itemize}
-\end{frame}
-
-\section{Results}
-
-{%
-\setbeamertemplate{frame footer}{}
-
-\begin{frame}{First Brillouin Zone}
-	\begin{columns}[c] % align columns
-		\begin{column}{.4\textwidth}
-			\begin{itemize}
-				\item {Excite Ony in the X direction}
-				\item {-X virtuals matter due to $\vec{k}' = \vec{k} + \vec{G}$}
-			\end{itemize}
-		\end{column}
-		\hfill
-		\begin{column}{0.6\textwidth}
-		    \begin{overprint}
-			    \onslide<1>\includegraphics[width=\linewidth]{../../images/1stBZ.eps}
-
-			\end{overprint}
-		\end{column}
-	\end{columns}
-\end{frame}
-
-{%
-\setbeamertemplate{frame footer}{}
-
-\begin{frame}{Orbital Energies}
-	\begin{columns}[c] % align columns
-		\begin{column}{.4\textwidth}
-			\begin{itemize}
-				\item {Nk = 57 reproduces the orbital energies reasonably well}
-				\item {Worst towards $\Gamma$, better for higher $|\vec{k}|$}
-			\end{itemize}
-		\end{column}
-		\hfill
-		\begin{column}{0.6\textwidth}
-		    \begin{overprint}
-			    \onslide<1>\includegraphics[width=\linewidth]{../../images/energycompare.eps}
-
-			\end{overprint}
-		\end{column}
-	\end{columns}
-\end{frame}
-
-{%
-\setbeamertemplate{frame footer}{}
-
-\begin{frame}{Matrix Diagonals}
-	\begin{columns}[c] % align columns
-		\begin{column}{.4\textwidth}
-			\begin{itemize}
-				\item {Spectrum is Dense}
-			\end{itemize}
-		\end{column}
-		\hfill
-		\begin{column}{0.6\textwidth}
-		    \begin{overprint}
-			    \onslide<1>\includegraphics[width=\linewidth]{../../images/exchist.eps}
-
-			\end{overprint}
-		\end{column}
-	\end{columns}
-\end{frame}
-
-\begin{comment}
-{%
-\setbeamertemplate{frame footer}{}
-
-\begin{frame}{Matrix Size Scaling}
-	\begin{columns}[c] % align columns
-		\begin{column}{.4\textwidth}
-			\begin{itemize}
-				\item {Scales as $2N_{exc}$}
-				\item {$N_{occ}$ and $N_{vir}$ both scale with $N_{kpoints}^D$}
-				\item {Use an iterative subspace method }
-				\item {Jacobi-Davidson(-Liu)}
-			\end{itemize}
-		\end{column}
-		\hfill
-		\begin{column}{0.6\textwidth}
-		    \begin{overprint}
-			    \onslide<1>\includegraphics[width=\linewidth]{../../images/matscale.eps}
-
-			\end{overprint}
-		\end{column}
-	\end{columns}
-\end{frame}
-
-\begin{frame}{Matrix-Vector Scaling}
-	\begin{columns}[c] % align columns
-		\begin{column}{.4\textwidth}
-			\begin{itemize}
-				\item {Scales as $N_{exc} \times  N_{occ}$ due to momentum conservation}
-			\end{itemize}
-		\end{column}
-		\hfill
-		\begin{column}{0.6\textwidth}
-		    \begin{overprint}
-			    \onslide<1>\includegraphics[width=\linewidth]{../../images/mvscaling.eps}
-
-			\end{overprint}
-		\end{column}
-	\end{columns}
-\end{frame}
-
-\end{comment}
-
-{%
-\setbeamertemplate{frame footer}{1) http://mathworld.wolfram.com/StrassenFormulas.html}
-
-\begin{frame}{Davidson Scaling}
-	\begin{columns}[c] % align columns
-		\begin{column}{.4\textwidth}
-			\begin{itemize}
-				\item {Davidson is Asymptotically quadratic.}
-				\item {Full diagonalization is almost cubic.}
-				\item {Matrix multiplication is order${}^1$ $log_2(7) \approx 2.807$}
-			\end{itemize}
-		\end{column}
-		\hfill
-		\begin{column}{0.6\textwidth}
-		    \begin{overprint}
-			    \onslide<1>\includegraphics[width=\linewidth]{../../images/dav_vs_exact_scaling.eps}
-
-			\end{overprint}
-		\end{column}
-	\end{columns}
-\end{frame}
-
-\begin{comment}
-\begin{frame}{Algorithm Wall time}
-	\begin{columns}[c] % align columns
-		\begin{column}{.4\textwidth}
-			\begin{itemize}
-				\item {Roughly quadratic wrt matrix dimension.}
-				\item {Outliers correspond to high condition number}
-			\end{itemize}
-		\end{column}
-		\hfill
-		\begin{column}{0.6\textwidth}
-		    \includegraphics[width=\linewidth]{../../images/overallruntime.eps}
-		\end{column}
-	\end{columns}
-\end{frame}
-\end{comment}
-
-\begin{frame}{Efficacy of Davidson's Algorithm}
-	\begin{columns}[c] % align columns
-		\begin{column}{.4\textwidth}
-			\begin{itemize}
-				\item {Reproduces Exact result to machine precision in all test cases.}
-				\item {Odd spikes are due to approximating circle by squares}
-			\end{itemize}
-		\end{column}
-		\hfill
-		\begin{column}{0.6\textwidth}
-		    \begin{overprint}
-			    \onslide<1>\includegraphics[width=\linewidth]{../../images/dav_vs_exact.eps}
-
-			\end{overprint}
-		\end{column}
-	\end{columns}
-\end{frame}
-
-{%
-\setbeamertemplate{frame footer}{Bernu, B.; Delyon, F.; Holzmann, M.; Baguet, L. Phys. Rev. B 2011, 84 (11), 115115.}
-\begin{frame}{Dependence on r${}_s$}
-	Crossover from stable to unstable in 2D agrees with previous results.
-	\includegraphics[width=.95\linewidth]{../../images/MeVsBernu.pdf}
-\end{frame}
-
-{%
-\setbeamertemplate{frame footer}{}
-\begin{frame}{Dependence on r${}_s$}
-\centering
-	3D data implies some stability at high density 
-	\includegraphics[width=.65\linewidth]{../../images/3dstab.pdf}
-\end{frame}
-
-{%
-\setbeamertemplate{frame footer}{}
-\begin{frame}{Dependence on r${}_s$}
-  \centering
-	Preliminary data for 1D shows some stability 
-	\includegraphics[width=.65\linewidth]{../../images/1dstab.pdf}
-\end{frame}
-
-{%
-\setbeamertemplate{frame footer}{}
-\begin{frame}[standout]
-  Questions?
-\end{frame}
-
-\begin{comment}
-\section{Concluding Remarks}
-{%
-\setbeamertemplate{frame footer}{}
-\begin{frame}{Next Steps}
-	\resizebox{\textwidth}{!}{%
-	\begin{tabular}{l c c}
-		Objective                 & Human Time   & Computer Time    \\
-		\midrule
-		Other instabilities in 2D & 30 mins & Week \\
-		All 3D & $\frac{1}{2}$ Day&  $>$Weeks? Parallel?
-	\end{tabular}}
-\end{frame}
-}
-\end{comment}
-
-\appendix
-
-%{%
-%\setbeamertemplate{frame footer}{}
-%\begin{frame}[fragile]{Backup slide}
-%	Empty Backup
-%\end{frame}
-%
 \end{document}

### 2017-10-04 analysis/log/smallruns.sh

@@ -1,0 +1,22 @@
+mpirun -n 3 ../../HFS/bin/release/3d/HFS --Nk 8 --fname HFS_3d_8Nk_1-0rs.json --rs 1.0 --Dav_maxits 11 &
+wait
+mpirun -n 3 ../../HFS/bin/release/3d/HFS --Nk 8 --fname HFS_3d_8Nk_1-5rs.json --rs 1.5 --Dav_maxits 11 &
+wait
+mpirun -n 3 ../../HFS/bin/release/3d/HFS --Nk 8 --fname HFS_3d_8Nk_2-0rs.json --rs 2.0 --Dav_maxits 11 &
+wait
+mpirun -n 3 ../../HFS/bin/release/3d/HFS --Nk 8 --fname HFS_3d_8Nk_2-5rs.json --rs 2.5 --Dav_maxits 11 &
+wait
+mpirun -n 3 ../../HFS/bin/release/3d/HFS --Nk 8 --fname HFS_3d_8Nk_3-0rs.json --rs 3.0 --Dav_maxits 11 &
+wait
+mpirun -n 3 ../../HFS/bin/release/3d/HFS --Nk 8 --fname HFS_3d_8Nk_3-5rs.json --rs 3.5 --Dav_maxits 11 &
+wait
+mpirun -n 3 ../../HFS/bin/release/3d/HFS --Nk 8 --fname HFS_3d_8Nk_4-0rs.json --rs 4.0 --Dav_maxits 11 &
+wait
+mpirun -n 3 ../../HFS/bin/release/3d/HFS --Nk 8 --fname HFS_3d_8Nk_4-5rs.json --rs 4.5 --Dav_maxits 11 &
+wait
+mpirun -n 3 ../../HFS/bin/release/3d/HFS --Nk 8 --fname HFS_3d_8Nk_5-0rs.json --rs 5.0 --Dav_maxits 11 &
+wait
+mpirun -n 3 ../../HFS/bin/release/3d/HFS --Nk 8 --fname HFS_3d_8Nk_5-5rs.json --rs 5.5 --Dav_maxits 11 &
+wait
+mpirun -n 3 ../../HFS/bin/release/3d/HFS --Nk 8 --fname HFS_3d_8Nk_6-0rs.json --rs 6.0 --Dav_maxits 11 &
+wait

### 2017-10-10 doc/papers/summary/HFStability-summary.tex
Added some more to intro and methods of summary

@@
 \documentclass{revtex4}
-%\usepackage{amsmath}
-%\usepackage{amssymb}
-%\usepackage{graphicx}
+\usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{braket}
+\usepackage{mathtools}
+\usepackage{textcomp}
+\usepackage{algorithm}
+\usepackage{booktabs}
 
 \begin{document}
-\title{Summary Hartree-Fock Stability of HEG}
+\title{Summary of Hartree-Fock Stability of HEG}
 \author{Evan Curtin}
@@
 In the past few years, phase diagrams have been determined for the HEG in 2 and 3 dimensions\cite{Delyon2008}\cite{Bernu2011}\cite{Baguet2013}.
-In all cases (to my knowledge) the phase diagrams are made by computing the energies of the polarized and unpolarized states, and comparing them.
+In all cases the phase diagrams are made by computing the energies of the polarized and unpolarized states, and comparing them.
+The present work focuses on directly calculating the stability of the paramagnetic homogeneous electron gas as a function of electron density.
+It should be emphasized that instability of the Hartree-Fock solution is a sufficient, but not necessary, condition for the presence of a symmetry-broken Hartree-Fock solution of lower energy to exist.
+The technique may be used to guide a search for the lowest energy Hartree-Fock solution by following the instability eigenvectors downhill in energy.
+Such an approach will be attempted in a future paper.
+
+\section{Methods}    
+    The Fermi level, $k_f$, is (p. 30 of \cite{Guiliani2005})
+
+    \begin{equation}
+    k_f
+    =\begin{cases} 
+    (3\pi^2n)^{\frac{1}{3}} = \left(\frac{9\pi}{4}\right)^{\frac{1}{3}}\frac{1}{r_sa_0} & 3D \\ \\
+    (2\pi n)^{\frac{1}{2}} = \frac{\sqrt{2}}{r_sa_0}  & 2D \\
+    \\
+    \frac{\pi}{2}n = \frac{\pi}{4 r_s a_0}   & 1D 
+    \end{cases}
+    .
+    \end{equation}
+
+    The two electron integral is given by (eq. 12 of \cite{Delyon2008} and p. 16 of \cite{Guiliani2005})
+
+    \begin{subequations}
+    	\begin{align}
+    	\braket{\vec{k}, \vec{k}'|\vec{k}'',\vec{k}'''}\stackrel{\text{2D, 3D}}{=}&
+    	\begin{cases} 
+    	\frac{\pi}{\Omega}\frac{2^{D-1}}{|\vec{k}-\vec{k}''|^{D-1}} 
+    	& \vec{k}''' = \vec{k}+\vec{k}'-\vec{k}'' \textbf{ and } |\vec{k}-\vec{k}''| \neq 0 \\
+    	0 
+    	& \text{else}
+    	\end{cases}
+    	\\ \nonumber \\
+    	\braket{k, k'|k'',k'''}\stackrel{\text{1D}}{=}&
+    	\begin{cases} 
+    	e^{|k-k''|^2a^2}\text{Ei}(-|k-k''|^2a^2)\text{ ;}
+    	& k''' = k+k'-k'' \textbf{ and } |k-k''| \neq 0 \\
+    	0\text{ ;} 
+    	& \text{else}
+    	\end{cases}
+    	\end{align}
+    \end{subequations}
+    where $\Omega$ is the direct lattice volume and D is the dimensionality of the system. Ei(x) 
+    denotes the exponential integral function The parameter $a$ in 1D is the radius of a cylinder
+    that approximates a 1D system. The limit $a \rightarrow 0$ diverges. The orbital energies are given 
+    by
+
+    \begin{equation}\label{eq:hf_orb_energy}
+    \epsilon_{\vec{k},\sigma}=
+    \frac{\hbar^2\vec{k}^2}{2m} - \sum\limits_{\vec{k}}^{|\vec{k}|< k_f}n_{\vec{k}\sigma}\braket{\vec{k}, \vec{k}' |\vec{k}', \vec{k}}
+    \end{equation}
+
+    Where $n_{\vec{k}\sigma}$ is the occupation number of the state with momentum $\vec{k}$ and spin $\sigma$.
+Here we have used the relationship to relate the discrete and continuous quantities, (p.
+15 of \cite{Guiliani2005}).
+
+    \subsection{Hartree-Fock Stability}
+    The HF stability condition was presented by Thouless \cite{Thouless1972} ($1^{st}$ Ed.
+1960) and is the presence of imaginary electronic oscillation frequencies in the random phase approximation (RPA).
+Equivalently, instability of a Hartree-Fock solution is borne out as a negative eigenvalue of the electronic Hessian (density-matrix--density-matrix response function).
+For a paramagnetic HF solution, the equations factorize into the matrices known to chemists as the singlet and triplet instability matrices \cite{Dunning1967}\cite{Seeger1977},
+    \begin{equation}\label{eq:1,3H}
+    {}^{1,3}\bf{H'}=
+    \begin{bmatrix}
+    {}^{1,3}\bf{A'} & {}^{1,3}\bf{B'} \\
+    \left({}^{1,3}\bf{B'}\right)^* & \left({}^{1,3}\bf{A'}\right)^* \\
+    \end{bmatrix},
+    \end{equation}
+    where the $1,3$ denote singlet and triplet states, respectively. $\bf{A}$, $\bf{B}$ have dimension $N_{occ}\times N_{vir}$ and are defined as follows:
+    \begin{subequations}
+    	\begin{align}
+    	{}^{1}{A'}_{i\rightarrow a, j\rightarrow b} &= (\epsilon_a-\epsilon_i)\delta_{ij}\delta_{ab} + 2\braket{aj|ib}-\braket{aj|bi}\\
+    	{}^{3}{A'}_{i\rightarrow a, j\rightarrow b} &= (\epsilon_a-\epsilon_i)\delta_{ij}\delta_{ab} - \braket{aj|bi}\\
+    	{}^{1}{B'}_{i\rightarrow a, j\rightarrow b} &= 2\braket{ab|ij}-\braket{ab|ji}\\
+    	{}^{3}{B'}_{i\rightarrow a, j\rightarrow b} &= -\braket{ab|ji}
+    	\end{align}
+    \end{subequations}
+    The matrix given in Equation \ref{eq:1,3H} represents the case of complex RHF stability in the space of complex RHF space (${}^{1}\mathbf{H}$ - internal instability) and in the space of complex UHF space (${}^{3}\mathbf{H}$ - triplet instability).
 

### 2017-10-17 doc/papers/summary/HFStability-summary.tex
Added more for summary

@@
 \usepackage{booktabs}
+\usepackage{color}
 
@@
 \section{Methods}
-    The Fermi level, $k_f$, is (p. 30 of \cite{Guiliani2005})
 
-    \begin{equation}
-    k_f
-    =\begin{cases} 
-    (3\pi^2n)^{\frac{1}{3}} = \left(\frac{9\pi}{4}\right)^{\frac{1}{3}}\frac{1}{r_sa_0} & 3D \\ \\
-    (2\pi n)^{\frac{1}{2}} = \frac{\sqrt{2}}{r_sa_0}  & 2D \\
-    \\
-    \frac{\pi}{2}n = \frac{\pi}{4 r_s a_0}   & 1D 
-    \end{cases}
-    .
+	Starting with the Jellium Hamiltonian, 
+	\begin{equation}\label{hamiltonian}
+		\mathbf{H} = ....
 	\end{equation}
 
-    The two electron integral is given by (eq. 12 of \cite{Delyon2008} and p. 16 of \cite{Guiliani2005})
+	Solutions to the Hartree-Fock equations in $D$ dimensions are plane waves of the form, 
+	\begin{equation}\label{planewave}
+		\phi_{\vec{k} \sigma} =
+		   \frac{1} { \sqrt{L ^ D} } e ^ {i \vec{k} \dot \vec{x}}.
+	\end{equation}
+	Choosing a plane wave basis with periodic boundary conditions is therefore natural, and results in the two electron repulsion integrals being analytic with the following forms, (eq.
+12 of \cite{Delyon2008} and p.
+16 of \cite{Guiliani2005})
 
@@
     	\begin{align}
-    	\braket{\vec{k}, \vec{k}'|\vec{k}'',\vec{k}'''}\stackrel{\text{2D, 3D}}{=}&
+    	\braket{\vec{k}, \vec{k}' | \vec{k}'', \vec{k}'''} 
+    	  \stackrel{ \text{2D, 3D} }{=}&
     	\begin{cases} 
-    	\frac{\pi}{\Omega}\frac{2^{D-1}}{|\vec{k}-\vec{k}''|^{D-1}} 
-    	& \vec{k}''' = \vec{k}+\vec{k}'-\vec{k}'' \textbf{ and } |\vec{k}-\vec{k}''| \neq 0 \\
+    	\frac{\pi} {\Omega} \frac{ 2^{D-1} } { | \vec{k} - \vec{k}'' | ^ {D-1} } 
+    	& \vec{k}''' = \vec{k} + \vec{k}' - \vec{k}'' + \vec{G} \textbf{ and } | \vec{k} - \vec{k}''| \neq 0 \\
     	0 
@@
     	\\ \nonumber \\
-    	\braket{k, k'|k'',k'''}\stackrel{\text{1D}}{=}&
+    	\braket{k, k' | k'', k'''} \stackrel{\text{1D}}{=}&
     	\begin{cases} 
-    	e^{|k-k''|^2a^2}\text{Ei}(-|k-k''|^2a^2)\text{ ;}
-    	& k''' = k+k'-k'' \textbf{ and } |k-k''| \neq 0 \\
+    	e ^ { |k-k''|^2a^2 } \text{Ei} (-|k - k''|^2 a^2)\text{ ;}
+    	& k''' = k + k' - k'' + \vec{G} \textbf{ and } |k - k''| \neq 0 \\
     	0\text{ ;} 
@@
     \end{subequations}
-    where $\Omega$ is the direct lattice volume and D is the dimensionality of the system. Ei(x) 
-    denotes the exponential integral function The parameter $a$ in 1D is the radius of a cylinder
-    that approximates a 1D system. The limit $a \rightarrow 0$ diverges. The orbital energies are given 
+    where $\Omega$ is the direct lattice volume and $\vec{G}$ is a reciprocal lattice vector of the system.
+Ei(x) denotes the exponential integral function and the parameter $a$ in 1D is the radius of a cylinder that approximates a 1D system to circumvent divergence of the integral in 1 dimension.
+The orbital energies are given
     by
@@
 
-    Where $n_{\vec{k}\sigma}$ is the occupation number of the state with momentum $\vec{k}$ and spin $\sigma$.
-Here we have used the relationship to relate the discrete and continuous quantities, (p.
-15 of \cite{Guiliani2005}).
+    Where $n_{\vec{k}\sigma}$ is the occupation number of the state with momentum $\vec{k}$ and spin $\sigma$ (p. 15 of \cite{Guiliani2005}).
 
@@
 1960) and is the presence of imaginary electronic oscillation frequencies in the random phase approximation (RPA).
-Equivalently, instability of a Hartree-Fock solution is borne out as a negative eigenvalue of the electronic Hessian (density-matrix--density-matrix response function).
-For a paramagnetic HF solution, the equations factorize into the matrices known to chemists as the singlet and triplet instability matrices \cite{Dunning1967}\cite{Seeger1977},
+Equivalently, instability of a Hartree-Fock solution is borne out as a negative eigenvalue of the electronic Hessian (static density-matrix--density-matrix response function).
+For a paramagnetic HF solution, the equations factorize into the matrices known to chemists as the singlet and triplet instability matrices \cite{Dunning1967}\cite{Seeger1977} \textcolor{red}{show this here?
+appendix?}
+    ,
     \begin{equation}\label{eq:1,3H}
@@
     \end{equation}
-    where the $1,3$ denote singlet and triplet states, respectively. $\bf{A}$, $\bf{B}$ have dimension $N_{occ}\times N_{vir}$ and are defined as follows:
+    where the $1,3$ denote singlet and triplet instabilities, respectively. $\bf{A}$, $\bf{B}$ have dimension $N_{occ}\times N_{vir}$ and are defined as follows:
     \begin{subequations}
@@
     The matrix given in Equation \ref{eq:1,3H} represents the case of complex RHF stability in the space of complex RHF space (${}^{1}\mathbf{H}$ - internal instability) and in the space of complex UHF space (${}^{3}\mathbf{H}$ - triplet instability).
+The lowest eigenvalue of both of these matrices will reveal the stability of the RHF solution.
+If they are both positive, the solution is stable with respect to symmetry breaking, while negative eigenvalues in either indicate instability with respect to either triplet or singlet perturbations (or both).
+We mention here that an eigenvalue of 0 does not indicate instability, and this case is discussed in detail by Cui et al \cite{Cui2013}.
 

### 2018-01-25 doc/papers/paper_skeleton/paper_skeleton.tex
Updated gitignore for latex files. Reformatted paper skelly

@@
-\documentclass{revtex4}
+\documentclass[preprint, journal=prl]{revtex4-1}
 \usepackage{graphicx}
 \usepackage{amsmath}
-\usepackage{amssymb}
 \usepackage{braket}
-
-\newcommand{\ki}{\mathbf{k}_{i}}
-\newcommand{\kj}{\mathbf{k}_{j}}
-\newcommand{\ka}{\mathbf{k}_{a}}
-\newcommand{\kb}{\mathbf{k}_{b}}
-\newcommand{\kp}{\mathbf{k}_{p}}
-\newcommand{\kq}{\mathbf{k}_{q}}
-\newcommand{\kr}{\mathbf{k}_{r}}
-\newcommand{\ks}{\mathbf{k}_{s}}
-
-\makeatletter
-\makeatother
+\usepackage{float}
+\usepackage{caption}
+\usepackage{color}
 
 \begin{document}
-\title{Hartree-Fock Stability Analysis of the Paramagnetic Homogeneous Electron Gas in
-1, 2 and 3 Dimensions.}
-\author{Evan Curtin, So Hirata}
+\title{Numerical Determination of the Hartree-Fock Stability of the Paramagnetic Electron Gas in 1, 2 and 3 Dimensions}
+\author{Evan Curtin}
+\author{So Hirata}
+\email{Sohirata@illinois.edu}
+\affiliation{Department of Chemistry, University of Illinois at Urbana-Champaign, 600 South Mathews Avenue, Urbana, Illinois 61801, USA}
+
+\begin{abstract}
+
+\end{abstract}
+
 \maketitle
 
-\section{Abstract}
+\section{Introduction}
+  The goal of electronic structure theory is to solve the electronic Schr{\"o}dinger equation  for a molecule or solid state system.
+The prevailing approach in \emph{ab initio} quantum  chemistry is to first compute a self-consistent single-determinant Hartree-Fock (HF) solution which will serve as a reference for many-body perturbative (MP) or coupled-cluster (CC) approaches.
+Implicit in these methods is the assumption that the reference wave function will be sufficiently close to the exact solution of the Schr{\"o}dinger equation to converge to the correct answer in a computationally feasible manner.
+Both the MP and CC approaches have the attractive quality that they are systematically improvable, i.e.
+increasing the accuracy of the resulting solution can be done by using a higher order of the theory.
+These so-called post-Hartree-Fock methods are able to recover more of the total electronic energy by accounting for the \emph{correlation energy} in the system.
+Traditionally, the correlation energy is defined by the difference between the exact energy and the Hartree-Fock energy \cite{Shavitt2009}
+  \begin{equation}\label{eq:correlation_energy}
+    E_{corr} = E_{exact} -  E_{HF}.
+  \end{equation}
+  In many cases the correlation energy is relatively small and the Hartree-Fock reference captures a significant portion of the exact total energy.
+In such cases, the prevailing approach is usually successful and has only implementation issues for larger systems.
+On the other hand there are systems which are not well treated by this approach, which are often called ``strongly correlated''.
+Examples of such systems are those with degenerate or near-degenerate HOMO-LUMO gaps, metallic solids or molecules close to breaking bonds.
+Oftentimes for such systems the traditional Hartree-Fock solutions are not even qualitatively correct, implying inadequacies in either the single-reference or mean-field approach.
 
-\section{Introduction}
+  It is often neglected, however, that the usual way for computing a Hartree-Fock solution in practice is to use a restricted form of the single determinantal wavefunction.
+In the Restricted  Hartree-Fock (RHF), the wave function is restricted to be an eigenfunction of the $\hat{S^2}$ and $\hat{S_z}$ operators, while in the Unrestricted variant (UHF), the wave function need only be an eigenfunction of the $\hat{S_z}$.
+There is yet another lesser-known variation of the theory, known as General Hartree-Fock (GHF), which assumes no spin-symmetries in the wave function.
+This allows for greater variational flexibility at the cost of ``broken symmetry''.
+Together these three levels of Hartree-Fock theory form a heirarchy of increasing parameter space within which to minimize the total energy.
 
-\section{Methods}
-We consider the paramagnetic state of the Homogeneous Electron Gas (HEG) in a $D$-dimensional
-box of length $L$. All states below the fermi wave vector, $k_f$ are doubly occupied, and all
-above are virtual. According to Guiliani and Vignale\cite{Guiliani2005}, $k_f$ is given by equation 
-\ref{kf} for 1, 2 and 3 dimensions.
+  Previously it has been shown for finite systems with form-degenerate HOMO-LUMO, there always exists a symmetry-breaking instability\cite{Yamada2015}.
+Whether this theorem holds in the infinite case remains to be seen.
+To investigate HF instabilities in zero band gap solids, a natural starting point is the Homogeneous Electron Gas (HEG, often called Jellium or Uniform Electron Gas) model.
+The model consists of electrons in a box with periodic boundary conditions  and the constraint that the entire system is charge-neutral via a uniform background positive  charge.
+The resulting Coulomb interactions cancel exactly, and the only remaining terms are due   to kinetic and exchange energies.
+Historically it was thought that the plane-wave paramagnetic solution to the HF equations for this model was the ``correct'' solution.
+However, in a landmark paper, Overhauser showed that certain symmetry broken solutions \emph{always} have lower-energy than the paramagnetic solutions at all electron densities\cite{Overhauser1962}.
+This hints at, but does not show, that the analogous triplet instability theorem persists in the infinite case.
 
-\begin{eqnarray} \label{kf}
-k_f
-=\begin{cases} 
-  (3\pi^2n)^{\frac{1}{3}} = \left(\frac{9\pi}{4}\right)^{\frac{1}{3}}\frac{1}{r_sa_0} & 3D \\ \\
-  (2\pi n)^{\frac{1}{2}} = \frac{\sqrt{2}}{r_sa_0}  & 2D \\
-  \\
-  \frac{\pi}{2}n = \frac{\pi}{4 r_s a_0}   & 1D 
- \end{cases} 
-\end{eqnarray}
+  Overhausers' paper sparked new interest in the HEG, and since then Energies of various phases thereof have been computed to great accuracy\cite{Ceperley1980}.
+More recently, phase diagrams have been determined for the HEG in 2 and 3 dimensions\cite{Delyon2008, Bernu2011, Baguet2013}.
+In all cases the phase diagrams are made by computing the energies of the polarized and unpolarized states, and comparing them.
+This approach necessitates that the form of the solutions is known ahead of time.
 
-The Hartree-Fock Hamiltonian  is defined in the usual way for the HEG in that the positive
-background charge exactly cancels the electron-electron coulomb interaction. One solution of the 
-Hartree-Fock equation is a set of plane waves,
+  The present work focuses on directly calculating the Hartree-Fock stability of the paramagnetic homogeneous electron gas as a function of electron density.
+The motivation is two-fold.
+First, the numerical studies of this model can give computational evidence for or against the ubiquity of symmetry-breaking HF instabilities in metallic solids.
+Secondly, the instabilities can help in determining lower energy HF solutions of the HEG.
+This is because the study will reveal where the symmetry broken Hartree-Fock reference is needed.
+To date, an optimal form (i.e.
+minimal energy in the HF manifold) of the Hartree-Fock solution to the HEG remains unknown, even though exact energy (including correlation) is essentially known.
+Therefore determining a lower energy HF solution can yield insight into the effects of correlation of this fundamental physical model.
 
-\begin{eqnarray} \label {planewave}
-  \phi_k(\vec{r}) = \frac{ e^ {i \bf{k} \cdot \bf{r}}} {\sqrt{D^N}},  
-\end{eqnarray}
+ % Thus the term ``Hartree-Fock Energy'' is inherently ambigious; this fact calling into question commonly held ideas about correlation and Hartree-Fock theory.
+Take for example the dissociation curve of H$_2$ in the RHF and UHF approximations, compared with the exact solution obtained by full configuration-interaction in the complete basis set limit.
+ % \begin{figure}[H]
+ %   \centering
+ %   \includegraphics[width=0.75\textwidth]{../../images/H2_curves.eps}
+ %   \caption{Dissociation curve of H$_2$ in the RHF and UHF approximations, compared to the exact limit (FCI).
+The difference in correlation energies as determined by each reference illustrates the ambiguity of that quantity.
+In the dissociation limit, the UHF correlation energy vanishes while the RHF correlation energy increases in magnitude.}
+ %   \label{h2diss}
+ % \end{figure}
+ % The correlation energy for the RHF reference case is dramatically larger than that for the UHF reference.
+In other words, \emph{the correlation energy is, by definition, inherently coupled to the Hartree-Fock reference}.
+The given example is well understood, but it brings to mind a more general idea that there may be more cases where apparently large correlation energies are due to simply using and inadequate level of Hartree-Fock theory.
+Scuseria and coworkers have leveraged this idea to create new coupled cluster theories while preserving the symmetry of the reference  \cite{Gomez2016}.
 
-defined with periodic boundary conditions\cite{Phillips2012}. Do determine the stability of these
-RHF solutions, we use the method introduced by Thouless \cite{Thouless1960}, and further 
-chatagerized by Seeger and Pople \cite{Seeger1977}. The solutions of the Hartree-Fock equations are 
-unstable when the Molecular Orbital Hessian,
+  %Another approach to this problem is to allow breaking of symmetry, and to take the variational principle at face value; lower energy is always better.
+For predicting certain observables this is not the case, but for energies alone we are free to maintain this mindset.
+If the HF solution is allowed to relax fully in its most general form, the resulting correlation energy may be reduced dramatically.
+Therefore the overarching theme of the proposed work is that \emph{many examples of strong correlation may be misleading, and in order to find out we have to find lower  energy Hartree-Fock solutions, even at the cost of broken symmetry}.
 
-\begin{eqnarray} \label{H}
-  \bf{H} = 
+  %If it turns out that fully minimizing the HF energy can reproduce a majority of the ``correlation energy'' in these systems, then using this HF searching method becomes a justified method of solving strongly correlated systems.
+This would mean that the strong correlation was in fact illusory, and is convertible to a weak correlation problem by means of a more rigorous Hartree-Fock theory.
+
+\section{Method}
+  Hartree-Fock (HF) Theory has been the foundation for \emph{ab initio} electronic structure theory  throughout its history.
+An often overlooked aspect of the theory is that there are many solutions to the HF equations for a given system, but being a solution to the Hartree-Fock equation ensures only that the solution is stationary with respect to the determined orbitals.
+If the solution is indeed a minimum, it is called ``stable'', while if there is any displacement in the electronic structure which lowers the energy, the solution is ``unstable''.
+A method for determining the stability of a Hartree-Fock solution was proposed by Thouless in 1960\cite{Thouless1960}.
+The condition was rederived into the expression familiar to quantum chemists by Čížek and Paldus in 1967\cite{Cizek1967}.
+Furthermore, the stability equations factorize depending on the symmetry of the Hartree-Fock eigenfunctions.
+To this end, Seeger and Pople outlined a hierarchical approach to systematically evaluate the stability of HF states in the restricted, unrestricted and generalized Hartree-Fock procedures\cite{Seeger1977}.
+Recently, the method has been used to aid the search for the lowest-energy Unrestricted Hartree-Fock (UHF) solutions in molecules, as well as the General Hartree-Fock (GHF) solutions in geometrically frustrated hydrogen rings which cannot conform even to the UHF scheme\cite{Pulay2016, Goings2015}.
+The lower energy HF solutions in these studies were located by first finding the instabilities in the higher spin-symmetry solutions, then using this information to obtain ``symmetry breaking'' displacements that lower the energy.
+
+  To determine if there is indeed a symmetry-broken HF solution of lower energy, the usual method  is to determine the stability of a found Hartree-Fock solution.
+Instabilities are indicated by a negative eigenvalue the Electronic Hessian,
+  \begin{equation}
+    \bf{H}=
     \begin{bmatrix}
-    \bf{A}   & \bf{B} \\
-    \bf{B^*} & \bf{A^*}\\
+      \bf{A} &\bf{B} \\
+      \bf{B}^* & \bf{A}^* \\
     \end{bmatrix},
-\end{eqnarray}
-
-has any strictly negative eigenvalues. An unstable HF solution is one that is a stationary solution
-to the HF equations, but has a negative second-order variation in the energy with respect to 
-electronic oscillations. Thus, a solution being
-unstable is a sufficient condition for another solution of lower energy existing.
-
-The square matrices $\bf{A}$ and $\bf{B}$ are defined in 
-terms of the excitations of the system, and thus have the size of the number of possible 
-excitations. Their elements are
-
-\begin{eqnarray} \label{A_B}
-	A_{\ki\rightarrow \ka, \kj\rightarrow \kb} &=& 
-	(\epsilon_{\ka} - \epsilon_{\ki})\delta_{\ki\kj}\delta_{\ka\kb} + \braket{\ka\kj||\ki\kb}\\
-	B_{\ki\rightarrow \ka, \kj\rightarrow \kb} &=& \braket{\ka\kb||\ki\kj},  \nonumber
-\end{eqnarray}
-
-where $\epsilon_{\ki}$ is the $i$'th eigenvalue of the one-electron Fock operator. 
-The convention for the two electron integrals is,
-
-\begin{eqnarray} \label{TwoElectron}
-  \braket{\kp\kq|\kr\ks}  &=& \int\int \phi_{\kp}^*(\mathbf{x}_1) \phi_{\kq}^*(\mathbf{x}_2) 
-                              \frac{1}{r_{12}} 
-                              \phi_{\kr}(\mathbf{x}_1) \phi_{\ks}(\mathbf{x}_2) 
-                              \mathrm{d}\mathbf{x}_1  \mathrm{d}\mathbf{x}_2, \\
-  \braket{\kp\kq||\kr\ks} &=& \braket{\kp\kq|\kr\ks} - \braket{\kp\kq|\ks\kr}                  
-\end{eqnarray}
-
-and the integration is over both Cartesian and spin coordinates. The analytic form of the two 
-electron integral for the case of the HEG is given by
-
+  \end{equation} 
+  where the matrices $\mathbf{A}$ and $\mathbf{B}$ have dimension $N_{occupied} \times N_{virtual}$ with elements given by
+  \begin{align}
+     A_{i \rightarrow a, j \rightarrow b} &= (\epsilon_a-\epsilon_i)\delta_{ij}\delta_{ab} 
+     + \left< aj||ib \right>, \\
+     B_{i \rightarrow a, j \rightarrow b} &= \left< ab||ij \right>. 
+  \end{align}    
+  For a paramagnetic HF solution (RHF), the Orbital Hessian factorizes into the matrices known to chemists as the singlet and triplet instability matrices ($\bf{{}^1H}$ and $\bf{{}^3H}$, respectively)\cite{Dunning1967,Seeger1977}.
   \begin{subequations}
-  \begin{eqnarray} \label{TwoElectronAnalytic}
-    \braket{\kp\kq||\kr\ks}\stackrel{\text{2D, 3D}}{=}
-    	\begin{cases} 
-      	\frac{\pi}{\Omega} \frac{2^{D-1}}{ |\kp - \kr|^{D-1} } 
-      	& \ks + \kr = \kp + \kq  \mathrm{~and~} | \kp - \kr | \neq 0 \\
-      	0 
-      	& \text{else}
-    	\end{cases}
-    \\ \nonumber \\
-    \braket{\kp\kq||\kr\ks}\stackrel{\text{1D}}{=}
-    	\begin{cases} 
-      	e^{ |\kp - \kr|^2a^2 }  \text{Ei} (-|\kp - \kr|^2a^2)
-      	& \ks + \kr = \kp + \kq \mathrm{~and~} | \kp - \kr | \neq 0 \\
-      	0 
-      	& \text{else}
-    	\end{cases},
+    \begin{eqnarray}
+      {}^{1}{A'}_{i\rightarrow a, j\rightarrow b} &=& 
+      (\epsilon_a-\epsilon_i)\delta_{ij}\delta_{ab} 
+      + 2\braket{aj|ib}-\braket{aj|bi}\\
+      {}^{3}{A'}_{i\rightarrow a, j\rightarrow b} &=& 
+      (\epsilon_a-\epsilon_i)\delta_{ij}\delta_{ab} 
+      - \braket{aj|bi}\\
+      {}^{1}{B'}_{i\rightarrow a, j\rightarrow b} &=& 2\braket{ab|ij}-\braket{ab|ji}\\
+      {}^{3}{B'}_{i\rightarrow a, j\rightarrow b} &=& -\braket{ab|ji}
     \end{eqnarray}
   \end{subequations}
+  The lowest eigenvalue of both of these matrices will reveal the stability of the RHF solution.
+If  ${}^1\bf{H}$ has negative eigenvalues, the solution is unstable with respect to changes that preserve singlet character (singlet instability), while if ${}^3\bf{H}$ has negative eigenvalues, the solution is unstable towards displacements that would change the wavefunction towards a triplet state (triplet instability).
+The solution is stable if neither ${}^1\bf{H}$ nor ${}^3\bf{H}$ has a negative eigenvalue.
+An eigenvalue of 0 does not indicate instability, and this case is discussed in detail by Cui et al \cite{Cui2013}.
 
-where $\Omega$ is the direct lattice volume. \cite{Delyon2008} \cite{Guiliani2005}. Ei(x) 
-denotes the exponential integral function and the parameter $a$ in 1D is the radius of a cylinder
-that approximates a 1D system (For more details we refer the reader to reference 
-\cite{Guiliani2005}). The eigenenergies of the one particle Fock operator can be determined by
-evaluating
+\subsection{Method}
+  Starting with the Jellium Hamiltonian in atomic units, 
+  \begin{equation}\label{hamiltonian}
+   	\hat{H} = \sum_i \frac{\hat{p}_i^2}{2}  + \frac{1}{2} \sum_{i < j} \frac{1}{|\vec{r}_i - 
+   	\vec{r}_j|},
+  \end{equation}
+  one solution to the Hartree-Fock equations in $D$ dimensions are plane waves of the form	
+  \begin{equation}\label{planewave}
+   	\phi_{\vec{k}} =
+    \frac{1} { \sqrt{L ^ D} } e ^ {i \vec{k} \dot \vec{x}},
+  \end{equation}
+  where $L$ is the length of one side of the direct lattice with cubic symmetry.
+Using this as the basis for the rest of the analysis, the two electron repulsion integrals are analytic and  well-behaved in two and three dimensions\cite{Delyon2008, Guiliani2005}
+  \begin{align}
+    \braket{\vec{k}, \vec{k}' | \vec{k}'', \vec{k}'''} 
+    \stackrel{ \text{2D, 3D} }{=}&
+    \begin{cases} 
+      \frac{\pi} {L ^ D} \frac{ 2^{D-1} } { | \vec{k} - \vec{k}'' | ^ {D-1} } 
+      & \vec{k}''' = \vec{k} + \vec{k}' - \vec{k}'' + n\vec{G} \textbf{ and } | \vec{k} - 
+      \vec{k}''| \neq 0 \\
+      0 
+      & \text{else},
+    \end{cases}
+  \end{align}
+  where $n\vec{G}$ is any integer times a reciprocal lattice vector of the system. The orbital energies are
+  \begin{equation}\label{eq:hf_orb_energy}
+    \epsilon_{\vec{k},\sigma}=
+    \frac{\hbar^2\vec{k}^2}{2m} - \sum\limits_{\vec{k}}^{|\vec{k}|< 
+    k_f}n_{\vec{k}\sigma}\braket{\vec{k}, \vec{k}' |\vec{k}', \vec{k}},
+  \end{equation}
+  where $n_{\vec{k}\sigma}$ is the occupation number of the state with momentum $\vec{k}$ and spin $\sigma$ \cite{Guiliani2005}.
+In one dimension, the two electron integral diverges, and it is common to use a delta function interaction,
+  \begin{equation}
+    V(r_{12}) = V_0\delta(r_{12}),
+  \end{equation}
+  and the two electron integral in this case is simply
+  \begin{align}
+    \braket{\vec{k}, \vec{k}' | \vec{k}'', \vec{k}'''} 
+    \stackrel{ \text{1D} }{=}&
+    \begin{cases} 
+      V_0 
+      & \vec{k}''' = \vec{k} + \vec{k}' - \vec{k}'' + n\vec{G}\\
+      0 
+      & \text{else}.
+    \end{cases}
+  \end{align}
 
-\begin{equation} \label{eq:hf_orb_energy}
-  \epsilon_{\kp}=
-  	\frac{\hbar^2|\kp|^2}{2m} - \sum\limits_{\ki}^{occ}
-    n_{\ki} \braket{\kp, \ki | \ki, \kp}
+\subsection{Results}   
+  Using the equations for energies and two electron integrals, the stability analysis was performed on the paramagnetic HEG model as a function of electron density (or equivalently, the Wigner-Seitz radius, $r_s$).
+The approach of explicitly constructing and diagonalizing the orbital hessian is intractable both in terms of memory and calculation time requirements.
+Since the instability condition is that the any eigenvalue is negative, it suffices to calculate the sign of only the lowest eigenvalue.
+This is a task well suited for an iterative subspace solver.
+To this end, the Jacobi-Davidson algorithm was from the SLEPc library was used to calculated the lowest eigenvalues\cite{Hernandez2005}.
+
+  \begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{../../images/singlet-stability-convergence.pdf}
+    \caption{The lowest eigenvalue of ${}^1\mathbf{H}$ as a function of $r_s$ with increasing number of k-points in 1, 2 and 3 dimensions.}
+    \label{fig:singlet_convergence}
+  \end{figure}
+  \begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{../../images/triplet-stability-convergence.pdf}
+    \caption{The lowest eigenvalue of ${}^3\mathbf{H}$ as a function of $r_s$ with increasing number of k-points in 1, 2 and 3 dimensions.}
+    \label{fig:triplet_convergence}
+  \end{figure}
+  To determine the $r_s$ at which the lowest eigenvalue of $\mathbf{H}$ changes sign, the lowest eigenvalues were linearly interpolated  {\color{red} (this can easily be changed to one of [(‘linear’, ‘nearest’, ‘zero’, ‘slinear’, ‘quadratic’, ‘cubic’ where ‘zero’, ‘slinear’, ‘quadratic’ and ‘cubic’ refer to a spline interpolation of zeroth, first, second or third order)]} as a function of $r_s$ and solving
+  \begin{equation} \label{eq:transition_rs}
+    \lambda_{min}(r_s) = 0.
   \end{equation}
-Where $n_{\ki}$ is the occupation number of the state $\ki$ and spin \cite{Guiliani2005}.
+  The solution to eq.
+\ref{eq:transition_rs} is referred to as the transition $r_s$ and this quantity was determined while increasing the number of k-points in the simulation to convergence (see Fig.
+\ref{fig:onset}).
 
-A program was implemented to calculate the stability of the HEG with a simple cubic lattice in 1, 2
-and 3 dimensions. As we are only interested in the presence of any number of negative eigenvalues, 
-it suffices to calculate the lowest eigenvalue and determine its sign. Due to the sparse and 
-diagonally dominant nature of $\mathbf{H}$, this is a natural candidate for the Jacobi-Davidson 
-Algorithm \cite{Davidson1975}. The algorithm was implented using the SLEPc package, an extension of 
-the PETSc suite \cite{Hernandez2005}\cite{petsc-web-page}.
+  \begin{tabular}{c | c }\label{table:transition_rs}
+    D~~~ & ~~ Transition $r_s$ \\
+    \hline
+    1    &  0.09 \\
+    2    &  0.87 \\
+    3    &  3.16 \\
+    \hline
+  \end{tabular}
 
-\section{Discussion}
+  The transition $r_s$ occurs at $r_s = 1$ in 2D and $r_s = 3$ in 3D (See Fig.~\ref{fig:stability} and Fig.~\ref{fig:onset}).
+These results are consistent with those seen by other methods\cite{Baguet2014, Bernu2011}.
+On the other hand, the transition $r_s$ for one dimension tends towards zero and stays quite close as the number of grid points increases.
+Indeed, numerical issues appear at very high density (low $r_s$) due to divergence of the two electron integrals in the asymptotic limit.
+With this in mind, it is clear at least that the instability in the 1D case persists even at very high densities (potentially all finite densities), which is to be expected from Overhauser's proof of instability at all values of $r_s$ in 1D for the delta function potential \cite{Overhauser1962}.
+  \begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{../../images/combined_onset.eps}
+    \caption{The value of $r_s$ at which the singlet (blue) and triplet (orange) instability    occurs with increasing number of k-points in 1, 2 and 3 dimensions.
+In the 1D case (left), the singlet instability never appeared in the calculations performed.
+}
+    \label{fig:onset}
+  \end{figure}
 
-\section{Conclusion}
-
-\section{Acknowledgements}
+\begin{acknowledgements}
+The authors would like to thank...
+\end{acknowledgements}
 
 \section{References}
-\bibliography{paper_skeleton}
+\bibliography{references}
+
 \end{document}

### 2018-01-26 doc/papers/paper_skeleton/paper_skeleton.tex
Updated notebook

@@
     \centering
-    \includegraphics[width=\textwidth]{../../images/singlet-stability-convergence.pdf}
+    \includegraphics[width=\textwidth]{../../images/singlet-stability-convergence.eps}
     \caption{The lowest eigenvalue of ${}^1\mathbf{H}$ as a function of $r_s$ with increasing number of k-points in 1, 2 and 3 dimensions.}
@@
     \centering
-    \includegraphics[width=\textwidth]{../../images/triplet-stability-convergence.pdf}
+    \includegraphics[width=\textwidth]{../../images/triplet-stability-convergence.eps}
     \caption{The lowest eigenvalue of ${}^3\mathbf{H}$ as a function of $r_s$ with increasing number of k-points in 1, 2 and 3 dimensions.}
@@
 
-  \begin{tabular}{c | c }\label{table:transition_rs}
-    D~~~ & ~~ Transition $r_s$ \\
+  \begin{tabular}{ c | c }\label{table:transition_rs}
+    D~~~ & ~~ Transition $r_s$ (bohr$^{-1}$) \\
     \hline
-    1    &  0.09 \\
+    1    &  0.02 \\
     2    &  0.87 \\
@@
 
-  The transition $r_s$ occurs at $r_s = 1$ in 2D and $r_s = 3$ in 3D (See Fig.~\ref{fig:stability} and Fig.~\ref{fig:onset}).
+  The transition $r_s$ values are presented in table \ref{table:transition_rs}.
 These results are consistent with those seen by other methods\cite{Baguet2014, Bernu2011}.

### 2018-01-26 PyHFS/src/OrbitalHessian.py

@@ -4,7 +4,11 @@ import sys
 
 import numpy as np
 
-import slepc_wrapper
+try:
+    import slepc_wrapper
+except ImportError:
+    print("SLEPC CANT BE LOADED DONT USE")
+
 import twoERI
 
 

### 2018-01-26 PyHFS/src/main.py

@@ -6,11 +6,15 @@ import time
 import parameters
 from OrbitalHessian import OrbitalHessian
 
-import slepc4py
-from petsc4py import PETSc
-Pprint = PETSc.Sys.Print
 
-slepc4py.init(sys.argv)
+try:
+    import slepc4py
+    from petsc4py import PETSc
+    Pprint = PETSc.Sys.Print
+    
+    slepc4py.init(sys.argv)
+except ImportError:
+    print("CANT USE SLEPC NOW")
 
 
 def main():

### 2018-02-26 doc/papers/paper_skeleton/paper_skeleton.tex
update before purge

@@
 \begin{abstract}
-
+  In molecular electronic structure theory, breaking symmetry of a Hartree-Fock reference serves as a viable means to resolve spurious degeneracies in certain systems.
+This allows for the use of a wide array of post-Hartree-Fock methods to recover more of the correlation energy.
+While there exists proofs of the existence of lower energy broken symmetry solutions under certain circumstance in the finite case, we are unaware of analogous ones in the periodic case.
+This study presents numerical experiments into stability of paramagnetic solutions of the Homogeneous electron gas within the Hartree-Fock approximation to glean insight into the periodic case.
+We show that in 2 and 3 dimensions, the paramagnetic solution is unstable at $r_s$ above 0.87 and 3.2 atomic units, respectively.
+In one dimension the solution is essentially always unstable, in agreement with Overhauser's theorem.
+This approach also lends itself to a means of finding lower energy broken symmetry solutions, at various levels of restriction within Hartree-Fock theory.
 \end{abstract}
@@
 Together these three levels of Hartree-Fock theory form a heirarchy of increasing parameter space within which to minimize the total energy.
+In order to test whether or not a lower energy solution of broken symmetry exists, a ``stability analysis'' can be performed on a determined Hartree-Fock solution.
+
+  First, a self-consistent solution to the HF equations needs to be found, but being a solution to the Hartree-Fock equation ensures only that the solution is stationary with respect to the determined orbitals.
+If the solution is indeed a minimum, it is called ``stable'', while if there is any displacement in the electronic structure which lowers the energy, the solution is ``unstable''.
+A method for determining the stability of a Hartree-Fock solution was proposed by Thouless in 1960\cite{Thouless1960}.
+The condition was rederived into the expression familiar to quantum chemists by Čížek and Paldus in 1967\cite{Cizek1967}.
+Furthermore, the stability equations factorize depending on the symmetry of the Hartree-Fock eigenfunctions.
+To this end, Seeger and Pople outlined a hierarchical approach to systematically evaluate the stability of HF states in the restricted, unrestricted and generalized Hartree-Fock procedures\cite{Seeger1977}.
+Recently, the method has been used to aid the search for the lowest-energy Unrestricted Hartree-Fock (UHF) solutions in molecules, as well as the General Hartree-Fock (GHF) solutions in geometrically frustrated hydrogen rings which cannot conform even to the UHF scheme\cite{Pulay2016, Goings2015}.
+The lower energy HF solutions in these studies were located by first finding the instabilities in the higher spin-symmetry solutions, then using this information to obtain ``symmetry breaking'' displacements that lower the energy.
 
@@
 \section{Method}
-  Hartree-Fock (HF) Theory has been the foundation for \emph{ab initio} electronic structure theory  throughout its history.
-An often overlooked aspect of the theory is that there are many solutions to the HF equations for a given system, but being a solution to the Hartree-Fock equation ensures only that the solution is stationary with respect to the determined orbitals.
-If the solution is indeed a minimum, it is called ``stable'', while if there is any displacement in the electronic structure which lowers the energy, the solution is ``unstable''.
-A method for determining the stability of a Hartree-Fock solution was proposed by Thouless in 1960\cite{Thouless1960}.
-The condition was rederived into the expression familiar to quantum chemists by Čížek and Paldus in 1967\cite{Cizek1967}.
-Furthermore, the stability equations factorize depending on the symmetry of the Hartree-Fock eigenfunctions.
-To this end, Seeger and Pople outlined a hierarchical approach to systematically evaluate the stability of HF states in the restricted, unrestricted and generalized Hartree-Fock procedures\cite{Seeger1977}.
-Recently, the method has been used to aid the search for the lowest-energy Unrestricted Hartree-Fock (UHF) solutions in molecules, as well as the General Hartree-Fock (GHF) solutions in geometrically frustrated hydrogen rings which cannot conform even to the UHF scheme\cite{Pulay2016, Goings2015}.
-The lower energy HF solutions in these studies were located by first finding the instabilities in the higher spin-symmetry solutions, then using this information to obtain ``symmetry breaking'' displacements that lower the energy.
 
   To determine if there is indeed a symmetry-broken HF solution of lower energy, the usual method  is to determine the stability of a found Hartree-Fock solution.
-Instabilities are indicated by a negative eigenvalue the Electronic Hessian,
+Instabilities are indicated by a negative eigenvalue in the Electronic Hessian,
   \begin{equation}
@@
   \end{align}
+
+  Where occupied states are labelled by $i$ and $j$, virtual by $a$ and $b$, and $i \rightarrow a$ refers to the excitation which replaces state $i$ with state $a$.
+The relevant two electron notation is
+  \begin{equation}
+    \left< pq||rs \right> = \left< pq|rs \right> - \left< pq|sr \right>,
+  \end{equation}
+  where, 
+  \begin{equation}
+    \left< pq|rs \right> = \int \int \phi^*_p(\vec{r}_1) \phi^*_q(\vec{r}_2) \frac{1}{r_{12}} \phi_r(\vec{r}_1) \phi_s(\vec{r}_2) d\vec{r_1} d\vec{r_2}, 
+  \end{equation}
+  and states labeled with $p$, $q$, $r$, or $s$ are either occupied or virtual.
 For a paramagnetic HF solution (RHF), the Orbital Hessian factorizes into the matrices known to chemists as the singlet and triplet instability matrices ($\bf{{}^1H}$ and $\bf{{}^3H}$, respectively)\cite{Dunning1967,Seeger1977}.
@@
 
-\subsection{Method}
-  Starting with the Jellium Hamiltonian in atomic units, 
+  To apply the stability analysis to the electron gas, start with the Jellium Hamiltonian in atomic units, 
   \begin{equation}\label{hamiltonian}
    	\hat{H} = \sum_i \frac{\hat{p}_i^2}{2}  + \frac{1}{2} \sum_{i < j} \frac{1}{|\vec{r}_i - 
-   	\vec{r}_j|},
+   	\vec{r}_j|}.
   \end{equation}
-  one solution to the Hartree-Fock equations in $D$ dimensions are plane waves of the form	
+  One solution to the Hartree-Fock equations in $D$ dimensions are plane waves of the form	
   \begin{equation}\label{planewave}
@@
   and the two electron integral in this case is simply
-  \begin{align}
+  \begin{align}\label{eq:ERI_1d}
     \braket{\vec{k}, \vec{k}' | \vec{k}'', \vec{k}'''} 
@@
   \end{align}  
+  These expressions can be used to evaluate the stability of the paramagnetic electron gas.
+In doing so, presence of instabilities of triplet (${}^3\mathbf{H}$) character are a sufficient, but not necessary, condition that a solution with different densities of $\alpha$ and $\beta$ spin exists which has lower energy than the paramagnetic solution.
+An example of such a solution would be the spin-density-wave (SDW) solution.
 
-\subsection{Results}   
+\section{Results}   
   Using the equations for energies and two electron integrals, the stability analysis was performed on the paramagnetic HEG model as a function of electron density (or equivalently, the Wigner-Seitz radius, $r_s$).
@@
 This is a task well suited for an iterative subspace solver.
-To this end, the Jacobi-Davidson algorithm was from the SLEPc library was used to calculated the lowest eigenvalues\cite{Hernandez2005}.
+To this end, the Jacobi-Davidson algorithm was from the SLEPc library was used to calculated the lowest eigenvalues using the Blue Waters Supercomputer\cite{Hernandez2005}.
 
-  \begin{figure}
+  A basis of plane waves with simple cubic symmetry was used for all calculations, and the number of k-points was incremented until the lowest eigenvalues were sufficiently converged {\color{red} (for 1D and 2D more data can be gathered but in 3D getting more data is computationally unfeasible at the moment)}.
+In the 1D calculations, a potential of $V_0 = 1$ in atomic units was used.
+  \begin{figure}[H]
     \centering
@@
   \end{figure}
-  \begin{figure}
+  \begin{figure}[H]
     \centering
@@
 \ref{fig:onset}).
+  \begin{figure}[H]
+    \centering
+    \includegraphics[width=\textwidth]{../../images/combined_onset.eps}
+    \caption{The value of $r_s$ at which the singlet (green) and triplet (blue) instability    occurs with increasing number of k-points in 1, 2 and 3 dimensions.
+In the 1D case (left), the singlet instability never appeared in the calculations performed.
+}
+    \label{fig:onset}
+  \end{figure}
 
-  \begin{tabular}{ c | c }\label{table:transition_rs}
+  \begin{table}[H]
+  \centering
+  \caption{The values of $r_s$ at which the lowest eigenvalue of $\mathbf{H}$ changes sign.}
+    \begin{tabular}{ c | c }
       D~~~ & ~~ Transition $r_s$ (bohr$^{-1}$) \\
@@
      \end{tabular}
-
+  \label{table:transition_rs}
+  \end{table}  
   The transition $r_s$ values are presented in table \ref{table:transition_rs}.
-These results are consistent with those seen by other methods\cite{Baguet2014, Bernu2011}.
+These results are consistent with those seen by other methods, which show the emergence of broken symmetry phases with distinguishably lower energy at $r_s \approx 0.8$ in 2D and $r_s \approx 3$ in 3D\cite{Baguet2014, Bernu2011}.
 On the other hand, the transition $r_s$ for one dimension tends towards zero and stays quite close as the number of grid points increases.
@@
 With this in mind, it is clear at least that the instability in the 1D case persists even at very high densities (potentially all finite densities), which is to be expected from Overhauser's proof of instability at all values of $r_s$ in 1D for the delta function potential \cite{Overhauser1962}.
-  \begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{../../images/combined_onset.eps}
-    \caption{The value of $r_s$ at which the singlet (blue) and triplet (orange) instability    occurs with increasing number of k-points in 1, 2 and 3 dimensions.
-In the 1D case (left), the singlet instability never appeared in the calculations performed.
-}
-    \label{fig:onset}
-  \end{figure}
+
+\section{Conclusion}
+  The paramagnetic Hartree-Fock solution to the Homogeneous electron gas was shown numerically to be unstable with respect to broken symmetry solutions at certain densities, which were determined in 2 and 3 dimensions.
+The one dimensional solution with the delta function potential is effectively always unstable (that is to say, the value of $r_s$ at which the solution becomes unstable is within numerical error of zero).
+These results are compatible with Overhauser's theorem and direct energy comparisons.
+While the present study did not find lower energy broken symmetry solutions, the procedure for doing so is outlined by Seeger\cite{Seeger1977}.
+This procedure may be computationally difficult to actualize for this system, but nevertheless could be a worthwhile pursuit.
+By tracing the instability eigenvectors downhill in energy, the broken symmetry solutions of lower energy may be found.
+Since the correlated energy is known, it could be compared to the lowest energy Hartree-Fock energy found and may give insights into the ability of broken symmetry Hartree-Fock solutions to describe periodic systems.
 

### 2018-04-02 doc/papers/paper_skeleton/paper_skeleton.tex
Added comments for original draft

@@
   \begin{equation}
-    \left< pq|rs \right> = \int \int \phi^*_p(\vec{r}_1) \phi^*_q(\vec{r}_2) \frac{1}{r_{12}} \phi_r(\vec{r}_1) \phi_s(\vec{r}_2) d\vec{r_1} d\vec{r_2}, 
+    \left< pq|rs \right> = 
+    \int \int \phi^*_p(\vec{r}_1) \phi^*_q(\vec{r}_2) 
+    V(\vec{r}_1, \vec{r}_2) 
+    \phi_r(\vec{r}_1) \phi_s(\vec{r}_2) 
+    d\vec{r_1} d\vec{r_2}, 
   \end{equation}
@@
     \centering
-    \includegraphics[width=\textwidth]{../../images/singlet-stability-convergence.eps}
+    \includegraphics[width=\textwidth]{../../images/singlet-stability-convergence.pdf}
     \caption{The lowest eigenvalue of ${}^1\mathbf{H}$ as a function of $r_s$ with increasing number of k-points in 1, 2 and 3 dimensions.}
@@
     \centering
-    \includegraphics[width=\textwidth]{../../images/triplet-stability-convergence.eps}
+    \includegraphics[width=\textwidth]{../../images/triplet-stability-convergence.pdf}
     \caption{The lowest eigenvalue of ${}^3\mathbf{H}$ as a function of $r_s$ with increasing number of k-points in 1, 2 and 3 dimensions.}
@@
     \centering
-    \includegraphics[width=\textwidth]{../../images/combined_onset.eps}
+    \includegraphics[width=\textwidth]{../../images/combined_onset.pdf}
     \caption{The value of $r_s$ at which the singlet (green) and triplet (blue) instability    occurs with increasing number of k-points in 1, 2 and 3 dimensions.

### 2018-05-24 doc/papers/paper_skeleton/paper_skeleton.tex
Update for last day

@@
 This study presents numerical experiments into stability of paramagnetic solutions of the Homogeneous electron gas within the Hartree-Fock approximation to glean insight into the periodic case.
-We show that in 2 and 3 dimensions, the paramagnetic solution is unstable at $r_s$ above 0.87 and 3.2 atomic units, respectively.
+We show that in 2 and 3 dimensions, the paramagnetic solution is unstable at $r_s$ above 0.87 and 3.2 bohr radii, respectively.
 In one dimension the solution is essentially always unstable, in agreement with Overhauser's theorem.
@@
 \section{Introduction} 
-  The goal of electronic structure theory is to solve the electronic Schr{\"o}dinger equation  for a molecule or solid state system.
-The prevailing approach in \emph{ab initio} quantum  chemistry is to first compute a self-consistent single-determinant Hartree-Fock (HF) solution which will serve as a reference for many-body perturbative (MP) or coupled-cluster (CC) approaches.
-Implicit in these methods is the assumption that the reference wave function will be sufficiently close to the exact solution of the Schr{\"o}dinger equation to converge to the correct answer in a computationally feasible manner.
-Both the MP and CC approaches have the attractive quality that they are systematically improvable, i.e.
-increasing the accuracy of the resulting solution can be done by using a higher order of the theory.
-These so-called post-Hartree-Fock methods are able to recover more of the total electronic energy by accounting for the \emph{correlation energy} in the system.
-Traditionally, the correlation energy is defined by the difference between the exact energy and the Hartree-Fock energy \cite{Shavitt2009}
-  \begin{equation}\label{eq:correlation_energy}
-    E_{corr} = E_{exact} -  E_{HF}.
-  \end{equation}
-  In many cases the correlation energy is relatively small and the Hartree-Fock reference captures a significant portion of the exact total energy.
-In such cases, the prevailing approach is usually successful and has only implementation issues for larger systems.
-On the other hand there are systems which are not well treated by this approach, which are often called ``strongly correlated''.
-Examples of such systems are those with degenerate or near-degenerate HOMO-LUMO gaps, metallic solids or molecules close to breaking bonds.
-Oftentimes for such systems the traditional Hartree-Fock solutions are not even qualitatively correct, implying inadequacies in either the single-reference or mean-field approach.
-
-  It is often neglected, however, that the usual way for computing a Hartree-Fock solution in practice is to use a restricted form of the single determinantal wavefunction.
-In the Restricted  Hartree-Fock (RHF), the wave function is restricted to be an eigenfunction of the $\hat{S^2}$ and $\hat{S_z}$ operators, while in the Unrestricted variant (UHF), the wave function need only be an eigenfunction of the $\hat{S_z}$.
-There is yet another lesser-known variation of the theory, known as General Hartree-Fock (GHF), which assumes no spin-symmetries in the wave function.
-This allows for greater variational flexibility at the cost of ``broken symmetry''.
-Together these three levels of Hartree-Fock theory form a heirarchy of increasing parameter space within which to minimize the total energy.
-In order to test whether or not a lower energy solution of broken symmetry exists, a ``stability analysis'' can be performed on a determined Hartree-Fock solution.
-
-  First, a self-consistent solution to the HF equations needs to be found, but being a solution to the Hartree-Fock equation ensures only that the solution is stationary with respect to the determined orbitals.
+  Computational electronic structure in practice often requires a self-consistent solution to the Hartree-Fock equations.
+However, Being a solution to the HF equations ensures only that the solution is stationary with respect to the determined orbitals.
 If the solution is indeed a minimum, it is called ``stable'', while if there is any displacement in the electronic structure which lowers the energy, the solution is ``unstable''.
@@
 
-  Previously it has been shown for finite systems with form-degenerate HOMO-LUMO, there always exists a symmetry-breaking instability\cite{Yamada2015}.
-Whether this theorem holds in the infinite case remains to be seen.
+  Previously it has been shown for finite systems with form-degenerate HOMO-LUMO, there always exists a symmetry-breaking instability, but this theorem does not hold in the infinite case \cite{Yamada2015}.
 To investigate HF instabilities in zero band gap solids, a natural starting point is the Homogeneous Electron Gas (HEG, often called Jellium or Uniform Electron Gas) model.
@@
 
-  The present work focuses on directly calculating the Hartree-Fock stability of the paramagnetic homogeneous electron gas as a function of electron density.
-The motivation is two-fold.
-First, the numerical studies of this model can give computational evidence for or against the ubiquity of symmetry-breaking HF instabilities in metallic solids.
-Secondly, the instabilities can help in determining lower energy HF solutions of the HEG.
-This is because the study will reveal where the symmetry broken Hartree-Fock reference is needed.
-To date, an optimal form (i.e.
-minimal energy in the HF manifold) of the Hartree-Fock solution to the HEG remains unknown, even though exact energy (including correlation) is essentially known.
-Therefore determining a lower energy HF solution can yield insight into the effects of correlation of this fundamental physical model.
-
- % Thus the term ``Hartree-Fock Energy'' is inherently ambigious; this fact calling into question commonly held ideas about correlation and Hartree-Fock theory.
-Take for example the dissociation curve of H$_2$ in the RHF and UHF approximations, compared with the exact solution obtained by full configuration-interaction in the complete basis set limit.
- % \begin{figure}[H]
- %   \centering
- %   \includegraphics[width=0.75\textwidth]{../../images/H2_curves.eps}
- %   \caption{Dissociation curve of H$_2$ in the RHF and UHF approximations, compared to the exact limit (FCI).
-The difference in correlation energies as determined by each reference illustrates the ambiguity of that quantity.
-In the dissociation limit, the UHF correlation energy vanishes while the RHF correlation energy increases in magnitude.}
- %   \label{h2diss}
- % \end{figure}
- % The correlation energy for the RHF reference case is dramatically larger than that for the UHF reference.
-In other words, \emph{the correlation energy is, by definition, inherently coupled to the Hartree-Fock reference}.
-The given example is well understood, but it brings to mind a more general idea that there may be more cases where apparently large correlation energies are due to simply using and inadequate level of Hartree-Fock theory.
-Scuseria and coworkers have leveraged this idea to create new coupled cluster theories while preserving the symmetry of the reference  \cite{Gomez2016}.
-
-  %Another approach to this problem is to allow breaking of symmetry, and to take the variational principle at face value; lower energy is always better.
-For predicting certain observables this is not the case, but for energies alone we are free to maintain this mindset.
-If the HF solution is allowed to relax fully in its most general form, the resulting correlation energy may be reduced dramatically.
-Therefore the overarching theme of the proposed work is that \emph{many examples of strong correlation may be misleading, and in order to find out we have to find lower  energy Hartree-Fock solutions, even at the cost of broken symmetry}.
-
-  %If it turns out that fully minimizing the HF energy can reproduce a majority of the ``correlation energy'' in these systems, then using this HF searching method becomes a justified method of solving strongly correlated systems.
-This would mean that the strong correlation was in fact illusory, and is convertible to a weak correlation problem by means of a more rigorous Hartree-Fock theory.
+  The present work focuses on directly calculating the Hartree-Fock stability of the paramagnetic homogeneous electron gas as a function of electron density in order to see if the singlet/instability theorems apply in this continuous system.
+It is important here to note that instability is a sufficient but not necessary condition for the presence of a lower energy solution, and therefore Overhauser's theorem does not strictly imply instability at all densities.
+Given this fact, we can learn about the differences between instability detection and direct minimization techniques within Hartree-Fock theory.
+It may also be insightful to see if the difference depend on the level of restriction used in the HF equations (i.e.
+UHF vs GHF).
 
@@
 
-  To determine if there is indeed a symmetry-broken HF solution of lower energy, the usual method  is to determine the stability of a found Hartree-Fock solution.
+  Usually to find a symmetry-broken HF solution of lower energy, the method employed is to determine the stability of a found Hartree-Fock solution.
 Instabilities are indicated by a negative eigenvalue in the Electronic Hessian,
@@
     \left< pq|rs \right> = 
-    \int \int \phi^*_p(\vec{r}_1) \phi^*_q(\vec{r}_2) 
+    \int \int \phi^*_p(\vec{x}_1) \phi^*_q(\vec{x}_2) 
     V(\vec{r}_1, \vec{r}_2) 
-    \phi_r(\vec{r}_1) \phi_s(\vec{r}_2) 
-    d\vec{r_1} d\vec{r_2}, 
+    \phi_r(\vec{x}_1) \phi_s(\vec{x}_2) 
+    d\vec{x_1} d\vec{x_2}, 
   \end{equation}
   and states labeled with $p$, $q$, $r$, or $s$ are either occupied or virtual.
-For a paramagnetic HF solution (RHF), the Orbital Hessian factorizes into the matrices known to chemists as the singlet and triplet instability matrices ($\bf{{}^1H}$ and $\bf{{}^3H}$, respectively)\cite{Dunning1967,Seeger1977}.
+In this paper angled brackets $\left< ...
+\right>$ denote integrals over spatial and spin degrees of freedom $d\vec{x}$, while parentheses $\left ( ...
+\right ) $ denote integration over spatial coordinates, $d\vec{r}$, only.
+For a paramagnetic HF solution (RHF), integrating the Orbital Hessian elements over spin yields the singlet and triplet instability matrices ($\bf{{}^1H}$ and $\bf{{}^3H}$, respectively)\cite{Dunning1967,Seeger1977}.
   \begin{subequations}
@@
       (\epsilon_a-\epsilon_i)\delta_{ij}\delta_{ab} 
-      + 2\braket{aj|ib}-\braket{aj|bi}\\
+      + 2\left(aj|ib\right)-\left(aj|bi\right)\\
       {}^{3}{A'}_{i\rightarrow a, j\rightarrow b} &=& 
       (\epsilon_a-\epsilon_i)\delta_{ij}\delta_{ab} 
-      - \braket{aj|bi}\\
-      {}^{1}{B'}_{i\rightarrow a, j\rightarrow b} &=& 2\braket{ab|ij}-\braket{ab|ji}\\
-      {}^{3}{B'}_{i\rightarrow a, j\rightarrow b} &=& -\braket{ab|ji}
+      - \left(aj|bi\right)\\
+      {}^{1}{B'}_{i\rightarrow a, j\rightarrow b} &=& 2\left(ab|ij\right) - \left(ab|ji\right)\\
+      {}^{3}{B'}_{i\rightarrow a, j\rightarrow b} &=& -\left(ab|ji\right)
     \end{eqnarray}
@@
   \begin{equation}\label{hamiltonian}
-   	\hat{H} = \sum_i \frac{\hat{p}_i^2}{2}  + \frac{1}{2} \sum_{i < j} \frac{1}{|\vec{r}_i - 
-   	\vec{r}_j|}.
+   	\hat{H} = - \sum_i \frac{\hat{p}_i^2}{2}  + \sum_{i < j} V(\vec{r}_i, \vec{r}_j)  .
   \end{equation}
@@
    	\phi_{\vec{k}} =
-    \frac{1} { \sqrt{L ^ D} } e ^ {i \vec{k} \dot \vec{x}},
+    \frac{1} { \sqrt{L ^ D} } e ^ {i \vec{k} \cdot \vec{x}},
   \end{equation}
@@
   \begin{align}
-    \braket{\vec{k}, \vec{k}' | \vec{k}'', \vec{k}'''} 
+    \left( \vec{k}, \vec{k}' | \vec{k}'', \vec{k}''' \right) 
     \stackrel{ \text{2D, 3D} }{=}&
@@
     \frac{\hbar^2\vec{k}^2}{2m} - \sum\limits_{\vec{k}}^{|\vec{k}|< 
-    k_f}n_{\vec{k}\sigma}\braket{\vec{k}, \vec{k}' |\vec{k}', \vec{k}},
+    k_f}n_{\vec{k}\sigma} \left( \vec{k}, \vec{k}' |\vec{k}', \vec{k} \right),
   \end{equation}
@@
     \begin{cases} 
-      V_0 
+      \frac{V_0}{L} 
       & \vec{k}''' = \vec{k} + \vec{k}' - \vec{k}'' + n\vec{G}\\
@@
     \centering
-    \includegraphics[width=\textwidth]{../../images/singlet-stability-convergence.pdf}
-    \caption{The lowest eigenvalue of ${}^1\mathbf{H}$ as a function of $r_s$ with increasing number of k-points in 1, 2 and 3 dimensions.}
+    \includegraphics[]{fit_curves.eps}
+    \caption{The lowest eigenvalue of ${}^1\mathbf{H}$ (Singlet instability) and ${}^3\mathbf{H}$ (Triplet instability) as a function of $r_s$ for a representative calculation in 2 dimensions with 1936 k-points.}
     \label{fig:singlet_convergence}
@@
   \end{figure}
-  To determine the $r_s$ at which the lowest eigenvalue of $\mathbf{H}$ changes sign, the lowest eigenvalues were linearly interpolated  {\color{red} (this can easily be changed to one of [(‘linear’, ‘nearest’, ‘zero’, ‘slinear’, ‘quadratic’, ‘cubic’ where ‘zero’, ‘slinear’, ‘quadratic’ and ‘cubic’ refer to a spline interpolation of zeroth, first, second or third order)]} as a function of $r_s$ and solving
+  To determine the $r_s$ at which the lowest eigenvalue of $\mathbf{H}$ changes sign, the lowest eigenvalues were linearly interpolated  as a function of $r_s$ and solving
   \begin{equation} \label{eq:transition_rs}
@@
     \centering
-    \includegraphics[width=\textwidth]{../../images/combined_onset.pdf}
+    \includegraphics[width=\textwidth]{onsets.eps}
     \caption{The value of $r_s$ at which the singlet (green) and triplet (blue) instability    occurs with increasing number of k-points in 1, 2 and 3 dimensions.
@@
   \centering
-  \caption{The values of $r_s$ at which the lowest eigenvalue of $\mathbf{H}$ changes sign.}
-    \begin{tabular}{ c | c }
-      D~~~ & ~~ Transition $r_s$ (bohr$^{-1}$) \\
+  \caption{Critical values of $r_s$.}
+    \begin{tabular}{ c  c  c }
+      D~ & ~ Instability (bohr$^{-1}$) ~ &  \\ 
       \hline
-      1    &  0.02 \\
-      2    &  0.87 \\
-      3    &  3.16 \\
+      1    &  0.51 &  \\
+      2    &  0.86 & 0.8 \\
+      3    &  2.92 & 3.0 \\
       \hline
@@
 On the other hand, the transition $r_s$ for one dimension tends towards zero and stays quite close as the number of grid points increases.
-Indeed, numerical issues appear at very high density (low $r_s$) due to divergence of the two electron integrals in the asymptotic limit.
-With this in mind, it is clear at least that the instability in the 1D case persists even at very high densities (potentially all finite densities), which is to be expected from Overhauser's proof of instability at all values of $r_s$ in 1D for the delta function potential \cite{Overhauser1962}.
 
 \section{Conclusion}
-  The paramagnetic Hartree-Fock solution to the Homogeneous electron gas was shown numerically to be unstable with respect to broken symmetry solutions at certain densities, which were determined in 2 and 3 dimensions.
-The one dimensional solution with the delta function potential is effectively always unstable (that is to say, the value of $r_s$ at which the solution becomes unstable is within numerical error of zero).
-These results are compatible with Overhauser's theorem and direct energy comparisons.
-While the present study did not find lower energy broken symmetry solutions, the procedure for doing so is outlined by Seeger\cite{Seeger1977}.
-This procedure may be computationally difficult to actualize for this system, but nevertheless could be a worthwhile pursuit.
-By tracing the instability eigenvectors downhill in energy, the broken symmetry solutions of lower energy may be found.
-Since the correlated energy is known, it could be compared to the lowest energy Hartree-Fock energy found and may give insights into the ability of broken symmetry Hartree-Fock solutions to describe periodic systems.
 

### 2018-05-24 HFS/src/calc_parameters.cpp

@@ -56,9 +56,9 @@ namespace HFS {
         if (NDIM == 1) {
             vol = 2.0 * N_elec * rs;
             if (use_delta_1D == true) {
-                two_e_const = twoE_parameter_1dCase;
+                two_e_const = twoE_parameter_1dCase / vol;
             } else {
-                two_e_const = twoE_parameter_1dCase;    // 'a' for the exponential integral, radius of cylinder.
+                two_e_const = twoE_parameter_1dCase / vol;    // 'a' for the exponential integral, radius of cylinder.
             }
         } else if (NDIM == 2) {
             vol = N_elec * PI * std::pow(rs, 2);
